\section{Version 1.2}
This section summarizes the changes from the \openshmem specification Version 1.1 to Version 1.2.  
A major change in this version is that it improves upon the execution model described in 1.1 by introducing an explicit \FUNC{shmem\_finalize} library call. This provides a collective mechanism of exiting an \openshmem program and releasing resources used by the library.  



The following list describes the specific changes in 1.2:
\begin{itemize}
\item Added specification of \VAR{pSync} initialization for all routines that use it.
\item Replaced all placeholder variable names \VAR{target} with \VAR{dest} to avoid confusion with Fortran `target' keyword.
\item New Execution Model for exiting/finishing OpenSHMEM programs.
\\See Section  \ref{subsec:execution_model}.
\item New library constants to support API that query version and name information.
\\See Section \ref{subsec:library_constants}.
\item New API \FUNC{shmem\_init} to provide mechanism to start an \openshmem program and replace deprecated \FUNC{start\_pes}.
\\See Section \ref{subsec:shmem_init}.
\item Deprecation of \FUNC{\_my\_pe} and \FUNC{\_num\_pes} routines.
\\See Sections \ref{subsec:shmem_my_pe} and \ref{subsec:shmem_num_pe}.
\item New API \FUNC{shmem\_finalize} to provide collective mechanism to cleanly exit an \openshmem program and release resources.
\\See Section \ref{subsec:shmem_finalize}.
\item New API \FUNC{shmem\_global\_exit} to provide mechanism to exit an \openshmem program.
\\See Section \ref{subsec:shmem_global_exit}.
\item Clarification related to the address of the referenced object in \FUNC{shmem\_ptr}.
\\See Section \ref{subsec:shmem_ptr}.
\item New API to query the version and name information. 
\\See Section \ref{subsec:shmem_version} and \ref{subsec:shmem_name}.
\item \openshmem library API normalization. All C symmetric memory management API begins with  \FUNC{shmem\_}.
\\See Section \ref{subsec:shfree}.
\item Notes and clarifications added to \FUNC{shmem\_malloc}.
\\See Section \ref{subsec:shfree}.
\item Deprecation of Fortran API routine \FUNC{SHMEM\_PUT}.
\\See Section \ref{subsec:shmem_put}. 
\item Clarification related to \FUNC{shmem\_wait}.
\\See Section \ref{subsec:shmem_wait}.
\item Undefined behavior for null pointers without zero counts added.
\\See Section \ref{sec:undefined}
\item Addition of new Annex for clearly specifying deprecated API and its support in the existing specification version.
\\See Section \ref{sec:dep_api}.

\end{itemize}
