\apisummary
{
    A collective operation that releases resources used by the \openshmem library.
    This only terminates the \openshmem portion of a program, not the entire
    program.
}

\begin{apidefinition}

\begin{Csynopsis}
void shmem_finalize(void);
\end{Csynopsis}

\begin{Fsynopsis}
CALL SHMEM_FINALIZE
\end{Fsynopsis}

\begin{apiarguments}
    \apiargument{None.}{}{}
\end{apiarguments}

\apidescription
{
    \FUNC{shmem\_finalize} is a collective operation that ends the \openshmem
    portion of a program previously initialized by \FUNC{shmem\_init} and
    releases resources used by the \openshmem library. This collective
    operation requires all \acp{PE} to participate in the call. There is an
    implicit global barrier in \FUNC{shmem\_finalize} so that pending
    communication is completed, and no resources can be released until all
    \acp{PE} have entered \FUNC{shmem\_finalize}. \FUNC{shmem\_finalize} must be
    the last \openshmem library call encountered in the \openshmem portion of a
    program. A call to \FUNC{shmem\_finalize} will release any resources
    initialized by a corresponding call to \FUNC{shmem\_init}. All processes and
    threads that represent the \acp{PE} will still exist after the call to
    \FUNC{shmem\_finalize} returns, but they will no longer have access to any
    resources that have been released.
}

\apireturnvalues{None.}

\apinotes
{
    \FUNC{shmem\_finalize} releases all resources used by the \openshmem library
    including the symmetric memory heap and pointers initiated by
    \FUNC{shmem\_ptr}. This collective operation requires all \acp{PE} to
    participate in the call, not just a subset of the \acp{PE}. The
    non-\openshmem portion of a program may continue after a call to
    \FUNC{shmem\_finalize} by all \acp{PE}. There is is an implicit
    \FUNC{shmem\_finalize} at the end of main, so that having an explicit call
    to \FUNC{shmem\_finalize} is optional. However, an explicit
    \FUNC{shmem\_finalize} may be required as an entry point for wrappers used
    by profiling or other tools that need to perform their own finalization.
}

\begin{apiexamples}

\apicexample
    {The following finalize example is for \CorCpp{} programs:}
    {./example_code/shmem_finalize_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
