\apisummary{
    Performs an atomic conditional swap on a remote data object.
}

\begin{apidefinition}

\begin{Csynopsis}
int shmem_int_cswap(int *dest, int cond, int value, int pe);
long shmem_long_cswap(long *dest, long cond, long value, int pe);
long shmem_longlong_cswap(long long *dest, long long cond, long long value, int pe);
\end{Csynopsis}

\begin{Fsynopsis}
INTEGER pe
INTEGER*4 SHMEM_INT4_CSWAP,  cond_i4, value_i4, ires_i4
ires_i4 = SHMEM_INT4_CSWAP(dest, cond_i4, value_i4, pe)
INTEGER*8 SHMEM_INT8_CSWAP,  cond_i8, value_i8, ires_i8
ires_i8 = SHMEM_INT8_CSWAP(dest, cond_i8, value_i8, pe)
\end{Fsynopsis}

\begin{apiarguments}
    \apiargument{OUT}{dest}{The remotely accessible integer data object to be
        updated on the remote \ac{PE}. }
    \apiargument{IN}{cond}{\VAR{cond} is compared to the remote \VAR{dest}
        value. If \VAR{cond} and the remote \VAR{dest} are equal, then \VAR{value}
        is swapped into the remote \VAR{dest}. Otherwise, the remote \VAR{dest} is
        unchanged.  In either case, the old value of the remote \VAR{dest} is
        returned as the routine return value. \VAR{cond} must be of the same data
        type as \VAR{dest}.}
    \apiargument{IN}{value}{The value to be atomically written to the remote
        \ac{PE}. \VAR{value} must be the same data type as \VAR{dest}.}
    \apiargument{IN}{pe}{An integer that indicates the \ac{PE} number upon which
        \VAR{dest} is to be updated. If you are using \Fortran, it must be a default
        integer value.}
\end{apiarguments}

\apidescription{  
    The conditional swap routines conditionally update a \VAR{dest} data object on
    an arbitrary \ac{PE} and return the prior contents of the data object in one
    atomic operation.   
}
\apidesctable{
    The  \VAR{dest}  and source data objects must conform to certain typing
    constraints, which are as follows:
}{Routine}{Data type}

\apitablerow{SHMEM\_INT4\_CSWAP}{\CONST{4}-byte integer.}
\apitablerow{SHMEM\_INT8\_CSWAP}{\CONST{8}-byte integer.}


\apireturnvalues{
    The contents that had been in the \VAR{dest} data object on the remote
    \ac{PE} prior to the conditional swap. Data type is the same as the
    \VAR{dest} data type.
}

\apinotes{
    None.
}

\begin{apiexamples}

\apicexample
    {The following call ensures that the first \ac{PE} to execute the
    conditional swap will successfully write its \ac{PE} number to
    \VAR{race\_winner} on \ac{PE} \CONST{0}.}
    {./example_code/shmem_cswap_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
