An \ac{AMO} is a one-sided communication mechanism that combines memory read,
update, or write operations with atomicity guarantees described in Section~%
\ref{subsec:amo_guarantees}.  Similar to the \ac{RMA} routines, described in
Section~\ref{sec:rma}, the \acp{AMO} are performed only on symmetric objects.
\openshmem defines two types of \ac{AMO} routines:

\begin{itemize}

\item
  The \emph{fetching} routines return the original value of, and optionally
  update, the remote data object in a single atomic operation.  The routines
  return after the data has been fetched from the target \ac{PE} and delivered
  to the calling \ac{PE}.
  The data type of the returned value is the same as the type of
  the remote data object.

  The fetching routines include:
  \FUNC{shmem\_atomic\_\{fetch, compare\_swap, swap\}\{\_nbi\}} and
  \FUNC{shmem\_atomic\_fetch\_\{inc, add, and, or, xor\}\{\_nbi\}}.

\item
  The \emph{non-fetching} routines update the remote data object in a single
  atomic operation.  A call to a non-fetching atomic routine issues the atomic
  operation and may return before the operation executes on the target \ac{PE}.
  The \FUNC{shmem\_quiet}, \FUNC{shmem\_barrier}, or \FUNC{shmem\_barrier\_all}
  routines can be used to force completion for these non-fetching
  atomic routines.

  The non-fetching routines include:
  \FUNC{shmem\_atomic\_\{set, inc, add, and, or, xor\}\{\_nbi\}}.

\end{itemize}

\openshmem \ac{AMO} routines specified in this section have two variants. In
one of the variants, the context handle, \VAR{ctx}, is explicitly passed as
an argument. In this variant, the operation is performed on the specified 
context. If the context handle \VAR{ctx} does not correspond to a valid
context, the behavior is undefined. In the other variant, the context handle
is not explicitly passed and thus, the operations are performed on the
default context.

Where appropriate compiler support is available, \openshmem provides
type-generic \ac{AMO} interfaces via \Cstd[11] generic selection.
The type-generic support for the \ac{AMO} routines is as follows:

\begin{itemize}
\item \FUNC{shmem\_atomic\_\{compare\_swap, fetch\_inc, inc, fetch\_add, add\}\{\_nbi\}}
  support the ``standard \ac{AMO} types'' listed in Table~\ref{stdamotypes},
\item \FUNC{shmem\_atomic\_\{fetch, set, swap\}} support
  the ``extended \ac{AMO} types'' listed in Table~\ref{extamotypes}, and
\item \FUNC{shmem\_atomic\_\{fetch\_and, and, fetch\_or, or, fetch\_xor, xor\}\{\_nbi\}}
  support the ``bitwise \ac{AMO} types'' listed in Table~\ref{bitamotypes}.
\end{itemize}

The standard, extended, and bitwise \ac{AMO} types include some of the exact-width
integer types defined in \HEADER{stdint.h} by \Cstd[99]~\S7.18.1.1 and
\Cstd[11]~\S7.20.1.1. When the \Cstd translation environment
does not provide exact-width integer types with \HEADER{stdint.h}, an
\openshmem implemementation is not required to provide support for these types.

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|l|}
      \hline
      \TYPE              & \TYPENAME  \\ \hline
      int                & int        \\ \hline
      long               & long       \\ \hline
      long long          & longlong   \\ \hline
      unsigned int       & uint       \\ \hline
      unsigned long      & ulong      \\ \hline
      unsigned long long & ulonglong  \\ \hline
      int32\_t           & int32      \\ \hline
      int64\_t           & int64      \\ \hline
      uint32\_t          & uint32     \\ \hline
      uint64\_t          & uint64     \\ \hline
      size\_t            & size       \\ \hline
      ptrdiff\_t         & ptrdiff    \\ \hline
    \end{tabular}
    \TableCaptionRef{Standard \ac{AMO} Types and Names}
    \label{stdamotypes}
  \end{center}
\end{table}

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|l|}
      \hline
      \TYPE              & \TYPENAME  \\ \hline
      float              & float      \\ \hline
      double             & double     \\ \hline
      int                & int        \\ \hline
      long               & long       \\ \hline
      long long          & longlong   \\ \hline
      unsigned int       & uint       \\ \hline
      unsigned long      & ulong      \\ \hline
      unsigned long long & ulonglong  \\ \hline
      int32\_t           & int32      \\ \hline
      int64\_t           & int64      \\ \hline
      uint32\_t          & uint32     \\ \hline
      uint64\_t          & uint64     \\ \hline
      size\_t            & size       \\ \hline
      ptrdiff\_t         & ptrdiff    \\ \hline
    \end{tabular}
    \TableCaptionRef{Extended \ac{AMO} Types and Names}
    \label{extamotypes}
  \end{center}
\end{table}

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|l|}
      \hline
      \TYPE              & \TYPENAME  \\ \hline
      unsigned int       & uint       \\ \hline
      unsigned long      & ulong      \\ \hline
      unsigned long long & ulonglong  \\ \hline
      int32\_t           & int32      \\ \hline
      int64\_t           & int64      \\ \hline
      uint32\_t          & uint32     \\ \hline
      uint64\_t          & uint64     \\ \hline
    \end{tabular}
    \TableCaptionRef{Bitwise \ac{AMO} Types and Names}
    \label{bitamotypes}
  \end{center}
\end{table}
