\clearpage %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

%defining pagestyle for annex
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\thesection}{\thesectionOrig}




\chapter{Writing OpenSHMEM Programs}
\section*{Incorporating OpenSHMEM into Programs}\label{sec:writing_programs}

The following section describes how to write a ``Hello World" \openshmem program.
To write a ``Hello World" \openshmem program, the user must:

\begin{itemize}
\item Include the header file \HEADER{shmem.h} for \Cstd.
\item Add the initialization call \hyperref[subsec:shmem_init]{\FUNC{shmem\_init}}.
\item Use \openshmem calls to query the local \ac{PE} number
    (\hyperref[subsec:shmem_my_pe]{\FUNC{shmem\_my\_pe}}) and the total number
    of \acp{PE} (\hyperref[subsec:shmem_n_pes]{\FUNC{shmem\_n\_pes}}).
\item Add the finalization call \hyperref[subsec:shmem_finalize]{\FUNC{shmem\_finalize}}.
\end{itemize}

In \openshmem, the order in which lines appear in the output is not
deterministic because \acp{PE} execute asynchronously in parallel.

\SourceExample{example_code/hello-openshmem.c}{
  \label{openshmem-hello}
  ``Hello World'' example program in \Cstd
}

\ProgramOutput{example_code/hello-openshmem-c.output}{
  Possible ordering of expected output with 4 \acp{PE} from the
  program in Example~\ref{openshmem-hello}
}

\clearpage %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Example~\ref{openshmem-hello-symmetric} shows a more complex
\openshmem program that illustrates the use of symmetric data objects.
Note the declaration of the \VAR{static short dest} array and its use as the
remote destination in \hyperref[subsec:shmem_put]{\FUNC{shmem\_put}}.

The \KEYWORD{static} keyword makes the \VAR{dest} array symmetric on all \acp{PE}.
Each \ac{PE} is able to transfer data to a remote \dest{} array by simply
specifying to an \openshmem routine such as \hyperref[subsec:shmem_put]{\FUNC{shmem\_put}}
the local address of the symmetric data object that will receive the data.
This local address resolution aids programmability because the address of the
\dest{} need not be exchanged with the active side (\ac{PE} \CONST{0}) prior to
the \acf{RMA} routine.

Conversely, the declaration of the \VAR{short source} array is asymmetric
(local only).
The \source{} object does not need to be symmetric because \PUT{} handles the
references to the \VAR{source} array only on the active (local) side.

\SourceExample{example_code/writing_shmem_example.c}{
  \label{openshmem-hello-symmetric}
  Example program with symmetric data objects
}

\ProgramOutput{example_code/writing_shmem_example.output}{
  Possible ordering of expected output with 4~\acp{PE} from the
  program in Example~\ref{openshmem-hello-symmetric}
}

\chapter{Compiling and Running Programs}\label{sec:compiling}
The \openshmem Specification does not specify how
\openshmem programs are compiled, linked, and run. This section shows some
examples of how wrapper programs are utilized in the \openshmem Reference
Implementation to compile and launch programs.

\section{Compilation}
\subsection*{Programs written in \Cstd}

The \openshmem Reference Implementation provides a wrapper program, named
\textbf{oshcc}, to aid in the compilation of \Cstd programs.
The wrapper may be called as follows:

\begin{lstlisting}[]
oshcc <compiler options> -o myprogram myprogram.c
\end{lstlisting}
Where the $\langle\mbox{compiler options}\rangle$ are options understood by the
underlying \Cstd compiler called by \textbf{oshcc}.


\subsection*{Programs written in \Cpp}

The \openshmem Reference Implementation provides a wrapper program, named
\textbf{oshc++}, to aid in the compilation of \Cpp programs.
The wrapper may be called as follows:

\begin{lstlisting}[]
oshc++ <compiler options> -o myprogram myprogram.cpp
\end{lstlisting}
Where the $\langle\mbox{compiler options}\rangle$ are options understood by the
underlying \Cpp compiler called by \textbf{oshc++}.


\section{Running Programs}

The \openshmem Reference Implementation provides a wrapper program, named
\textbf{oshrun}, to launch \openshmem programs.
The wrapper may be called as follows:

\begin{lstlisting}[]
oshrun <runner options> -np <#> <program> <program arguments>
\end{lstlisting}
The arguments for \textbf{oshrun} are:

\begin{tabular}{p{0.3\textwidth}p{0.6\textwidth}}
$\langle\mbox{runner options}\rangle$ & {Options passed to the underlying launcher.}\tabularnewline
-np $\langle\mbox{\#}\rangle$ & {The number of \acp{PE} to be used in the execution.}\tabularnewline
$\langle\mbox{program}\rangle$ & {The program executable to be launched.}\tabularnewline
$\langle\mbox{program arguments}\rangle$ & {Flags and other parameters to pass to the program.}\tabularnewline
\end{tabular}




\chapter{Undefined Behavior in OpenSHMEM}\label{sec:undefined}

The \openshmem Specification formalizes the expected behavior of
its library routines.  In cases where routines are improperly used
or the input is not in accordance with the Specification, the behavior
is undefined.

\begin{longtable}{|>{\raggedright}p{0.3\textwidth}|>{\raggedright}p{0.6\textwidth}|}
\hline
\textbf{Inappropriate Usage} & \textbf{Undefined Behavior}\tabularnewline
\hline
\endhead
Uninitialized library & If the \openshmem library is not initialized,
calls to \openshmem routines that do not initialize the \openshmem library have undefined
behavior.  For example, an implementation may try to continue or may abort
immediately upon an \openshmem call into the uninitialized library.
\tabularnewline
\hline
Specifying invalid \ac{PE} numbers & For \openshmem routines that accept a
\ac{PE} number as an argument, if the \ac{PE} number is invalid for the
team associated with the operation (either implicitly or explicitly), the
behavior is undefined.  An invalid \ac{PE} number includes those that are
negative or greater than or equal to the size of the associated team.
\tabularnewline
\hline
Use of non-symmetric variables & Some routines require remotely accessible
variables to perform their function.  For example, an \openshmem library may detect a \PUT{} to a non-symmetric variable
and choose to abort the program.
However, another implementation may choose to continue execution with or without a warning.
\tabularnewline
\hline
Non-symmetric allocation of symmetric memory & The symmetric memory management routines are
collectives. For example, all \acp{PE} in the program must call
\FUNC{shmem\_malloc} with the same \VAR{size} argument.  Program behavior after a
mismatched \FUNC{shmem\_malloc} call is undefined.\tabularnewline
\hline
Use of null pointers with nonzero \VAR{len} specified & In any \openshmem routine
that takes a pointer and \VAR{len} describing the number of elements in that
pointer, a null pointer may not be given unless the corresponding \VAR{len} is also
specified as zero. Otherwise, the resulting behavior is undefined.
The following cases summarize this behavior:
\begin{itemize}
    \item \VAR{len} is 0, pointer is null: supported.
    \item \VAR{len} is not 0, pointer is null: undefined behavior.
    \item \VAR{len} is 0, pointer is non-null: supported.
    \item \VAR{len} is not 0, pointer is non-null: supported.
\end{itemize}
\tabularnewline
\hline
Multithreaded use of a team in concurrent team-based collectives &
Team-based collective operations are not thread-safe on the same \VAR{team}
object.
Concurrent collective operations on the same team from multiple threads may result in undefined
behavior.
For example, it is undefined behavior for one thread to call a team-implicit
collective which implicitly operates on the world team (e.g.,
\FUNC{shmem\_barrier\_all}) and another thread to concurrently call a
team-based collective (e.g., \FUNC{shmem\_broadcastmem}) on the same world team
object, \LibHandleRef{SHMEM\_TEAM\_WORLD}. \tabularnewline
\hline
Destroying a team with unfreed private contexts & Before destroying a given
team, the user is responsible for destroying all contexts created from that team
with the \LibConstRef{SHMEM\_CTX\_PRIVATE} option enabled; otherwise, the
behavior is undefined.\tabularnewline
\hline
Creating a team with a $stride$ value equal to 0 and the $size$ value not equal to 1 &
If a $stride$ value equal to 0 is passed to \FUNC{shmem\_team\_split\_strided},
then the $size$ argument passed must be 1, or the behavior is undefined. \tabularnewline
\hline
Creating a team that implies a wrap-around sequence &
If the triplet provided to \FUNC{shmem\_team\_split\_strided} implies a
wrap-around sequence, the input is considered invalid and the behavior is
undefined.
In other words, when $stride$ is nonzero, a newly created team must only
include \acp{PE} whose subsequent parent \ac{PE} values are either all
increasing (for positive $stride$) or all decreasing (for negative
$stride$).
That is, \textit{wrap-around} with respect to the parent team's \ac{PE} values
is not permitted.
For example, the list of \acp{PE} in the parent team should not start at a high
number and then continue to include \acp{PE} in the lower end of the parent
team's \ac{PE} range. \tabularnewline
\hline
\end{longtable}


\input{content/interoperability}

\chapter{History of OpenSHMEM}\label{sec:openshmem_history}

SHMEM has a long history as a parallel-programming model and has been
extensively used on a number of products since 1993, including the Cray T3D,
Cray X1E, Cray XT3 and XT4, \ac{SGI} Origin, \ac{SGI} Altix, Quadrics-based
clusters, and InfiniBand-based clusters.

\begin{itemize}
\item SHMEM Timeline
  \begin{itemize}
  \item Cray SHMEM
    \begin{itemize}
    \item SHMEM first introduced by Cray Research, Inc.\ in 1993 for Cray T3D
    \item Cray was acquired by \ac{SGI} in 1996
    \item Cray was acquired by Tera in 2000 (MTA)
    \item Platforms: Cray T3D, T3E, C90, J90, SV1, SV2, X1, X2, XE, XMT, XT
    \item \ac{HPE} acquired Cray in 2019
    \end{itemize}
  \item \ac{SGI} SHMEM
    \begin{itemize}
    \item \ac{SGI} acquired Cray Research, Inc.\ and SHMEM was integrated into
      \ac{SGI}'s Message Passing Toolkit (MPT)
    \item \ac{SGI} currently owns the rights to SHMEM and \openshmem
    \item Platforms: Origin, Altix 4700, Altix XE, ICE, UV
    \item \ac{SGI} was acquired by Rackable Systems in 2009
    \item \ac{SGI} and \ac{OSSS} signed a
      SHMEM trademark licensing agreement in 2010
    \item \ac{HPE} acquired \ac{SGI} in 2016
    \end{itemize}
  \end{itemize}
\end{itemize}

A listing of \openshmem implementations can be found on
\url{http://www.openshmem.org/}.








\chapter{Deprecated \acs{API}}\label{sec:dep}

\section{Overview}\label{dep:overview}
\TableIndex{Deprecated \acs{API}}
For the \openshmem Specification, deprecation is the process of identifying
\ac{API} that is supported but no longer recommended for use by users.
The deprecated \ac{API} \textbf{must} be supported until clearly
indicated as otherwise by the Specification.
This chapter records the \ac{API} or functionality that have been deprecated, the
version of the \openshmem Specification that effected the deprecation, and the
most recent version of the \openshmem Specification in which the feature was
supported before removal.

\begin{center}
\scriptsize
\begin{longtable}{|l|c|c|l|}
    \hline
    \textbf{Deprecated \ac{API}}
    & \textbf{Deprecated Since}
    & \textbf{Last Version Supported}
    & \textbf{Replaced By} \\
    \hline
    \endhead
    %% Deprecated in 1.1
    Header Directory: \hyperref[dep:mpp_header]{\HEADER{mpp}} & 1.1 & Current & (none) \\ \hline
    %% Deprecated in 1.2
    \CorCpp: \hyperref[subsec:start_pes]{\FuncRef{start\_pes}} & 1.2 & Current & \hyperref[subsec:shmem_init]{\FUNC{shmem\_init}} \\ \hline
    \Fortran: \hyperref[subsec:start_pes]{\FuncRef{START\_PES}} & 1.2 & 1.4 & \hyperref[subsec:shmem_init]{\FUNC{SHMEM\_INIT}} \\ \hline
    \hyperref[subsec:start_pes]{Implicit finalization} & 1.2 & Current & \hyperref[subsec:shmem_finalize]{\FUNC{shmem\_finalize}} \\ \hline
    \CorCpp: \FuncRef{\_my\_pe} & 1.2 & Current & \hyperref[subsec:shmem_my_pe]{\FUNC{shmem\_my\_pe}} \\ \hline
    \CorCpp: \FuncRef{\_num\_pes} & 1.2 & Current & \hyperref[subsec:shmem_n_pes]{\FUNC{shmem\_n\_pes}} \\ \hline
    \Fortran: \FuncRef{MY\_PE} & 1.2 & 1.4 & \hyperref[subsec:shmem_my_pe]{\FUNC{SHMEM\_MY\_PE}} \\ \hline
    \Fortran: \FuncRef{NUM\_PES} & 1.2 & 1.4 & \hyperref[subsec:shmem_n_pes]{\FUNC{SHMEM\_N\_PES}} \\ \hline
    \CorCpp: \FuncRef{shmalloc} & 1.2 & Current & \hyperref[sec:memory_management]{\FUNC{shmem\_malloc}} \\ \hline
    \CorCpp: \FuncRef{shfree} & 1.2 & Current & \hyperref[sec:memory_management]{\FUNC{shmem\_free}} \\ \hline
    \CorCpp: \FuncRef{shrealloc} & 1.2 & Current & \hyperref[sec:memory_management]{\FUNC{shmem\_realloc}} \\ \hline
    \CorCpp: \FuncRef{shmemalign} & 1.2 & Current & \hyperref[sec:memory_management]{\FUNC{shmem\_align}} \\ \hline
    \Fortran: \FuncRef{SHMEM\_PUT} & 1.2 & 1.4 & \hyperref[subsec:shmem_put]{\FUNC{SHMEM\_PUT8} or \FUNC{SHMEM\_PUT64}} \\ \hline
    %% Deprecated in 1.3
    \minitab{
        \CorCpp: \FuncRef{shmem\_clear\_cache\_inv}
        \\ \CorCpp: \FuncRef{shmem\_clear\_cache\_line\_inv}
        \\ \CorCpp: \FuncRef{shmem\_set\_cache\_inv}
        \\ \CorCpp: \FuncRef{shmem\_set\_cache\_line\_inv}
        \\ \CorCpp: \FuncRef{shmem\_udcflush}
        \\ \CorCpp: \FuncRef{shmem\_udcflush\_line}
        } & 1.3 & 1.4 & (none) \\ \hline
    \minitab{
        \Fortran: \FuncRef{SHMEM\_CLEAR\_CACHE\_INV}
        %% Note: At the time of deprecation, the Fortran API did not specify
        %% SHMEM_CLEAR_CACHE_LINE_INV. While this omission is certainly an error,
        %% Fortran was removed in 1.5 so the omission was never corrected.
        \\ \Fortran: \FuncRef{SHMEM\_SET\_CACHE\_INV}
        \\ \Fortran: \FuncRef{SHMEM\_SET\_CACHE\_LINE\_INV}
        \\ \Fortran: \FuncRef{SHMEM\_UDCFLUSH}
        \\ \Fortran: \FuncRef{SHMEM\_UDCFLUSH\_LINE}
        } & 1.3 & 1.4 & (none) \\ \hline
    \LibConstRef{\_SHMEM\_SYNC\_VALUE}         & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_SYNC\_VALUE}} \\ \hline
    \LibConstRef{\_SHMEM\_BARRIER\_SYNC\_SIZE} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_BARRIER\_SYNC\_SIZE}} \\ \hline
    \LibConstRef{\_SHMEM\_BCAST\_SYNC\_SIZE}   & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_BCAST\_SYNC\_SIZE}} \\ \hline
    \LibConstRef{\_SHMEM\_COLLECT\_SYNC\_SIZE} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_COLLECT\_SYNC\_SIZE}} \\ \hline
    \LibConstRef{\_SHMEM\_REDUCE\_SYNC\_SIZE}  & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_REDUCE\_SYNC\_SIZE}} \\ \hline
    \LibConstRef{\_SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE}} \\ \hline
    \LibConstRef{\_SHMEM\_MAJOR\_VERSION} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_MAJOR\_VERSION}} \\ \hline
    \LibConstRef{\_SHMEM\_MINOR\_VERSION} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_MINOR\_VERSION}} \\ \hline
    \LibConstRef{\_SHMEM\_MAX\_NAME\_LEN} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_MAX\_NAME\_LEN}} \\ \hline
    \LibConstRef{\_SHMEM\_VENDOR\_STRING} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_VENDOR\_STRING}} \\ \hline
    \LibConstRef{\_SHMEM\_CMP\_EQ} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_CMP\_EQ}} \\ \hline
    \LibConstRef{\_SHMEM\_CMP\_NE} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_CMP\_NE}} \\ \hline
    \LibConstRef{\_SHMEM\_CMP\_LT} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_CMP\_LT}} \\ \hline
    \LibConstRef{\_SHMEM\_CMP\_LE} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_CMP\_LE}} \\ \hline
    \LibConstRef{\_SHMEM\_CMP\_GT} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_CMP\_GT}} \\ \hline
    \LibConstRef{\_SHMEM\_CMP\_GE} & 1.3 & Current & \hyperref[subsec:library_constants]{\CONST{SHMEM\_CMP\_GE}} \\ \hline
    %% Deprecated in 1.4
    \EnvVarRef{SMA\_VERSION}         & 1.4 & Current & \hyperref[subsec:environment_variables]{\ENVVAR{SHMEM\_VERSION}} \\ \hline
    \EnvVarRef{SMA\_INFO}            & 1.4 & Current & \hyperref[subsec:environment_variables]{\ENVVAR{SHMEM\_INFO}} \\ \hline
    \EnvVarRef{SMA\_SYMMETRIC\_SIZE} & 1.4 & Current & \hyperref[subsec:environment_variables]{\ENVVAR{SHMEM\_SYMMETRIC\_SIZE}} \\ \hline
    \EnvVarRef{SMA\_DEBUG}           & 1.4 & Current & \hyperref[subsec:environment_variables]{\ENVVAR{SHMEM\_DEBUG}} \\ \hline
    \minitab{\CorCpp: \FuncRef{shmem\_wait}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_wait}}
        & 1.4 & Current & See \textbf{Notes} for \hyperref[subsec:shmem_wait_until]{\FUNC{shmem\_wait\_until}} \\ \hline
    \CorCpp: \FuncRef{shmem\_wait\_until} & 1.4 & Current
        & \Cstd[11]: \hyperref[subsec:shmem_wait_until]{\FUNC{shmem\_wait\_until}}, \CorCpp: \hyperref[subsec:shmem_wait_until]{\FUNC{shmem\_long\_wait\_until}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_fetch}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_fetch}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_fetch]{\FUNC{shmem\_atomic\_fetch}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_set}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_set}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_set]{\FUNC{shmem\_atomic\_set}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_cswap}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_cswap}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_compare_swap]{\FUNC{shmem\_atomic\_compare\_swap}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_swap}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_swap}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_swap]{\FUNC{shmem\_atomic\_swap}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_finc}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_finc}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_fetch_inc]{\FUNC{shmem\_atomic\_fetch\_inc}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_inc}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_inc}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_inc]{\FUNC{shmem\_atomic\_inc}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_fadd}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_fadd}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_fetch_add]{\FUNC{shmem\_atomic\_fetch\_add}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_add}
        \\ \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_add}}
        & 1.4 & Current & \hyperref[subsec:shmem_atomic_add]{\FUNC{shmem\_atomic\_add}} \\ \hline
    Entire \Fortran \ac{API} & 1.4 & 1.4 & \openshmem \Cstd \ac{API} through \Fortran--\Cstd interoperability \\ \hline
    %% Deprecated in 1.5
    \minitab{
        \LibConstRef{SHMEM\_SYNC\_VALUE}
        \\ \LibConstRef{SHMEM\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_BARRIER\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_ALLTOALL\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_ALLTOALLS\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_BCAST\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_COLLECT\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_REDUCE\_SYNC\_SIZE}
        \\ \LibConstRef{SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE}
    } & 1.5 & Current & Team-based collectives, \minitab{Section~\ref{subsec:team_collectives}}. \\ \hline
    \CorCpp: Active-set-based \FuncRef{shmem\_sync}
        & 1.5 & Current & Team-based \hyperref[subsec:shmem_sync]{\FUNC{shmem\_sync}} \\ \hline
    \CorCpp: \FuncRef{shmem\_alltoall\{32, 64\}} & 1.5 & Current &
    \hyperref[subsec:shmem_alltoall]{\FUNC{shmem\_alltoall}} \\ \hline
    \CorCpp: \FuncRef{shmem\_alltoalls\{32, 64\}} & 1.5 & Current &
    \hyperref[subsec:shmem_alltoalls]{\FUNC{shmem\_alltoalls}} \\ \hline
    \CorCpp: \FuncRef{shmem\_broadcast\{32, 64\}} & 1.5 & Current &
    \hyperref[subsec:shmem_broadcast]{\FUNC{shmem\_broadcast}} \\ \hline
    \CorCpp: \FuncRef{shmem\_collect\{32, 64\}} & 1.5 & Current &
    \hyperref[subsec:shmem_collect]{\FUNC{shmem\_collect}} \\ \hline
    \CorCpp: \FuncRef{shmem\_fcollect\{32, 64\}} & 1.5 & Current &
    \hyperref[subsec:shmem_collect]{\FUNC{shmem\_fcollect}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_and\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_and_reduce]{\FUNC{shmem\_and\_reduce}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_or\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_or_reduce]{\FUNC{shmem\_or\_reduce}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_xor\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_xor_reduce]{\FUNC{shmem\_xor\_reduce}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_max\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_max_reduce]{\FUNC{shmem\_max\_reduce}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_min\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_min_reduce]{\FUNC{shmem\_min\_reduce}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_sum\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_sum_reduce]{\FUNC{shmem\_sum\_reduce}} \\ \hline
    \CorCpp: \FuncRef{shmem\_\FuncParam{TYPENAME}\_prod\_to\_all}
        & 1.5 & Current & \hyperref[subsec:shmem_prod_reduce]{\FUNC{shmem\_prod\_reduce}} \\ \hline
    \CorCpp: \hyperref[subsec:shmem_barrier]{\FuncRef{shmem\_barrier}}
        & 1.5 & Current & \hyperref[subsec:shmem_quiet]{\FuncRef{shmem\_quiet}} + \hyperref[subsec:shmem_sync]{\FuncRef{shmem\_sync}} \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_wait\_until(\CTYPE{short} ...)}
        \\ \CorCpp: \FuncRef{shmem\_short\_wait\_until}}
        & 1.5 & Current & (none) \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_wait\_until(\CTYPE{unsigned short} ...)}
        \\ \CorCpp: \FuncRef{shmem\_ushort\_wait\_until}}
        & 1.5 & Current & (none) \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_test(\CTYPE{short} ...)}
        \\ \CorCpp: \FuncRef{shmem\_short\_test}}
        & 1.5 & Current & (none) \\ \hline
    \minitab{\Cstd[11]: \FuncRef{shmem\_test(\CTYPE{unsigned short} ...)}
        \\ \CorCpp: \FuncRef{shmem\_ushort\_test}}
        & 1.5 & Current & (none) \\ \hline
    \minitab{Table~\ref{p2psynctypes}: point-to-point synchronization types}
        & 1.5 & Current & Table~\ref{stdamotypes}: standard \ac{AMO} types \\ \hline
    %% Deprecated in 1.6
    %% Deprecated in 1.7
    %% Notes
    %% - If a hyperref spans more than one line vertically, the clickable box
    %%   will also span more than one line. To prevent this, wrap the hyperref
    %%   in a minitab. Example in 1.5: "Team-based collectives".
    \end{longtable}
\end{center}

\section{Deprecation Rationale}\label{dep:rationale}

\subsection{Header Directory: \HEADER{mpp}}
\label{dep:mpp_header}
In addition to the default system header paths, \openshmem implementations
must provide all \openshmem-specified header files from the \HEADER{mpp}
header directory such that these headers can be referenced in \CorCpp as
\begin{lstlisting}[language=]
#include <mpp/shmem.h>
#include <mpp/shmemx.h>
\end{lstlisting}
and in \Fortran as
\begin{lstlisting}[language=]
include 'mpp/shmem.fh'
include 'mpp/shmemx.fh'
\end{lstlisting}
for backwards compatibility with \ac{SGI} SHMEM.

\subsection{\CorCpp: \FUNC{start\_pes}}
\label{dep:start_pes}
The \CorCpp routine \FUNC{start\_pes} includes an unnecessary initialization
argument that is remnant of historical \emph{SHMEM} implementations and no
longer reflects the requirements of modern \openshmem implementations.
Furthermore, the naming of \FUNC{start\_pes} does not include the standardized
\shmemprefixLC{} naming prefix. This routine has been deprecated and
\openshmem users are encouraged to use \FUNC{shmem\_init} instead.

\subsection{Implicit Finalization}
Implicit finalization was deprecated and replaced with explicit finalization using the
\FUNC{shmem\_finalize} routine.  Explicit finalization improves portability and
also improves interoperability with profiling and debugging tools.

\subsection{\CorCpp: \FUNC{\_my\_pe}, \FUNC{\_num\_pes}, \FUNC{shmalloc},
    \FUNC{shfree}, \FUNC{shrealloc}, \FUNC{shmemalign}}
\label{dep:func_not_shmemunder}
The \CorCpp routines \FUNC{\_my\_pe}, \FUNC{\_num\_pes}, \FUNC{shmalloc},
\FUNC{shfree}, \FUNC{shrealloc}, and \FUNC{shmemalign} were deprecated in order
to normalize the \openshmem \ac{API} to use \shmemprefixLC{} as the standard
prefix for all routines.

\subsection{\textit{Fortran}: \FUNC{START\_PES}, \FUNC{MY\_PE}, \FUNC{NUM\_PES}} %% WARNING: Issue #66.
The \Fortran routines \FUNC{START\_PES}, \FUNC{MY\_PE}, and \FUNC{NUM\_PES}
were deprecated in order to minimize the \ac{API} differences from the deprecation
of \CorCpp routines \FUNC{start\_pes}, \FUNC{\_my\_pe}, and \FUNC{\_num\_pes}.

\subsection{\textit{Fortran}: \FUNC{SHMEM\_PUT}} %% WARNING: Issue #66.
\label{dep:fortran_shmem_put}
The \Fortran routine \FUNC{SHMEM\_PUT} is defined only for the \Fortran
\ac{API} and is semantically identical to \Fortran routines
\FUNC{SHMEM\_PUT8} and \FUNC{SHMEM\_PUT64}.  Since \FUNC{SHMEM\_PUT8} and
\FUNC{SHMEM\_PUT64} have defined equivalents in the \CorCpp interface,
\FUNC{SHMEM\_PUT} is ambiguous and has been deprecated.

\subsection{SHMEM\_CACHE}
\label{dep:shmem_cache}
The \FUNC{SHMEM\_CACHE} \ac{API}
\begin{center}
\begin{tabular}{ll}
    \CorCpp: & \Fortran: \\
    \FUNC{shmem\_clear\_cache\_inv}     & \FUNC{SHMEM\_CLEAR\_CACHE\_INV} \\
    \FUNC{shmem\_set\_cache\_inv}       & \FUNC{SHMEM\_SET\_CACHE\_INV} \\
    \FUNC{shmem\_set\_cache\_line\_inv} & \FUNC{SHMEM\_SET\_CACHE\_LINE\_INV} \\
    \FUNC{shmem\_udcflush}              & \FUNC{SHMEM\_UDCFLUSH} \\
    \FUNC{shmem\_udcflush\_line}        & \FUNC{SHMEM\_UDCFLUSH\_LINE} \\
    \FUNC{shmem\_clear\_cache\_line\_inv} \\
\end{tabular}
\end{center}
was originally implemented for systems with cache-management instructions.
This \ac{API} has largely gone unused on cache-coherent system architectures.
\FUNC{SHMEM\_CACHE} has been deprecated.

\subsection{\CONST{\_SHMEM\_*} Library Constants}
\label{dep:libconst_undershmem}
The library constants
\begin{center}
\begin{tabular}{ll}
    \CONST{\_SHMEM\_SYNC\_VALUE}         & \CONST{\_SHMEM\_MAX\_NAME\_LEN} \\
    \CONST{\_SHMEM\_BARRIER\_SYNC\_SIZE} & \CONST{\_SHMEM\_VENDOR\_STRING} \\
    \CONST{\_SHMEM\_BCAST\_SYNC\_SIZE}   & \CONST{\_SHMEM\_CMP\_EQ} \\
    \CONST{\_SHMEM\_COLLECT\_SYNC\_SIZE} & \CONST{\_SHMEM\_CMP\_NE} \\
    \CONST{\_SHMEM\_REDUCE\_SYNC\_SIZE}  & \CONST{\_SHMEM\_CMP\_LT} \\
    \CONST{\_SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE} & \CONST{\_SHMEM\_CMP\_LE} \\
    \CONST{\_SHMEM\_MAJOR\_VERSION}      & \CONST{\_SHMEM\_CMP\_GT} \\
    \CONST{\_SHMEM\_MINOR\_VERSION}      & \CONST{\_SHMEM\_CMP\_GE} \\
\end{tabular}
\end{center}
do not adhere to the \Cstd standard's reserved identifiers and the \Cpp
standard's reserved names.  These constants were deprecated and replaced
with corresponding constants of prefix \shmemprefix{} that adhere to \CorCpp{}
and \Fortran naming conventions.

\subsection{\ENVVAR{SMA\_*} Environment Variables}
\label{dep:envvar_sma}
The environment variables \ENVVAR{SMA\_VERSION}, \ENVVAR{SMA\_INFO},
\ENVVAR{SMA\_SYMMETRIC\_SIZE}, and \ENVVAR{SMA\_DEBUG}
were deprecated in order to normalize the \openshmem \ac{API} to use
\shmemprefix{} as the standard prefix for all environment variables.

\subsection{\CorCpp: \FUNC{shmem\_wait}}
\label{dep:shmem_wait}
The \CorCpp interface for \FUNC{shmem\_wait} and \FUNC{shmem\_\FuncParam{TYPENAME}\_wait}
was identified as unintuitive with respect to
the comparison operation it performed.  As \FUNC{shmem\_wait} can be trivially
replaced by \FUNC{shmem\_wait\_until} where \VAR{cmp} is
\CONST{SHMEM\_CMP\_NE}, the \FUNC{shmem\_wait} interface was deprecated in
favor of \FUNC{shmem\_wait\_until}, which makes the comparison operation
explicit and better communicates the developer's intent.

\subsection{\CorCpp: \FUNC{shmem\_wait\_until}}
\label{dep:long_typed_shmem_wait_until}
The \CTYPE{long}-typed \CorCpp routine \FUNC{shmem\_wait\_until} was deprecated
in favor of the \Cstd[11] type-generic interface of the same name or the
explicitly typed \CorCpp routine \FUNC{shmem\_long\_wait\_until}.

\subsection{\textit{C11} and \CorCpp: \FUNC{shmem\_fetch}, \FUNC{shmem\_set}, %% Issue #66.
    \FUNC{shmem\_cswap}, \FUNC{shmem\_swap}, \FUNC{shmem\_finc},
    \FUNC{shmem\_inc}, \FUNC{shmem\_fadd}, \FUNC{shmem\_add}}
\label{dep:amo_not_shmem_atomic}
The \Cstd[11] and \CorCpp interfaces for
\begin{center}
\begin{tabular}{ll}
    \Cstd[11]: & \CorCpp: \\
    \FUNC{shmem\_fetch} & \FUNC{shmem\_\FuncParam{TYPENAME}\_fetch} \\
    \FUNC{shmem\_set}   & \FUNC{shmem\_\FuncParam{TYPENAME}\_set}   \\
    \FUNC{shmem\_cswap} & \FUNC{shmem\_\FuncParam{TYPENAME}\_cswap} \\
    \FUNC{shmem\_swap}  & \FUNC{shmem\_\FuncParam{TYPENAME}\_swap}  \\
    \FUNC{shmem\_finc}  & \FUNC{shmem\_\FuncParam{TYPENAME}\_finc}  \\
    \FUNC{shmem\_inc}   & \FUNC{shmem\_\FuncParam{TYPENAME}\_inc}   \\
    \FUNC{shmem\_fadd}  & \FUNC{shmem\_\FuncParam{TYPENAME}\_fadd}  \\
    \FUNC{shmem\_add}   & \FUNC{shmem\_\FuncParam{TYPENAME}\_add}   \\
\end{tabular}
\end{center}
were deprecated and replaced with
similarly named interfaces within the \FUNC{shmem\_atomic\_*} namespace
in order to more clearly identify these calls as performing atomic operations.
In addition, the abbreviated names ``cswap'', ``finc'', and ``fadd'' were
expanded for clarity to ``compare\_swap'', ``fetch\_inc'', and ``fetch\_add''.

\subsection{\textit{Fortran} API} %% WARNING: Issue #66.
\label{dep:fortran}
The entire \openshmem \Fortran \ac{API} was deprecated in \openshmem[1.4] and
removed in \openshmem[1.5] because of a general lack of
use and a lack of conformance with legacy \Fortran standards. In lieu of an
extensive update of the \Fortran \ac{API}, \Fortran users are encouraged to
leverage the \openshmem Specification's \Cstd \ac{API} through the
\Fortran--\Cstd interoperability initially standardized by \Fortran[2003]%
\footnote{Formally, \Fortran[2003] is known as ISO/IEC~1539-1:2004(E).}.


\subsection{Active-set-based library constants and collectives}
\label{dep:active_set_libconst_and_collectives}
With the addition of \openshmem teams, Section~\ref{subsec:team}, the previous
method for performing collective
operations has been superseded by a more readable, flexible method for
organizing and communicating between groups of \acp{PE}. All collective routines
which previously indicated subgroups of \acp{PE} with a list of
parameters to describe the subgroup composition (active set) should be phased
out in favor of using collective operations with a team parameter.

The library constants
\begin{center}
\begin{tabular}{ll}
    \LibConstRef{SHMEM\_SYNC\_VALUE}            & \LibConstRef{SHMEM\_BCAST\_SYNC\_SIZE} \\
    \LibConstRef{SHMEM\_SYNC\_SIZE}             & \LibConstRef{SHMEM\_COLLECT\_SYNC\_SIZE} \\
    \LibConstRef{SHMEM\_BARRIER\_SYNC\_SIZE}    & \LibConstRef{SHMEM\_REDUCE\_SYNC\_SIZE} \\
    \LibConstRef{SHMEM\_ALLTOALL\_SYNC\_SIZE}   & \LibConstRef{SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE} \\
    \LibConstRef{SHMEM\_ALLTOALLS\_SYNC\_SIZE} \\
\end{tabular}
\end{center}
were deprecated as these constants pertain only to active-set-based collectives.

The \CorCpp active-set-based \FuncRef{shmem\_sync} routine was deprecated and
replaced with the team-based \Cstd[11] \FuncRef{shmem\_sync} or \CorCpp
\FuncRef{shmem\_team\_sync} routine.

The fixed-sized versions of the active-set-based routines
\begin{center}
\begin{tabular}{ll}
    \FuncRef{shmem\_alltoall32} & \FuncRef{shmem\_alltoall64} \\
    \FuncRef{shmem\_alltoalls32} & \FuncRef{shmem\_alltoalls64} \\
    \FuncRef{shmem\_broadcast32} & \FuncRef{shmem\_broadcast64} \\
    \FuncRef{shmem\_collect32} & \FuncRef{shmem\_collect64} \\
    \FuncRef{shmem\_fcollect32} & \FuncRef{shmem\_fcollect64} \\
\end{tabular}
\end{center}
were deprecated. Instead, all team-based collective routines use standard
\Cstd types with the option to use generic \Cstd[11] functions for more portable
and maintainable implementations.

The active-set-based reduction routines
\begin{center}
\begin{tabular}{ll}
    \FuncRef{shmem\_\FuncParam{TYPENAME}\_and\_to\_all} & \FuncRef{shmem\_\FuncParam{TYPENAME}\_max\_to\_all} \\
    \FuncRef{shmem\_\FuncParam{TYPENAME}\_or\_to\_all}  & \FuncRef{shmem\_\FuncParam{TYPENAME}\_min\_to\_all} \\
    \FuncRef{shmem\_\FuncParam{TYPENAME}\_xor\_to\_all} & \FuncRef{shmem\_\FuncParam{TYPENAME}\_sum\_to\_all} \\
                                                        & \FuncRef{shmem\_\FuncParam{TYPENAME}\_prod\_to\_all} \\
\end{tabular}
\end{center}
were deprecated and replaced with team-based reduction routines.


\subsection{\CorCpp: \FUNC{shmem\_barrier}}
\label{dep:shmem_barrier}
Each \openshmem team might
be associated with some number of communication contexts. The \FUNC{shmem\_barrier}
function implies that the default context is quiesced after synchronizing
some active set of \acp{PE}. Since teams may have some number of contexts associated
with the team, it becomes less clear which context would be the ``default'' context
for that particular team. Rather than continue to support \FUNC{shmem\_barrier}
for active-sets or teams, programs should use a call to \FUNC{shmem\_quiet}
followed by a call to \FUNC{shmem\_sync} in order to explicitly
indicate which context to quiesce.

\subsection{\textit{C11} and \CorCpp: \CTYPE{short} and \CTYPE{unsigned short} variants of \FUNC{shmem\_wait\_until} and \FUNC{shmem\_test}}
\label{dep:short_ushort_typed_shmem_wait_until_and_test}
The \CTYPE{short} and \CTYPE{unsigned short} type \CorCpp and \textit{C11}
routines for \FUNC{shmem\_wait\_until} and \FUNC{shmem\_test} were deprecated
because point-to-point synchronization routines are only compatible with
\acp{AMO} (as of \openshmem 1.5), and there is no corresponding \ac{AMO} for
\CTYPE{short} and \CTYPE{unsigned short}.

\subsection{Table~\ref{p2psynctypes}: point-to-point synchronization types}
\label{dep:p2p_sync_types}
As of \openshmem 1.5, the point-to-point synchronization routines are only
compatible with \acp{AMO}, so their interfaces are defined via the
standard \ac{AMO} types in Table~\ref{stdamotypes}.


%%
%% For section headings, use \textit{Fortran} instead of \Fortran.
%% Do not use commands that take optional arguments (e.g., \Fortran, \Cstd)
%% because they do not render at all in the PDF bookmarks.
%%
%% See Issue #66 for details.
%%


\chapter{Changes to this Document}\label{sec:changelog}

\section{Version 1.6}
\label{changelog:v1.6}
Major changes in \openshmem[1.6] include the addition of the new
\FUNC{shmem\_team\_ptr}, \FUNC{shmem\_ibget}, and \FUNC{shmem\_ibput}
functions.

The following list describes the specific changes in \openshmem[1.6]:
\begin{enumerate}
%
\item Added an inclusive (\FUNC{shmem\_sum\_inscan}) and exclusive 
(\FUNC{shmem\_sum\_exscan}) collective summation operation. 
\ChangelogRef{subsec:shmem_scan}
%
\item Added support for initialization and finalization routines to be called
    multiple times, and added an initialization status query API
    \FUNC{shmem\_query\_initialized}.
\ChangelogRef{subsec:shmem_init, subsec:shmem_finalize, subsec:shmem_query_initialized}%
%
\item Added interleaved block transfer APIs \FUNC{shmem\_ibget} and
    \FUNC{shmem\_ibput}.
\ChangelogRef{subsec:shmem_ibget, subsec:shmem_ibput}%
%
\item Added \FUNC{shmem\_signal\_add} and \FUNC{shmem\_signal\_set} to
  update a remote flag without associated data transfer of a put-with-signal operation.
\ChangelogRef{subsec:shmem_signal_add, subsec:shmem_signal_set}%
%
\item Added a team-based pointer query routine:
  \FUNC{shmem\_team\_ptr}.
\ChangelogRef{subsec:shmem_team_ptr}%
%
\item Clarified that the behavior of \FUNC{shmem\_team\_split\_strided} is
    undefined when the input \VAR{start}, \VAR{stride}, and \VAR{size} arguments
    imply a \textit{wrap-around} with respect to the parent team's \acp{PE}.
\ChangelogRef{subsec:shmem_team_split_strided}%
%
\item Added the session routines, \FUNC{shmem\_ctx\_session\_start} and
    \FUNC{shmem\_ctx\_session\_stop}, which allow users to pass hints to the
    \openshmem library to apply runtime optimizations.
\ChangelogRef{subsec:sessions}%
\item Added fine grained completion routine: \FUNC{shmem\_pe\_quiet}.
\ChangelogRef{subsec:shmem_pe_quiet}%
%
\item Split the listings for the \FUNC{shmem\_\{malloc, free, realloc, align\}}
  functions from a single entry in \openshmem[1.5] into separate entries.
\ChangelogRef{subsec:shmem_malloc, subsec:shmem_free, subsec:shmem_realloc,
  subsec:shmem_align}%
%
\item Clarified that the \FUNC{shmem\_\{malloc, free, realloc, align,
    malloc\_with\_hints, calloc\}} functions are collective operations on
    the world team.
\ChangelogRef{subsec:shmem_malloc, subsec:shmem_free, subsec:shmem_realloc,
  subsec:shmem_align, subsec:shmmallochint, subsec:shmem_calloc}%
%
\item Clarified that \FUNC{shmem\_team\_get\_config} returns the current
    configuration values, which may differ from the values assigned at the
        time of the team's creation.
\ChangelogRef{subsec:shmem_team_get_config}
%
\item Clarified the behavior of \FUNC{shmem\_team\_get\_config} when the
    \VAR{config\_mask} is 0 and/or the \VAR{config} argument is a null pointer.
\ChangelogRef{subsec:shmem_team_get_config}
%
\item Clarified the behavior of \FUNC{shmem\_team\_split\_strided} when the
    stride argument is 0 or negative.
\ChangelogRef{subsec:shmem_team_split_strided}
%
\item Clarified the requirements for the source buffer before entering the
    collective routines.
\ChangelogRef{subsec:shmem_alltoall,subsec:shmem_broadcast,subsec:shmem_collect,subsec:shmem_reductions,subsec:shmem_scan}
%
\item Added a new Errata Section~\ref{sec:errata} that indicates errors or ambiguities in the
    \openshmem specification and the version that required correction or clarification.
\ChangelogRef{sec:errata}
%
\item Removed \openshmem[1.5] Table 9, which was an incomplete duplicate of
    \openshmem[1.5] Table 10, and clarified the types, names, and supporting
    operations for team-based reductions. \label{changelog:reduction_table}
\ChangelogRef{teamreducetypes}%
%
\item Clarified that \VAR{source} and \VAR{dest} arrays must be the same
    across \acp{PE} in \openshmem reductions \label{changelog:reduction_args}
\ChangelogRef{subsec:shmem_reductions}
%
\item Clarified that \OPR{Fence} operations only guarantee ordering for
    operations that are performed on the same context. \label{changelog:fence_ctx}
\ChangelogRef{subsec:shmem_fence}%
%
\item Clarified that \FUNC{shmem\_test\_all} and \FUNC{shmem\_test\_all\_vector}
    routines return 1 when the test set is empty. \label{changelog:test_all}
\ChangelogRef{subsec:shmem_test_all,subsec:shmem_test_all_vector}%
%
\item Clarified that \FUNC{shmem\_team\_split\_strided} and
    \FUNC{shmem\_team\_split\_strided} return a nonzero value when the parent
        team compares equal to \LibConstRef{SHMEM\_TEAM\_INVALID}. \label{changelog:split_strided_2d}
\ChangelogRef{subsec:shmem_team_split_strided, subsec:shmem_team_split_2d}%
%
\item Corrected the level argument's recommended value in API notes for
    \FUNC{shmem\_pcontrol} to indicate that the value should be greater than
    2 to enable profiling with profile library defined effects and
    additional arguments. \label{changelog:pcontrol}
\ChangelogRef{subsec:shmem_pcontrol}
%
\item Added a \texttt{const} qualifier to the \VAR{cmp\_values} argument in the
    following point-to-point synchronization routines:
    \FUNC{shmem\_wait\_until\_all\_vector},
    \FUNC{shmem\_wait\_until\_any\_vector},
    \FUNC{shmem\_wait\_until\_some\_vector},
    \FUNC{shmem\_test\_all\_vector}, \FUNC{shmem\_test\_any\_vector}, and
    \FUNC{shmem\_test\_some\_vector}. \label{changelog:p2p_vector_const}
\ChangelogRef{
  subsec:shmem_wait_until_all_vector,
  subsec:shmem_wait_until_any_vector,
  subsec:shmem_wait_until_some_vector,
  subsec:shmem_test_all_vector,
  subsec:shmem_test_any_vector,
  subsec:shmem_test_some_vector}%
%

\end{enumerate}

\section{Version 1.5}
Major changes in \openshmem[1.5] include the addition of new team-based
collective functions, \OPR{put-with-signal} functions, nonblocking \ac{AMO}
functions, multiple-element point-to-point synchronization and vector
comparison functions, a \FUNC{shmem\_malloc\_with\_hints} function, a profiling
interface, and the removal of the entire \Fortran \ac{API}.

The following list describes the specific changes in \openshmem[1.5]:
\begin{enumerate}
%
\item Removed \FUNC{SHMEM\_CACHE}.
\ChangelogRef{dep:shmem_cache}%
%
\item Deprecated \CTYPE{short} and \CTYPE{unsigned short} variants for
\FUNC{shmem\_wait\_until} and \FUNC{shmem\_test}.
\ChangelogRef{
  subsec:shmem_wait_until,
  subsec:shmem_test,
  dep:short_ushort_typed_shmem_wait_until_and_test}%
%
\item Added \FUNC{shmem\_malloc\_with\_hints} interface and corresponding hints
\CONST{SHMEM\_MALLOC\_ATOMICS\_REMOTE} and \CONST{SHMEM\_MALLOC\_SIGNAL\_REMOTE}.
\ChangelogRef{subsec:shmmallochint, subsec:library_constants}%
%
\item Specified that team-based broadcast operations update the \VAR{dest} object on
all \acp{PE}, including the root \ac{PE}.
\ChangelogRef{subsec:shmem_broadcast}%
%
\item Deprecated active-set-based library constants and collective functions.
\ChangelogRef{
  subsec:library_constants,
  subsec:coll,
  dep:active_set_libconst_and_collectives,
  dep:shmem_barrier}%
%
\item Added team management functions:
  \FUNC{shmem\_team\_my\_pe},
  \FUNC{shmem\_team\_n\_pes},
  \FUNC{shmem\_team\_get\_config}, \\
  \FUNC{shmem\_team\_translate\_pe},
  \FUNC{shmem\_team\_split\_strided},
  \FUNC{shmem\_team\_split\_2d}, and
  \FUNC{shmem\_team\_destroy}.
\ChangelogRef{
  subsec:shmem_team_my_pe,
  subsec:shmem_team_n_pes,
  subsec:shmem_team_get_config,
  subsec:shmem_team_translate_pe,
  subsec:shmem_team_split_strided,
  subsec:shmem_team_split_2d,
  subsec:shmem_team_destroy}%
%
\item Added team-based communication-management functions:
  \FUNC{shmem\_team\_create\_ctx} and \\
  \FUNC{shmem\_ctx\_get\_team}.
\ChangelogRef{
  subsec:shmem_team_create_ctx,
  subsec:shmem_ctx_get_team}%
%
\item Added team-based collective functions: \FUNC{shmem\_sync},
  \FUNC{shmem\_alltoall[mem]}, \FUNC{shmem\_alltoalls[mem]}, \\
  \FUNC{shmem\_broadcast[mem]}, \FUNC{shmem\_collect[mem]}, \FUNC{shmem\_fcollect[mem]}, and \\
  \FUNC{shmem\_\{and, or, xor, max, min, sum, prod\}\_reduce}.
\ChangelogRef{
  subsec:shmem_sync,
  subsec:shmem_alltoall,
  subsec:shmem_alltoalls,
  subsec:shmem_broadcast,
  subsec:shmem_collect,
  subsec:shmem_reductions}%
%
\item Clarified interoperability of \openshmem with other programming models.
\ChangelogRef{sec:interoperability}%
%
\item Clarified restrictions on using pointers to symmetric objects.
\ChangelogRef{
  subsec:pointers_to_symmetric_objects,
  subsec:invoking_openshmem_operations}%
%
\item Added support for nonblocking \ac{AMO} functions.
\ChangelogRef{subsec:amo_nbi}%
%
\item Added support for blocking \OPR{put-with-signal} functions.
\ChangelogRef{subsec:shmem_put_signal}%
%
\item Added support for nonblocking \OPR{put-with-signal} functions.
\ChangelogRef{subsec:shmem_put_signal_nbi}%
%
\item Deprecated point-to-point synchronization types and names.
\ChangelogRef{p2psynctypes, dep:p2p_sync_types}%
%
\item Clarified that point-to-point synchronization routines preserve the
  atomicity of \openshmem \acp{AMO}.
\ChangelogRef{subsec:amo_guarantees}%
%
\item Clarified that symmetric variables used as \VAR{ivar} arguments to
  point-to-point synchronization routines must be updated using \openshmem
  \acp{AMO}.
\ChangelogRef{subsec:p2p_intro}%
%
\item Removed the entire \openshmem \Fortran \ac{API}.
\ChangelogRef{dep:fortran}%
%
\item Added support for multipliers in \VAR{SHMEM\_SYMMETRIC\_SIZE}
environment variables.
\ChangelogRef{subsec:environment_variables}%
%
\item Added support for a multiple-element point-to-point synchronization \ac{API} with
  the functions: \FUNC{shmem\_wait\_until\_all}, \FUNC{shmem\_wait\_until\_any},
  \FUNC{shmem\_wait\_until\_some}, \FUNC{shmem\_test\_all},
  \FUNC{shmem\_test\_any}, and \FUNC{shmem\_test\_some}.
\ChangelogRef{
  subsec:shmem_wait_until_all,
  subsec:shmem_wait_until_any,
  subsec:shmem_wait_until_some,
  subsec:shmem_test_all,
  subsec:shmem_test_any,
  subsec:shmem_test_some}%
%
\item Added support for vectorized comparison values in the multiple-element
  point-to-point synchronization \ac{API} with the functions:
  \FUNC{shmem\_wait\_until\_all\_vector}, \FUNC{shmem\_wait\_until\_any\_vector},
  \FUNC{shmem\_wait\_until\_some\_vector},
  \FUNC{shmem\_test\_all\_vector}, \FUNC{shmem\_test\_any\_vector}, and
  \FUNC{shmem\_test\_some\_vector}.
\ChangelogRef{
  subsec:shmem_wait_until_all_vector,
  subsec:shmem_wait_until_any_vector,
  subsec:shmem_wait_until_some_vector,
  subsec:shmem_test_all_vector,
  subsec:shmem_test_any_vector,
  subsec:shmem_test_some_vector}%
%
\item Added \openshmem profiling interface.
\ChangelogRef{sec:openshmem_profiling_interface}%
%
\item Specified the validity of communication contexts, added the constant
  \CONST{SHMEM\_CTX\_INVALID}, and clarified the behavior of
  \FUNC{shmem\_ctx\_*} routines on invalid contexts.
\ChangelogRef{sec:ctx}%
%
\item Clarified \ac{PE} active set requirements.
\ChangelogRef{subsec:coll}%
%
\item Clarified that when the \VAR{size} argument is zero, symmetric heap
    allocation routines perform no action and return a null pointer; that
    symmetric heap management routines that perform no action do not perform a
    barrier; and that the \VAR{alignment} argument to \FUNC{shmem\_align} must
    be power of two multiple of \CONST{sizeof(void*)}.
\ChangelogRef{subsec:shmem_malloc, subsec:shmem_align, subsec:shmem_realloc}%
%
\item Clarified that the \openshmem lock \ac{API} provides a non-reentrant mutex and
    that \FUNC{shmem\_clear\_lock} performs a quiet operation on the default
    context.
\ChangelogRef{subsec:shmem_lock}%
%
\item Clarified the atomicity guarantees of the \openshmem memory model.
\ChangelogRef{subsec:amo_guarantees}%
%
\end{enumerate}

\section{Version 1.4}
Major changes in \openshmem[1.4] include
multithreading support,
\emph{contexts} for communication management,
\FUNC{shmem\_sync},
\FUNC{shmem\_calloc},
expanded type support,
a new namespace for atomic operations,
atomic bitwise operations,
\FUNC{shmem\_test} for nonblocking point-to-point synchronization,
and \Cstd[11] type-generic interfaces for point-to-point synchronization.

The following list describes the specific changes in \openshmem[1.4]:
\begin{enumerate}
%
\item New communication management \ac{API}, including \FUNC{shmem\_ctx\_create};
    \FUNC{shmem\_ctx\_destroy}; and additional \ac{RMA}, \ac{AMO}, and memory ordering
    routines that accept \CTYPE{shmem\_ctx\_t} arguments.
\ChangelogRef{sec:ctx}%
%
\item New \ac{API} \FUNC{shmem\_sync\_all} and \FUNC{shmem\_sync} to provide \ac{PE}
    synchronization without completing pending communication operations.
\ChangelogRef{subsec:shmem_sync_all, subsec:shmem_sync}%
%
\item Clarified that the \openshmem extensions header files are required, even when empty.
\ChangelogRef{subsec:bindings}%
%
\item Clarified that the \FUNC{SHMEM\_GET64} and \FUNC{SHMEM\_GET64\_NBI}
    routines are included in the \Fortran language bindings.
\ChangelogRef{subsec:shmem_get, subsec:shmem_get_nbi}%
%
\item Clarified that \FUNC{shmem\_init} must be matched with a call to
    \FUNC{shmem\_finalize}.
\ChangelogRef{subsec:shmem_init, subsec:shmem_finalize}%
%
\item Added the \CONST{SHMEM\_SYNC\_SIZE} constant.
\ChangelogRef{subsec:library_constants}%
%
\item Added type-generic interfaces for \FUNC{shmem\_wait\_until}.
\ChangelogRef{subsec:shmem_wait_until}%
%
\item Removed the \VAR{volatile} qualifiers from the \VAR{ivar} arguments to
\FUNC{shmem\_wait} routines and the \VAR{lock} arguments in the lock \ac{API}.
\emph{Rationale: Volatile qualifiers were added to several \ac{API} routines in
\openshmem[1.3]; however, they were later found to be unnecessary.}
\ChangelogRef{subsec:shmem_wait_until, subsec:shmem_lock}%
%
\item Deprecated the \VAR{SMA\_}* environment variables and added equivalent
\VAR{SHMEM\_}* environment variables.
\ChangelogRef{subsec:environment_variables, dep:envvar_sma}%
%
\item Added the \Cstd[11] \CTYPE{\_Noreturn} function specifier to
\FUNC{shmem\_global\_exit}.
\ChangelogRef{subsec:shmem_global_exit}%
%
\item Clarified ordering semantics of memory ordering, point-to-point synchronization, and collective
synchronization routines.
%
\item Clarified deprecation overview and added deprecation rationale.
\ChangelogRef{dep:overview, dep:rationale}%
%
\item Deprecated header directory \HEADER{mpp}.
\ChangelogRef{dep:mpp_header}%
%
\item Deprecated the \FUNC{shmem\_wait} functions and the \CTYPE{long}-typed \CorCpp \FUNC{shmem\_wait\_until} function.
\ChangelogRef{subsec:shmem_wait_until, dep:shmem_wait, dep:long_typed_shmem_wait_until}%
%
\item Added the \FUNC{shmem\_test} functions.
\ChangelogRef{subsec:p2p_intro}%
%
\item Added the \FUNC{shmem\_calloc} function.
\ChangelogRef{subsec:shmem_calloc}%
%
\item Introduced the thread safe semantics that define the interaction between
    \openshmem routines and user threads.
\ChangelogRef{subsec:thread_support}%
%
\item Added the new routine \FUNC{shmem\_init\_thread} to initialize the
    \openshmem library with one of the defined thread levels.
\ChangelogRef{subsec:shmem_init_thread}%
%
\item Added the new routine \FUNC{shmem\_query\_thread} to query the thread
    level provided by the \openshmem implementation.
\ChangelogRef{subsec:shmem_query_thread}%
%
\item Clarified the semantics of \FUNC{shmem\_quiet} for a multithreaded
    \openshmem \ac{PE}.
\ChangelogRef{subsec:shmem_quiet}%
%
\item Revised the description of \FUNC{shmem\_barrier\_all} for a multithreaded
    \openshmem \ac{PE}.
\ChangelogRef{subsec:shmem_barrier_all}%
%
\item Revised the description of \FUNC{shmem\_wait} for a multithreaded
    \openshmem \ac{PE}.
\ChangelogRef{subsec:shmem_wait_until}%
%
\item Clarified description for \CONST{SHMEM\_VENDOR\_STRING}.
\ChangelogRef{subsec:library_constants}%
%
\item Clarified description for \CONST{SHMEM\_MAX\_NAME\_LEN}.
\ChangelogRef{subsec:library_constants}%
%
\item Clarified \ac{API} description for \FUNC{shmem\_info\_get\_name}.
\ChangelogRef{subsec:shmem_info_get_name}%
%
\item Expanded the type support for \ac{RMA}, \ac{AMO}, and point-to-point
    synchronization operations.
%% cleveref will compress a list of references by default. It is better to not
%% compress this list of *table* references because the clickable hyperref
%% links are useful. You can tell cleveref to not compress the LHS and RHS by
%% inserting an empty item between them; i.e., `,,`.
\ChangelogRef{stdrmatypes,, stdamotypes,, extamotypes,, p2psynctypes}%
%
\item Renamed \ac{AMO} operations to use \FUNC{shmem\_atomic\_*} prefix and
      deprecated old \ac{AMO} routines.
\ChangelogRef{sec:amo, dep:amo_not_shmem_atomic}%
%
\item Added fetching and non-fetching bitwise AND, OR, and XOR atomic
      operations.
\ChangelogRef{sec:amo}%
%
\item Deprecated the entire \Fortran \ac{API}.
\ChangelogRef{dep:fortran}%
%
\item Replaced the \CTYPE{complex} macro in complex-typed reductions with the
      \Cstd[99] (and later) type specifier \CTYPE{\_Complex} to remove an
      implicit dependence on \HEADER{complex.h}.
\ChangelogRef{subsec:shmem_reductions}%
%
\item Clarified that complex-typed reductions in C are optionally supported.
\ChangelogRef{subsec:shmem_reductions}%
%
\end{enumerate}




\section{Version 1.3}
Major changes in \openshmem[1.3] include the addition of
nonblocking \ac{RMA} operations,
atomic \PUT{} and \GET{} operations,
all-to-all collectives,
and \Cstd[11] type-generic interfaces for \ac{RMA} and \ac{AMO} operations.

The following list describes the specific changes in \openshmem[1.3]:
\begin{enumerate}
%
\item Clarified implementation of \acp{PE} as threads.
%
\item Added \CTYPE{const} to every read-only pointer argument.
%
\item Clarified definition of \OPR{Fence}.
\ChangelogRef{subsec:programming_model}%
%
\item Clarified implementation of symmetric memory allocation.
\ChangelogRef{subsec:memory_model}%
%
\item Restricted atomic operation guarantees to other atomic operations with the same datatype.
\ChangelogRef{subsec:amo_guarantees}%
%
\item Deprecation of all constants that start with \CONST{\_SHMEM\_*}.
\ChangelogRef{subsec:library_constants, dep:libconst_undershmem}%
%
\item Added a type-generic interface to \openshmem \ac{RMA} and \ac{AMO}
    operations based on \Cstd[11] Generics.
\ChangelogRef{sec:rma, sec:amo}%
%
\item New nonblocking variants of remote memory access, \FUNC{SHMEM\_PUT\_NBI}
    and \FUNC{SHMEM\_GET\_NBI}.
\ChangelogRef{subsec:shmem_put_nbi, subsec:shmem_get_nbi}%
%
\item New atomic elemental read and write operations, \FUNC{SHMEM\_FETCH} and
    \FUNC{SHMEM\_SET}.
\ChangelogRef{subsec:shmem_atomic_fetch, subsec:shmem_atomic_set}%
%
\item New alltoall data exchange operations, \FUNC{SHMEM\_ALLTOALL}
    and \FUNC{SHMEM\_ALLTOALLS}.
\ChangelogRef{subsec:shmem_alltoall, subsec:shmem_alltoalls}%
%
\item Added \CTYPE{volatile} to remotely accessible pointer argument in
    \FUNC{SHMEM\_WAIT} and \FUNC{SHMEM\_LOCK}.
\ChangelogRef{subsec:shmem_wait_until, subsec:shmem_lock}%
%
\item Deprecation of \FUNC{SHMEM\_CACHE}.
\ChangelogRef{dep:shmem_cache}%
%
\end{enumerate}




\section{Version 1.2}
Major changes in \openshmem[1.2] include
a new initialization routine (\FUNC{shmem\_init}),
improvements to the execution model with an explicit
library-finalization routine (\FUNC{shmem\_finalize}),
an early-exit routine (\FUNC{shmem\_global\_exit}),
namespace standardization,
and clarifications to several \ac{API} descriptions.

The following list describes the specific changes in \openshmem[1.2]:
\begin{enumerate}
%
\item Added specification of \VAR{pSync} initialization for all routines that use it.
%
\item Replaced all placeholder variable names \VAR{target} with \VAR{dest} to
      avoid confusion with \Fortran's \KEYWORD{target} keyword.
%
\item New Execution Model for exiting/finishing \openshmem programs.
\ChangelogRef{subsec:execution_model}%
%
\item New library constants to support \ac{API} that query version and name information.
\ChangelogRef{subsec:library_constants}%
%
\item New \ac{API} \FUNC{shmem\_init} to provide mechanism to start an \openshmem
      program and replace deprecated \FUNC{start\_pes}.
\ChangelogRef{subsec:shmem_init, dep:start_pes}%
%
\item Deprecation of \FUNC{\_my\_pe} and \FUNC{\_num\_pes} routines.
\ChangelogRef{subsec:shmem_my_pe, subsec:shmem_n_pes, dep:func_not_shmemunder}%
%
\item New \ac{API} \FUNC{shmem\_finalize} to provide collective mechanism to cleanly
      exit an \openshmem program and release resources.
\ChangelogRef{subsec:shmem_finalize}%
%
\item New \ac{API} \FUNC{shmem\_global\_exit} to provide mechanism to exit an
    \openshmem program.
\ChangelogRef{subsec:shmem_global_exit}%
%
\item Clarification related to the address of the referenced object in
    \FUNC{shmem\_ptr}.
\ChangelogRef{subsec:shmem_ptr}%
%
\item New \ac{API} to query the version and name information.
\ChangelogRef{subsec:shmem_info_get_version, subsec:shmem_info_get_name}%
%
\item \openshmem library \ac{API} normalization. All \Cstd symmetric memory management
      \ac{API} begins with \FUNC{shmem\_}.
\ChangelogRef{sec:memory_management, dep:func_not_shmemunder}%
%
\item Notes and clarifications added to \FUNC{shmem\_malloc}.
\ChangelogRef{subsec:shmem_malloc}%
%
\item Deprecation of \Fortran \ac{API} routine \FUNC{SHMEM\_PUT}.
\ChangelogRef{dep:fortran_shmem_put}%
See \openshmem[1.4], Section 9.5.1.
%
\item Clarification related to \FUNC{shmem\_wait}.
\ChangelogRef{subsec:shmem_wait_until}%
%
\item Undefined behavior for null pointers without zero counts added.
\ChangelogRef{sec:undefined}%
%
\item Added new Annex for clearly specifying deprecated \ac{API} and its
      support across versions of the \openshmem Specification.
\ChangelogRef{sec:dep}%
%
\end{enumerate}




\section{Version 1.1}
Major changes from \openshmem[1.0] to \openshmem[1.1] include
the introduction of the \HEADER{shmemx.h} header file for nonstandard \ac{API}
extensions,
clarifications to completion semantics and \ac{API} descriptions in agreement with
the \ac{SGI} SHMEM specification,
and general readability and usability improvements to the document structure.

The following list describes the specific changes in \openshmem[1.1]:
\begin{enumerate}
%
\item Clarifications of the completion semantics of memory synchronization
      interfaces.
\ChangelogRef{subsec:memory_order}%
%
\item Clarification of the completion semantics of memory load and store
      operations in context of \FUNC{shmem\_barrier\_all} and \FUNC{shmem\_barrier}
      routines.
\ChangelogRef{subsec:shmem_barrier_all, subsec:shmem_barrier}%
%
\item Clarification of the completion and ordering semantics of
      \FUNC{shmem\_quiet} and \FUNC{shmem\_fence}.
\ChangelogRef{subsec:shmem_quiet, subsec:shmem_fence}%
%
\item Clarifications of the completion semantics of \ac{RMA} and \ac{AMO}
      routines.
\ChangelogRef{sec:rma, sec:amo}%
%
\item Clarifications of the memory model and the memory alignment requirements
      for symmetric data objects.
\ChangelogRef{subsec:memory_model}%
%
\item Clarification of the execution model and the definition of a \ac{PE}.
\ChangelogRef{subsec:execution_model}%
%
\item Clarifications of the semantics of \FUNC{shmem\_pe\_accessible} and
      \FUNC{shmem\_addr\_accessible}.
\ChangelogRef{subsec:shmem_pe_accessible, subsec:shmem_addr_accessible}%
%
\item Added an annex on interoperability with \ac{MPI}.
\ChangelogRef{sec:interoperability}%
%
\item Added examples to the different interfaces.
%
\item Clarification of the naming conventions for constant in \Cstd and
      \Fortran.
\ChangelogRef{subsec:library_constants, subsec:shmem_wait_until}%
%
\item Added \ac{API} calls: \FUNC{shmem\_char\_p}, \FUNC{shmem\_char\_g}.
\ChangelogRef{subsec:shmem_p, subsec:shmem_g}%
%
\item Removed \ac{API} calls: \FUNC{shmem\_char\_put},
      \FUNC{shmem\_char\_get}.
\ChangelogRef{subsec:shmem_put, subsec:shmem_get}%
%
\item The usage of \CTYPE{ptrdiff\_t}, \CTYPE{size\_t}, and \CTYPE{int} in the
      interface signature was made consistent with the description.
\ChangelogRef{subsec:coll, subsec:shmem_iput, subsec:shmem_iget}%
%
\item Revised \FUNC{shmem\_barrier} example.
\ChangelogRef{subsec:shmem_barrier}%
%
\item Clarification of the initial value of \VAR{pSync} work arrays for
\FUNC{shmem\_barrier}.
\ChangelogRef{subsec:shmem_barrier}%
%
\item Clarification of the expected behavior when multiple \FUNC{start\_pes}
calls are encountered.
\ChangelogRef{subsec:start_pes}%
%
\item Corrected the definition of atomic increment operation.
\ChangelogRef{subsec:shmem_atomic_inc}%
%
\item Clarification of the size of the symmetric heap and when it is set.
\ChangelogRef{sec:memory_management}%
%
\item Clarification of the integer and real sizes for \Fortran \ac{API}.
\ChangelogRef{
  subsec:shmem_atomic_add,
  subsec:shmem_atomic_compare_swap,
  subsec:shmem_atomic_swap,
  subsec:shmem_atomic_fetch_inc,
  subsec:shmem_atomic_inc,
  subsec:shmem_atomic_fetch_add}%
%
\item Clarification of the expected behavior on program \OPR{exit}.
\ChangelogRef{subsec:execution_model}%
%
\item More detailed description for the progress of \openshmem operations
provided.
\ChangelogRef{subsec:progress}%
%
\item Clarification of naming convention for nonstandard interfaces and their
inclusion in \HEADER{shmemx.h}.
\ChangelogRef{subsec:bindings}%
%
\item Various fixes to \openshmem code examples across the Specification to
include appropriate header files.
%
\item Removing requirement that implementations should detect size mismatch and
return error information for \FUNC{shmalloc} and ensuring consistent
language.
\ChangelogRef{subsec:shmem_malloc, sec:undefined}%
%
\item \Fortran programming fixes for examples.
\ChangelogRef{subsec:shmem_reductions, subsec:shmem_wait_until}%
%
\item Clarifications of the reuse \VAR{pSync} and \VAR{pWork} across
collectives.
\ChangelogRef{
  subsec:coll,
  subsec:shmem_broadcast,
  subsec:shmem_collect,
  subsec:shmem_reductions}%
%
\item Name changes for UV and ICE for \ac{SGI} systems.
\ChangelogRef{sec:openshmem_history}%
%
\end{enumerate}

\chapter{Errata}\label{sec:errata}

Errors or ambiguities in the \openshmem specification may be discovered after
publication.
Errata, or corrections, are included in the sections below indicating the
version of the \openshmem specification that required the correction or
clarification.
These corrections have been applied to all subsequent versions of the
specification and this section serves as a historical record of the changes
made to assist users and implementors with applying the necessary corrections.
Errata that result in a change to the specification are also included in
Annex~\ref{sec:changelog}.
For an implementation to comply with a particular version of \openshmem, it
must account for all errata associated with that version as indicated below.

\section{Version 1.5}

\begin{enumerate}
  \item Removed \openshmem[1.5] Table 9, which was an incomplete duplicate of
      \openshmem[1.5] Table 10, and clarified the types, names, and supporting
      operations for team-based reductions
        (\ref{changelog:v1.6}.\ref{changelog:reduction_table}).
  \item Clarified that \VAR{source} and \VAR{dest} arrays must be the same
      across \acp{PE} in \openshmem reductions
        (\ref{changelog:v1.6}.\ref{changelog:reduction_args}).
  \item Clarified that \OPR{Fence} operations only guarantee ordering for operations
     that are performed on the same context
        (\ref{changelog:v1.6}.\ref{changelog:fence_ctx}).
  \item Clarified that \FUNC{shmem\_test\_all} and
     \FUNC{shmem\_test\_all\_vector} routines return 1 when the test set is empty
        (\ref{changelog:v1.6}.\ref{changelog:test_all}).
  \item Clarified that \FUNC{shmem\_team\_split\_strided} and
     \FUNC{shmem\_team\_split\_2d} return a nonzero value when the parent team is
     \LibConstRef{SHMEM\_TEAM\_INVALID}
        (\ref{changelog:v1.6}.\ref{changelog:split_strided_2d}).
  \item Corrected the \VAR{level} argument's recommended value in API notes for
     \FUNC{shmem\_pcontrol} to indicate that the value should be greater than 2 to enable
     profiling with profile library defined effects and additional arguments
        (\ref{changelog:v1.6}.\ref{changelog:pcontrol}).
  \item Added a \texttt{const} qualifier to the \VAR{cmp\_values} argument in the
     following point-to-point synchronization routines:
     \FUNC{shmem\_wait\_until\_all\_vector},
     \FUNC{shmem\_wait\_until\_any\_vector},
     \FUNC{shmem\_wait\_until\_some\_vector},
     \FUNC{shmem\_test\_all\_vector}, \FUNC{shmem\_test\_any\_vector}, and
     \FUNC{shmem\_test\_some\_vector}
        (\ref{changelog:v1.6}.\ref{changelog:p2p_vector_const}).
\end{enumerate}

%end of setlength command that was started in frontmatter.tex
