\emph{Collective routines} are defined as \newtext{coordinated} communication or synchronization
operations \oldtext{on} \newtext{performed by} a group of \acp{PE} \oldtext{called an active set}.

{\color{Green}
\openshmem provides two types of collective routines:

\begin{enumerate}
\item Collective routines that operate on teams use a team handle parameter to determine
which \acp{PE} will participate in the routine, and use resources encapsulated by the team object
to perform operations. See Section~\ref{subsec:team} for details on team management.
These routines will be the standard for \openshmem moving forward.
\item Collective routines that operate on active sets use a set of parameters to determine
which \acp{PE} will participate and what resources are used to perform operations. These routines
are the legacy API for collectives which will be deprecated and phased out of
implementations moving forward.
\end{enumerate}

Collective routines with no team or active set parameters are deprecated,
and implicitly operate on the team consisting of all \acp{PE} in the computation,
\LibHandleRef{SHMEM\_TEAM\_WORLD}

The team-based collective routines are performed with respect to a valid
\openshmem team, which is specified by a team handle argument.
Team-based collective operations require all \acp{PE} in the team to call
the routine in order for the operation to complete. If an invalid team handle
or \LibConstRef{SHMEM\_TEAM\_NULL} is passed to a team-based collective
routine, the behavior is undefined.

Team objects encapsulate the per \ac{PE} system resources required to complete
team-based collective routines.
All \openshmem teams-based collective calls are blocking routines which may use those
system resources. On completion of a team-based collective call, the \ac{PE} may
immediately call another collective on that same team without any other intervening
synchronization across the team.

While \openshmem routines provide thread safety as per the requesting threading model
(see \ref{subsec:thread_support}), the teams object itself is not thread-safe. It is up
to the program to ensure that on a given \ac{PE}, there are no simutanously calls to routines
on a given team object, including all team based collective calls.

Collective operations are matched across a given team based on ordering. So for a given team,
collectives must occur in the same order across all PEs in a team.

The team-based collective routines defined in the \openshmem Specification are:

\begin{itemize}
\item \FUNC{shmem\_team\_sync}
\item \FUNC{shmem\_team\_broadcast\{32, 64\}}
\item \FUNC{shmem\_team\_collect\{32, 64\}}
\item \FUNC{shmem\_team\_fcollect\{32, 64\}}
\item Reductions for the following operations: AND, MAX, MIN, SUM, PROD, OR, XOR
\item \FUNC{shmem\_team\_alltoall\{32, 64\}}
\item \FUNC{shmem\_team\_alltoalls\{32, 64\}}
\end{itemize}

In addition, all team creation functions are collective operations. In addition to the ordering
and thread safety requirements described here, there are additional synchronization requirements
on team creation operations. See section \ref{subsec:team} for more details.

The deprecated function \FUNC{shmem\_sync\_all} is provided for backward compatibility to synchronize
all \acp{PE} in the computation. This should be replaced in applications by the equivalent
\FUNC{shmem\_sync(SHMEM\_TEAM\_WORLD)}.
}

\begin{DeprecateBlock}
The \newtext{active-set-based} collective routines require all \acp{PE}
in the active set to simultaneously call the
routine.  A \ac{PE} that is not in the active set calling the collective
routine results in undefined behavior.  \oldtext{All collective routines have an
active set as an input parameter except \FUNC{shmem\_barrier\_all} and
\FUNC{shmem\_sync\_all}. Both \FUNC{shmem\_barrier\_all} and
\FUNC{shmem\_sync\_all} must be called by all \acp{PE} of the \openshmem program.}

The active set is defined by the arguments \VAR{PE\_start}, \VAR{logPE\_stride},
and \VAR{PE\_size}.  \VAR{PE\_start} specifies the starting \ac{PE} number and
is the lowest numbered \ac{PE} in the active set.  The stride between successive
\acp{PE} in the active set is $2^{logPE\_stride}$ and \VAR{logPE\_stride} must
be greater than or equal to zero.  \VAR{PE\_size} specifies the number of
\acp{PE} in the active set and must be greater than zero.  The active set must
satisfy the requirement that its last member corresponds to a valid \ac{PE}
number, that is
$0 \le PE\_start + (PE\_size - 1) * 2^{logPE\_stride} < npes$.

All \acp{PE} participating in the \newtext{active-set-based} collective routine must provide the same
values for these arguments.  If any of these requirements are not met, the
behavior is undefined.

Another argument important to \newtext{active-set-based} collective routines is \VAR{pSync}, which is a
symmetric work array.  All \acp{PE} participating in an \newtext{active-set-based} collective must pass the
same \VAR{pSync} array.  On completion of \newtext{such} a collective call, the \VAR{pSync} is
restored to its original contents.  The user is permitted to reuse a \VAR{pSync}
array if all previous collective routines using the \VAR{pSync} array have been
completed by all participating \acp{PE}. One can use a synchronization
collective routine such as \FUNC{shmem\_barrier} to ensure completion of previous \newtext{active-set-based} collective
routines. The \FUNC{shmem\_barrier} and \FUNC{shmem\_sync} routines allow the same
\VAR{pSync} array to be used on consecutive calls as long as the \acp{PE}
in the active set do not change.

All collective routines defined in the Specification are blocking.  The
collective routines return on completion.  The \newtext{active-set-based} collective
routines defined in the \openshmem Specification are:

\begin{itemize}
\item \FUNC{shmem\_barrier\_all}
\item \FUNC{shmem\_barrier}
\item \FUNC{shmem\_sync\_all}
\item \FUNC{shmem\_sync}
\item \FUNC{shmem\_broadcast\{32, 64\}}
\item \FUNC{shmem\_collect\{32, 64\}}
\item \FUNC{shmem\_fcollect\{32, 64\}}
\item Reductions for the following operations: AND, MAX, MIN, SUM, PROD, OR, XOR
\item \FUNC{shmem\_alltoall\{32, 64\}}
\item \FUNC{shmem\_alltoalls\{32, 64\}}
\end{itemize}

{\color{Green}
The active-set-based \FUNC{shmem\_barrier} and routine has been deprecated and
no team-based barrier routines will be defined. In future, the behavior
previously provided by \FUNC{shmem\_barrier} should be realized by first calling
\FUNC{shmem\_ctx\_quiet} on any relevant communication contexts followed by a call
to \FUNC{shmem\_sync} by some \openshmem team.

Calls to \FUNC{shmem\_barrier\_all}
should be replaced with a call to quiet the default communication context followed
by a call to \FUNC{shmem\_sync} by \LibHandleRef{SHMEM\_TEAM\_WORLD}.
}
\end{DeprecateBlock}
