\TableIndex{Environment Variables}

The \openshmem specification provides a set of environment variables that allows
users to configure the \openshmem implementation and receive information about
the implementation. The implementations of the specification are free to define
additional variables. Currently, the specification defines four environment
variables. All environment variables that start with \VAR{SMA\_*} are
deprecated, but currently supported for backwards compatibility.
If both \VAR{SHMEM\_}- and \VAR{SMA\_}-prefixed environment variables
are set, then the value in the \VAR{SHMEM\_}-prefixed environment variable
establishes the controlling value. Refer to the
\hyperref[subsec:deprecate-sma-env]{\VAR{SMA\_*} Environment Variables}
deprecation rationale for more details.

\medskip{}

\begin{longtable}{|p{0.260\textwidth}|p{0.145\textwidth}|p{0.50\textwidth}|}
\hline
\textbf{Variable} & \textbf{Value} & \textbf{Description}
\tabularnewline\hline
%%
\EnvVarDecl{SHMEM\_VERSION}
    & Any
    & Print the library version at start-up
    \tabularnewline\hline
%%
\EnvVarDecl{SHMEM\_INFO}
    & Any
    & Print helpful text about all these environment variables
    \tabularnewline\hline
%%
\EnvVarDecl{SHMEM\_SYMMETRIC\_SIZE}
    & Non-negative integer or floating point value with an optional character
    suffix
    & Specifies the size (in bytes) of the symmetric heap memory per \ac{PE}.
    The resulting size is implementation-defined and must be least as large as
    the integer ceiling of the product of the numeric prefix and the scaling
    factor. The allowed character suffixes for the scaling factor are as
    follows:
      \begin{itemize}
        \item k or K multiplies by \(2^{10}\)  (kibibytes)
        \item m or M multiplies by \(2^{20}\)  (mebibytes)
        \item g or G multiplies by \(2^{30}\)  (gibibytes)
        \item t or T multiplies by \(2^{40}\)  (tebibytes)
      \end{itemize}
      For example, string \enquote{20m} is equivalent to the integer value
      20971520, or 20 mebibytes. Similarly the string \enquote{3.1M} is
      equivalent to the integer value 3250586.
      Only one multiplier is recognized and any characters following the
      multiplier are ignored, so \enquote{20kk} will not produce the same
      result as \enquote{20m}. Usage of string \enquote{.5m} will yield the
      same result as the string \enquote{0.5m}.

      An invalid value for \ENVVAR{SHMEM\_SYMMETRIC\_SIZE} is an error, which the
      \openshmem library shall report by either returning a nonzero value from
      \FUNC{shmem\_init\_thread} or causing program termination.
    \tabularnewline\hline
%%
\EnvVarDecl{SHMEM\_DEBUG}
    & Any
    & Enable debugging messages
    \tabularnewline\hline
\end{longtable}

\medskip{}
