\begin{description}

\item[Blocking] An \openshmem routine for which return from a call to
  that routine guarantees local completion for its associated local
  buffers.

\item[Local completion] of an \openshmem operation indicates that all
  local objects involved in the operation are locally complete.

  For an \openshmem operation that reads a local object of
  memory---for example, the \source{} argument of \FUNC{shmem\_put}
  or, for only the root \ac{PE}, \FUNC{shmem\_team\_broadcast}---local
  completion of that object specifies the point (in time) after which
  a write (or update) to that object by the \ac{PE} initiating the
  operation would not affect the value(s) read by the \openshmem
  implementation in performing the operation.

  For an \openshmem operation that writes a local object of
  memory---for example, the \dest{} argument of \FUNC{shmem\_get} or
  \FUNC{shmem\_team\_broadcast}---local completion of that object
  specifies the point after which a read of that local object by the
  \ac{PE} initiating the operation will return the value(s) produced
  by the \openshmem implementation in performing the operation.

\item[Nonblocking] An \openshmem routine for which return from a call
  to that routine guarantees neither local nor remote completion.

\item[Remote completion] of an \openshmem operation indicates that all
  remote objects involved in the operation are remotely complete.

  For an \openshmem operation that reads a remote object of
  memory---for example, the \source{} argument of \FUNC{shmem\_get} or
  \FUNC{shmem\_team\_alltoall}---remote completion of that object
  specifies the point (in time) after which a write (or update) to
  that object by any \ac{PE} would not affect the value(s) read by the
  \openshmem implementation in performing the operation.

  For an \openshmem operation that writes a remote object of
  memory---for example, the \dest{} argument of \FUNC{shmem\_put} or
  \FUNC{shmem\_team\_alltoall}---remote completion of that object
  specifies the point after which a read of that remote object by the
  target \ac{PE} will return the value(s) produced by the \openshmem
  implementation in performing the operation.

  See \FUNC{shmem\_quiet} for mechanisms that ensure remote completion
  (Section~\ref{subsec:shmem_quiet}).

\end{description}
