\openshmem provides ISO \Cstd and \Fortran[90] language bindings.
As of \openshmem[1.4], the \Fortran API is deprecated.
For rationale and considerations of
future \Fortran use of \openshmem, see Section~\ref{subsec:deprecate-fortran}.

Any implementation that provides both \Cstd and \Fortran bindings can claim
conformance to the specification. Alternatively, an implementation may claim
conformance only with respect to one of those languages. For example,
an implementation that provides only a
\Cstd interface may claim to conform to the \openshmem specification with
respect to the \Cstd language, but not to \Fortran, and should make this distinction
clear in its documentation. The \openshmem header files \HEADER{shmem.h} for
\Cstd and \HEADER{shmem.fh} for
\Fortran must contain only the interfaces and constant names defined in this
specification.

\openshmem \acp{API} can be implemented as either routines or macros. However,
implementing the interfaces using macros is strongly discouraged as this could
severely limit the use of external profiling tools and high-level compiler
optimizations. An \openshmem program should avoid defining routine names,
variables, or identifiers with the prefix \shmemprefix (for \Cstd and
\Fortran), \shmemprefixC (for \Cstd) or with \openshmem \ac{API} names.

All \openshmem extension \acp{API} that are not part of this specification must
be defined in the \HEADER{shmemx.h} and \HEADER{shmemx.fh} include files for
\Cstd and \Fortran language bindings, respectively.  These header files
must exist, even if no extensions are provided.  Any extensions shall use the
\FUNC{shmemx\_} prefix for all routine, variable, and constant names.
