\TableIndex{Library Handles}
\TableIndex{Handles}

The \openshmem library provides a set of predefined named constant handles.
All named constants can be used in initialization expressions or assignments,
but not necessarily in array declarations or as labels in \Cstd switch statements.
This implies named constants to be link-time but not necessarily compile-time
constants.

\begin{longtable}{|p{0.45\textwidth}|p{0.5\textwidth}|}
\hline
\textbf{Handle} & \textbf{Description}
\tabularnewline \hline
\endhead
%%
\LibHandleDecl{SHMEM\_TEAM\_WORLD} &
Handle of type \CTYPE{shmem\_team\_t} that corresponds to the
default team of all \acp{PE} in the \openshmem program.  All point-to-point
communication operations and collective synchronizations that do not specify a team
are performed on the default team.
See Section~\ref{subsec:team} for more detail about its use.
\tabularnewline \hline
%%
\LibHandleDecl{SHMEM\_TEAM\_SHARED} &
Handle of type \CTYPE{shmem\_team\_t} that corresponds to a team of \acp{PE}
that share a memory domain.  \LibHandleRef{SHMEM\_TEAM\_SHARED} refers to
the team of all PEs that would mutually return a non-null address from a
call to \FUNC{shmem\_ptr} for all symmetric heap objects.  That is,
\FUNC{shmem\_ptr} must return a non-null pointer to the local PE for all
symmetric heap objects on all target \acp{PE} in the team.  This means that
symmetric heap objects on each \ac{PE} are
directly load/store accessible by all \acp{PE} in the team.
See Section~\ref{subsec:team} for more detail about its use.
\tabularnewline \hline
%%
\LibHandleDecl{SHMEM\_CTX\_DEFAULT} &
Handle of type \CTYPE{shmem\_ctx\_t} that corresponds to the
default communication context.  All point-to-point communication operations
and synchronizations that do not specify a context are performed on the
default context.
See Section~\ref{sec:ctx} for more detail about its use.
\tabularnewline \hline
%%
\end{longtable}
