The objective of the \openshmem profiling interface is to ensure an 
easy and flexible usage model for profiling (and other similar) 
tool developers to interface their codes into \openshmem 
implementations on different platforms. Since \openshmem is a 
machine-independent standard with different implementations, it is 
unreasonable to expect that the authors and developers of profiling 
tools for \openshmem will have access to the source code that 
implements \openshmem on any particular machine. It is, therefore,  
necessary to provide a mechanism by which the implementors of such 
tools can collect whatever performance information they wish 
\emph{without} access to the underlying implementation.

The \openshmem profiling interface places the following requirements 
on implementations. 

\begin{enumerate}
\item An \openshmem implementation must provide a mechanism through 
which all of the \openshmem defined functions may be accessible 
with a name shift. This requires an alternate 
entry point name, with the prefix \FUNC{pshmem\_} for each 
\openshmem function. For \openshmem inlined functions (e.g. macros), 
it is also required that the \FUNC{pshmem\_} version is supplied 
although it is not possible to replace the \FUNC{shmem\_} version 
with a user-defined version at link time.
\item It must be ensured that the \openshmem functions that are not 
replaced as above, may still be linked into an executable image 
without causing name clashes. 
\item Documentation of the implementation of different language 
bindings of the \openshmem interface must indicate if they 
are layered on top of each other. Using this documentation,   
developers can determine whether they need to implement the 
profile interface for each binding or not. For example, it must 
be noted that the \openshmem \Cstd[11] type-generic interfaces for 
different RMA and AMO operations cannot have any equivalent 
\FUNC{pshmem\_} interfaces because the \Cstd[11] type-generic 
interfaces are implemented as macros.
\item In the case where the implementation of different API  
feature sets is implemented through a layered approach using 
``wrapper'' functions, the wrapper functions must be kept separate 
from the rest of the library. This requirement allows the developers 
to extract these functions from the original \openshmem library 
and add them into the profiling library without bringing along any 
other code.
\item A no-op routine, \FUNC{shmem\_pcontrol}, must be provided 
in the \openshmem library.
\item It must be ensured that any \openshmem types or constants that are 
needed by the \FUNC{pshmem\_} interfaces are defined in \HEADER{pshmem.h}.
\end{enumerate}

Provided that an \openshmem implementation meets these requirements, 
it is possible for the implementor of the profiling system 
to intercept the \openshmem calls that are made by the user 
program. The information required can be collected before and after 
calling the underlying \openshmem implementation through the name 
shifted entry points. 

\subsection{Control of Profiling}
\label{sec:pshmem_control_profile}
Any user code must be able to control the profiler dynamically 
during runtime. Generally, this capability is used for the 
purposes of

\begin{itemize}
\item Enabling and disabling of profiling based on the current 
state of the execution and calculation,
\item Flushing of the trace buffers at non-critical execution 
regions,
\item Adding user events to a trace file.
\end{itemize}

These functionalities can be achieved through the usage of 
\FUNC{shmem\_pcontrol}.

\subsubsection{\textbf{SHMEM\_PCONTROL}}\label{subsec:shmem_pcontrol}
\input{content/shmem_pcontrol}



\subsection{Example Implementations}
\label{sec:pshmem_example_implementations}

\subsubsection{Profiler}
\label{sec:pshmem_example_profiler}

The following example illustrates how a profiler can measure the
total and average time spent by the \FUNC{shmem\_long\_put} 
function in the profiling library that intercepts the \openshmem 
function calls from the user application.

\lstinputlisting[language={C}, tabsize=2,
      basicstyle=\ttfamily\footnotesize,
      morekeywords={size_t, ptrdiff_t, shmem_ctx_t, _Thread_local}]
      {example_code/pshmem_example.c}

\subsubsection{\openshmem Library}
\label{sec:pshmem_example_library}
To implement the name-shift versions of the \openshmem functions, 
there are various options available. The following two examples 
present two such options that can be implemented in C on a Unix 
system. These two options are dependent on whether the linker 
and compiler support weak symbols. 

If the compiler and linker support weak external symbols, then 
only a single library is required. The following two examples show 
how the name-shifted requirement can be achieved on such platforms. 

\noindent\textbf{Example 1}

\lstinputlisting[language={C}, tabsize=2,
      basicstyle=\ttfamily\footnotesize,
      morekeywords={size_t, ptrdiff_t, shmem_ctx_t, _Thread_local}]
      {example_code/pshmem_weak_symbol_1.c}

The effect of the \FUNC{\#pragma} directive is to define the 
external symbol \FUNC{shmem\_example} as a weak definition that 
aliases the \FUNC{pshmem\_example} function. This 
means that the linker will allow another definition 
of the symbol (e.g. the profiling library may contain an alternate 
definition). The weak definition is used in the case where no other 
definition for the same function exists. 

\noindent\textbf{Example 2}

\lstinputlisting[language={C}, tabsize=2,
      basicstyle=\ttfamily\footnotesize,
      morekeywords={size_t, ptrdiff_t, shmem_ctx_t, _Thread_local}]
      {example_code/pshmem_weak_symbol_2.c}

In this example, the keyword \FUNC{\_\_attribute\_\_} is used to 
declare the \FUNC{shmem\_example} function as an alias for 
the original function, \FUNC{pshmem\_example}.

In the absence of weak symbols, one possible solution would be to 
use the C macro preprocessor as shown in the following example. 

\lstinputlisting[language={C}, tabsize=2,
      basicstyle=\ttfamily\footnotesize,
      morekeywords={size_t, ptrdiff_t, shmem_ctx_t, _Thread_local}]
      {example_code/pshmem_no_weak_symbol_1.c}

Each of the user-defined functions in the profiling library would 
then be declared in the following manner. 

\lstinputlisting[language={C}, tabsize=2,
      basicstyle=\ttfamily\footnotesize,
      morekeywords={size_t, ptrdiff_t, shmem_ctx_t, _Thread_local}]
      {example_code/pshmem_no_weak_symbol_2.c}

The same source file can then be compiled to produce both versions 
of the library, depending on the state of the 
\VAR{BUILD\_PSHMEM\_INTERFACES} macro symbol.

\subsection{Limitations}
\label{sec:pshmem_limitations}

\subsubsection{Multiple Counting}
\label{sec:pshmem_multiple_count}
Since some functions in \openshmem library may be implemented 
using more basic \openshmem functions, it is possible for these basic  
profiling functions to be called from within an \openshmem function 
that was originally called from a profiling routine. For example, 
\openshmem collective operations can be implemented using basic 
point-to-point operations. Thus, profiling such a collective 
operation may lead to counting a profiling function for a
point-to-point operation more than once after being called from the 
collective function. It is the developer's responsibility to ensure 
the profiling application does not count a function more than once if 
that effect is not intended. For a single-threaded profiler, this 
can be achieved through a static variable counting the number of 
times a function has been profiled. In a multi-threaded environment, 
additional synchronizations are needed to manage updates to this 
counter and thus, it becomes more complex to accurately profile the 
\openshmem functions.

\subsubsection{Separate Build and Link}
\label{sec:pshmem_separate_build_link}
To build the profiling tool with both the default \openshmem
functions as well as the \openshmem functions to be intercepted, 
developers must build the multiple instances of the \openshmem
functions separately and link them to provide all the definitions. 
This is necessary so that the developers of the profiling library 
need only to define those \openshmem functions that they wish 
to intercept; references to any other functions will be fulfilled 
by the default \openshmem library. The link step can be summarized 
as follows. \\

\noindent\texttt{\% cc ... -lmyprof -lpsma -lsma} \\

Here, \texttt{libmyprof.a} contains the profiler functions that 
intercept the \openshmem functions to be profiled, 
\texttt{libpsma.a} contains the name-shifted \openshmem function 
definitions, and \texttt{libsma.a} contains the default \openshmem
function definitions. 

\subsubsection{\Cstd[11] Type-Generic Interfaces}
\label{sec:pshmem_c11_type_generic_interfaces}
\openshmem provides type-generic interfaces through \Cstd[11] 
generic selection. These interfaces are defined as macros 
and are mapped to \Cstd interface bindings. As a result, the 
\Cstd[11] type-generic interfaces cannot be intercepted and  
name-shifted \FUNC{pshmem\_} routines are not provided for these  
bindings. Furthermore, because no two associations in a \Cstd[11] 
\FUNC{\_Generic} selection expression can contain compatible types, 
the type name of the \Cstd operation that is invoked may not be 
identical to the type name of the original call's arguments (e.g. 
\VAR{int32\_t} may map to \VAR{int}).
