The \ac{RMA} routines described in this section can be used to perform
reads from and writes to symmetric data objects. These operations
are one-sided, meaning that the \ac{PE} invoking an operation provides all
communication parameters and the targeted \ac{PE} is passive. A characteristic
of one-sided communication is that it decouples communication from
synchronization. One-sided communication mechanisms transfer data; however,
they do not synchronize the sender of the data with the receiver of the data.

\openshmem \ac{RMA} routines are performed on symmetric data objects.  The
initiator \ac{PE} of a call is designated as the \emph{origin} \ac{PE} and the
\ac{PE} targeted by an operation is designated as the \emph{destination} \ac{PE}.  The
\source{} and \dest{} designators refer to the data objects that an operation
reads from and writes to.  In the case of the remote update routine, \PUT{},
the origin \ac{PE} provides the \source{} data object and the destination
\ac{PE} provides the \dest{} data object. In the case of the remote read
routine, \GET{}, the origin \ac{PE} provides the \dest{} data object and the
destination \ac{PE} provides the \source{} data object.

The destination \ac{PE} is specified as an integer representing the \ac{PE} number.
This \ac{PE} number is relative to the team associated with the
communication context being used for the operation. If no context argument is passed to the routine,
then the routine operates on the default context, which implies that
the \ac{PE} number is relative to the world team.
If the \ac{PE} number passed to the routine is invalid, being negative
or greater than or equal to the size of the \openshmem team, then the behavior is undefined.

\openshmem \ac{RMA} routines specified in this section have two variants. In
one of the variants, the context handle, \VAR{ctx}, is explicitly passed as
an argument. In this variant, the operation is performed on the specified
context. If the context handle \VAR{ctx} does not correspond to a valid
context, the behavior is undefined. In the other variant, the context handle
is not explicitly passed and thus, the operations are performed on the
default context.

Where appropriate compiler support is available, \openshmem provides type-generic 
one-sided communication interfaces via \Cstd[11] generic selection
(\Cstd[11]~\S6.5.1.1\footnote{Formally, the \Cstd[11] specification is ISO/IEC 9899:2011(E).})
for block, scalar, and block-strided put and get communication. 
Such type-generic routines are supported for the ``standard \ac{RMA} types''
listed in Table \ref{stdrmatypes}.

The standard \ac{RMA} types include the exact-width integer types defined in
\HEADER{stdint.h} by \Cstd[99]%
\footnote{Formally, the \Cstd[99] specification is ISO/IEC~9899:1999(E).}%
~\S7.18.1.1 and \Cstd[11]~\S7.20.1.1. When the \Cstd translation environment
does not provide exact-width integer types with \HEADER{stdint.h}, an
\openshmem implementation is not required to provide support for these types.

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|l|}
      \hline
      \TYPE              & \TYPENAME  \\ \hline
      float              & float      \\ \hline
      double             & double     \\ \hline
      long double        & longdouble \\ \hline
      char               & char       \\ \hline
      signed char        & schar      \\ \hline
      short              & short      \\ \hline
      int                & int        \\ \hline
      long               & long       \\ \hline
      long long          & longlong   \\ \hline
      unsigned char      & uchar      \\ \hline
      unsigned short     & ushort     \\ \hline
      unsigned int       & uint       \\ \hline
      unsigned long      & ulong      \\ \hline
      unsigned long long & ulonglong  \\ \hline
      int8\_t            & int8       \\ \hline
      int16\_t           & int16      \\ \hline
      int32\_t           & int32      \\ \hline
      int64\_t           & int64      \\ \hline
      uint8\_t           & uint8      \\ \hline
      uint16\_t          & uint16     \\ \hline
      uint32\_t          & uint32     \\ \hline
      uint64\_t          & uint64     \\ \hline
      size\_t            & size       \\ \hline
      ptrdiff\_t         & ptrdiff    \\ \hline
    \end{tabular}
    \TableCaptionRef{Standard \ac{RMA} Types and Names}
    \label{stdrmatypes}
  \end{center} 
\end{table}
