\apisummary{
    Performs an atomic fetch-and-add operation on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
TYPE shmem_fadd(TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by Table \ref{stdamotypes}.

\begin{Csynopsis}
TYPE shmem_<TYPENAME>_fadd(TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding \TYPENAME{} specified by Table \ref{stdamotypes}.

\begin{Fsynopsis}
INTEGER pe
INTEGER*4 SHMEM_INT4_FADD, ires_i4, value_i4
ires_i4 = SHMEM_INT4_FADD(dest, value_i4, pe)
INTEGER*8 SHMEM_INT8_FADD, ires_i8, value_i8
ires_i8 = SHMEM_INT8_FADD(dest, value_i8, pe)
\end{Fsynopsis}

\begin{apiarguments}

\apiargument{OUT}{dest}{The remotely accessible integer data object to be updated on
    the remote \ac{PE}. The type of \VAR{dest} should match that implied in the
    SYNOPSIS section.}
\apiargument{IN}{value}{The value to be atomically added to \VAR{dest}.  The
    type of \VAR{value} should match that implied in the SYNOPSIS section.}
\apiargument{IN}{pe}{An integer that indicates the \ac{PE} number on which
    \VAR{dest} is to be updated.  If you are using \Fortran, it must be a default
    integer value.}

\end{apiarguments}

\apidescription{
    \FUNC{shmem\_fadd} routines perform an atomic fetch-and-add operation.  An
    atomic fetch-and-add operation fetches the old \VAR{dest} and adds \VAR{value}
    to \VAR{dest} without the possibility of another atomic operation on the
    \VAR{dest} between the time of the fetch and the update.  These routines add
    \VAR{value} to \VAR{dest} on \VAR{pe} and return the previous contents of
    \VAR{dest} as an atomic operation.
}

\apidesctable{
    If you are using \Fortran, \VAR{dest} must be of the following type:
}{Routine}{Data type of \VAR{dest} and \VAR{source}}

\apitablerow{SHMEM\_INT4\_FADD}{\CONST{4}-byte integer}
\apitablerow{SHMEM\_INT8\_FADD}{\CONST{8}-byte integer}


\apireturnvalues{
    The contents that had been at the \VAR{dest} address on the remote \ac{PE}
    prior to the atomic addition operation.  The data type of the return value is
    the same as the \VAR{dest}.
}

\apinotes{
    None.
}

\begin{apiexamples}

\apicexample
	{The following \FUNC{shmem\_fadd} example is for C11 programs:}
        {./example_code/shmem_fadd_example.c}
        {}

\end{apiexamples}

\end{apidefinition}
