\apisummary{
    Returns a local pointer to a symmetric data object on the specified \ac{PE}.
}

\begin{apidefinition}

\begin{Csynopsis}
void *@\FuncDecl{shmem\_ptr}@(const void *dest, int pe);
\end{Csynopsis}

\begin{Fsynopsis}
POINTER (PTR, POINTEE)
INTEGER pe
PTR = @\FuncDecl{SHMEM\_PTR}@(dest, pe)
\end{Fsynopsis}


\begin{apiarguments}
\apiargument{IN}{dest}{The symmetric address of the remotely accessible data
    object to be referenced.}
\apiargument{IN}{pe}{An integer that indicates the \ac{PE} number on which \dest{} is to
		 be accessed.  When using \Fortran, it must be a  default
		 integer value.}
\end{apiarguments}

\apidescription{
    \FUNC{shmem\_ptr} returns an address that may be used to directly reference
    \dest{} on the specified \ac{PE}.  This address can be assigned to a
    pointer.  After that, ordinary loads and stores to \dest{} may be
    performed.  The address returned by \FUNC{shmem\_ptr} is a local address to
    a remotely accessible data object.  Providing this address to argument of
    an \openshmem routine that requires a symmetric address results in
    undefined behavior.
    
    The \FUNC{shmem\_ptr} routine can provide an efficient means to accomplish
    communication, for example when a sequence of reads and writes to a data
    object on a remote \ac{PE} does not match the access pattern provided in an
    \openshmem data transfer routine like \FUNC{shmem\_put} or
    \FUNC{shmem\_iget}.
}

\apireturnvalues{
    A local pointer to the remotely accessible \dest{} data object is returned
    when it can be accessed using memory loads and stores.  Otherwise, a null
    pointer is returned.
}

\apinotes{
    When calling \FUNC{shmem\_ptr}, \dest{} is the address of the referenced
    symmetric data object on the calling \ac{PE}.
}

\begin{apiexamples}

\apifexample
    { This  \Fortran  program calls \FUNC{shmem\_ptr} and then \ac{PE} 0 writes to
    the \VAR{BIGD} array on \ac{PE} 1: }
    {./example_code/shmem_ptr_example.f90 }
    {}
    
\apicexample
    {This is the equivalent program written in \Cstd[11]:}
    {./example_code/shmem_ptr_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
