\apisummary{
    Registers the arrival of a \ac{PE} at a \newtext{synchronization point} \oldtext{barrier} and suspends \ac{PE}
    execution until all other \acp{PE} \newtext{in the default team} arrive at \newtext{a synchronization point} \oldtext{the barrier}.
}

\begin{apidefinition}

\begin{Csynopsis}
void @\FuncDecl{shmem\_sync\_all}@(void);
\end{Csynopsis}

\begin{apiarguments}

    \apiargument{None.}{}{}

\end{apiarguments}

\apidescription{

  \newtext{%
    This routine blocks the calling \ac{PE} until all \acp{PE} in the
    default team have called \FUNC{shmem\_sync\_all}.
  }
  \oldtext{%
    The \FUNC{shmem\_sync\_all} routine registers the arrival of a \ac{PE} at a
    barrier. Barriers are a fast mechanism for synchronizing all \acp{PE} at
    once.  This routine blocks the \ac{PE} until all \acp{PE} have called
    \FUNC{shmem\_sync\_all}.
  }
    In a multithreaded \openshmem program, only the calling thread is
    blocked.

    In contrast with the \FUNC{shmem\_barrier\_all} routine,
    \FUNC{shmem\_sync\_all} only ensures completion and visibility of previously issued memory
    stores and does not ensure completion of remote memory updates issued via
    \openshmem routines.
}

\apireturnvalues{
    None.
}

\apinotes{
  \newtext{%
    The \FUNC{shmem\_sync\_all} routine is equivalent to calling
    \FUNC{shmem\_team\_sync} on the default team.
  }
  \oldtext{%
    The \FUNC{shmem\_sync\_all} routine can be used to portably ensure that
    memory access operations observe remote updates in the order enforced by the
    initiator \acp{PE}, provided that the initiator PE ensures completion of remote
    updates with a call to \FUNC{shmem\_quiet} prior to the call to the
    \FUNC{shmem\_sync\_all} routine.
  }
}

\end{apidefinition}
