\apisummary{
    This nonblocking atomic operation performs an atomic swap to a remote data
    object.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_atomic\_swap\_nbi}@(TYPE *fetch, TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_atomic\_swap\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the extended \ac{AMO} types specified by
Table~\ref{extamotypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_swap\_nbi}@(TYPE *fetch, TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_swap\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the extended \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{extamotypes}.

\begin{apiarguments}
  \apiargument{IN}{ctx}{A context handle specifying the context on which to
      perform the operation. When this argument is not provided, the
      operation is performed on the default context.}
  \apiargument{OUT}{fetch}{Local address of data object to be updated.
      The type of \VAR{fetch} should match that implied in the SYNOPSIS section.}
  \apiargument{OUT}{dest}{Symmetric address of the destination data object.
      The type of \dest{} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{value}{The value to be atomically written to the remote
      \ac{PE}.
      The type of \VAR{value} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{pe}{\ac{PE} number of the remote \ac{PE} relative to the team associated
      with the given \VAR{ctx} when provided, or the default context otherwise.}
\end{apiarguments}

\apidescription{
    The nonblocking \FUNC{shmem\_atomic\_swap\_nbi} routines perform an atomic
    swap operation. This routine returns after initiating the operation. The
    operation is considered complete after a subsequent call to
    \FUNC{shmem\_quiet}. At the completion of \FUNC{shmem\_quiet}, it has written
    \VAR{value} into \dest{} on \ac{PE} and fetched the prior contents of
    \dest{} into \VAR{fetch} local data object.
}

\apireturnvalues{
    None.
}

\end{apidefinition}
