\apisummary{
  Atomically perform a fetching bitwise AND operation on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
TYPE @\FuncDecl{shmem\_atomic\_fetch\_and}@(TYPE *dest, TYPE value, int pe);
TYPE @\FuncDecl{shmem\_atomic\_fetch\_and}@(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the bitwise \ac{AMO} types specified by
Table~\ref{bitamotypes}.

\begin{Csynopsis}
TYPE @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_fetch\_and}@(TYPE *dest, TYPE value, int pe);
TYPE @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_fetch\_and}@(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the bitwise \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{bitamotypes}.

\begin{apiarguments}

  \apiargument{IN}{ctx}{\oldtext{The context on which to perform the operation.} \newtext{A context handle specifying the context on which to perform the operation.}
    When this argument is not provided, the operation is performed on
    \oldtext{\CONST{SHMEM\_CTX\_DEFAULT}} \newtext{the default context}.}
  \apiargument{OUT}{dest}{A pointer to the remotely accessible data object to
    be updated.}
  \apiargument{IN}{value}{The operand to the bitwise AND operation.}
  \apiargument{IN}{pe}{An integer value for the \ac{PE} on which \VAR{dest}
    is to be updated.}

\end{apiarguments}

\apidescription{
  \FUNC{shmem\_atomic\_fetch\_and} atomically performs a fetching bitwise AND
  on the remotely accessible data object pointed to by \VAR{dest} at PE
  \VAR{pe} with the operand \VAR{value}.
  \newtext{
  If the context handle \VAR{ctx} does not correspond to a valid context,
  the behavior is undefined.
  }
}

\apireturnvalues{
  The value pointed to by \VAR{dest} on PE \VAR{pe} immediately before the
  operation is performed.
}

\apinotes{
  None.
}

\end{apidefinition}
