\apisummary{
    Performs an atomic fetch-and-increment  operation on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
TYPE shmem_atomic_fetch_inc(TYPE *dest, int pe);
TYPE shmem_atomic_fetch_inc(shmem_ctx_t ctx, TYPE *dest, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by
Table~\ref{stdamotypes}.

\begin{Csynopsis}
TYPE shmem_<TYPENAME>_atomic_fetch_inc(TYPE *dest, int pe);
TYPE shmem_ctx_<TYPENAME>_atomic_fetch_inc(shmem_ctx_t ctx, TYPE *dest, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{stdamotypes}.

\begin{Fsynopsis}
INTEGER pe
INTEGER*4 SHMEM_INT4_FINC, ires_i4
ires_i4 = SHMEM_INT4_FINC(dest, pe)
INTEGER*8 SHMEM_INT8_FINC, ires_i8
ires_i8 = SHMEM_INT8_FINC(dest, pe)
\end{Fsynopsis}


\begin{apiarguments}

\apiargument{IN}{ctx}{The context on which to perform the operation.
    When this argument is not provided, the operation is performed on
    \CONST{SHMEM\_CTX\_DEFAULT}.}
\apiargument{OUT}{dest}{The remotely accessible integer data object to be updated
    on the remote \ac{PE}. The type of \dest{} should match that implied in the
    SYNOPSIS section.}
\apiargument{IN}{pe}{An integer that indicates the \ac{PE} number on which
    \dest{} is to be updated.  When using \Fortran, it must be a default
    integer value.}

\end{apiarguments}


\apidescription{
   These routines perform a fetch-and-increment operation.  The \dest{} on
   \ac{PE} \VAR{pe} is increased by one and the routine returns the previous
   contents of \dest{} as an atomic operation.
}

\apidesctable{
    When using \Fortran, \VAR{dest} must be of the following type:
}{Routine}{Data type of \VAR{dest}}

\apitablerow{SHMEM\_INT4\_FINC}{\CONST{4}-byte integer}
\apitablerow{SHMEM\_INT8\_FINC}{\CONST{8}-byte integer}

\apireturnvalues{
    The contents that had been at the \dest{} address on the remote \ac{PE} prior to
    the increment.  The data type of the return value is the same as the \dest.
}

\apinotes{
    As of \openshmem[1.4], the \Cstd[11] and \CorCpp interfaces
    \FUNC{shmem\_fetch\_inc} and \FUNC{shmem\_TYPENAME\_fetch\_inc} have been
    deprecated. Their behavior and call signature are identical to the
    respective replacement interfaces, \FUNC{shmem\_atomic\_fetch\_inc} and
    \FUNC{shmem\_TYPENAME\_atomic\_fetch\_inc}, subject to the constraints
    that the deprecated interfaces do not accept a context argument and
    are only supported for \CTYPE{int}, \CTYPE{long}, and \CTYPE{long~long}
    types.
}

\begin{apiexamples}

\apicexample
    {The following \FUNC{shmem\_atomic\_fetch\_inc} example is for
    \Cstd[11] programs:}
    {./example_code/shmem_atomic_fetch_inc_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
