\apisummary{
    A collective operation that releases all resources used by the \openshmem
    library.  This only terminates the \openshmem portion of a program, not the
    entire program.
}

\begin{apidefinition}

\begin{Csynopsis}
void @\FuncDecl{shmem\_finalize}@(void);
\end{Csynopsis}

\begin{apiarguments}
    \apiargument{None.}{}{}
\end{apiarguments}

\apidescription{
    \FUNC{shmem\_finalize} ends the \openshmem
    portion of a program previously initialized by \FUNC{shmem\_init} or \FUNC{shmem\_init\_thread}.
   This is a collective
    operation that requires all \acp{PE} to participate in the call.

    An \openshmem program may perform a series of matching
    initialization and finalization calls.
    The last call to \FUNC{shmem\_finalize} in this series
    releases all resources used by the \openshmem library.
    This call destroys all teams created by the \openshmem program.
    As a result, all shareable contexts are destroyed.
    The user is
    responsible for destroying all contexts with the
    \CONST{SHMEM\_CTX\_PRIVATE} option enabled prior to this call;
    otherwise, the behavior is undefined.

    The last call to \FUNC{shmem\_finalize} performs an implicit global barrier
    to ensure that pending communications are completed and that no resources
    are released until all \acp{PE} have entered \FUNC{shmem\_finalize}. All
    other calls to \FUNC{shmem\_finalize} perform an operation semantically
    equivalent to \FUNC{shmem\_barrier\_all} and return without freeing any
    \openshmem resources.

    The last call to \FUNC{shmem\_finalize} causes the \openshmem library
    to enter an uninitialized state. No further \openshmem calls may be
    made until an \openshmem initialization routine is called.
    All processes
    that represent the \acp{PE} will still exist after the
    call to \FUNC{shmem\_finalize} returns, but they will no longer have access
    to resources that have been released.
}

\apireturnvalues{
    None.
}

\apinotes{
    The last call to \FUNC{shmem\_finalize} releases all resources used by the \openshmem library
    including the symmetric memory heap and pointers initiated by
    \FUNC{shmem\_ptr}. This collective operation requires all \acp{PE} to
    participate in the call, not just a subset of the \acp{PE}. The
    non-\openshmem portion of a program may continue after a call to
    \FUNC{shmem\_finalize} by all \acp{PE}.

    Calls to \FUNC{shmem\_finalize} that are not the last in a series of
    initialization and finalization calls do not free any \openshmem resources.
    Thus, teams, contexts, or symmetric memory allocations may be leaked until
    the final call to \FUNC{shmem\_finalize}. Applications that perform
    multiple initialization and finalization calls should free resources prior
    to calling \FUNC{shmem\_finalize} to avoid such leaks.
}

\begin{apiexamples}

\apicexample
    {The following finalize example is for \Cstd[11] programs:}
    {./example_code/shmem_finalize_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
