\apisummary{
    Controls data cache utilities. 
    (This routine is deprecated and is provided for backwards compatibility. 
    Implementations must include it, and the routines should function properly 
    while notifying the user about deprecation of its use.)
}

\begin{apidefinition}

\begin{Csynopsis}
void shmem_clear_cache_inv(void);
void shmem_set_cache_inv(void);
void shmem_clear_cache_line_inv(void *dest);
void shmem_set_cache_line_inv(void *dest);
void shmem_udcflush(void);
void shmem_udcflush_line(void *dest);
\end{Csynopsis}

\begin{Fsynopsis}
CALL SHMEM_CLEAR_CACHE_INV
CALL SHMEM_SET_CACHE_INV
CALL SHMEM_SET_CACHE_LINE_INV(dest)
CALL SHMEM_UDCFLUSH
CALL SHMEM_UDCFLUSH_LINE(dest)
\end{Fsynopsis}

\begin{apiarguments}

\apiargument{IN}{dest}{A data object that is local to the \ac{PE}.  \VAR{dest}
    can be of any noncharacter type. If you are using \Fortran, it can be of any
    kind.}

\end{apiarguments}

\apidescription{   
    \FUNC{shmem\_set\_cache\_inv} enables automatic cache coherency mode.
    
    \FUNC{shmem\_set\_cache\_line\_inv} enables automatic cache coherency mode for
    the cache line associated with the address of \VAR{dest} only.
    
    \FUNC{shmem\_clear\_cache\_inv} disables automatic cache coherency mode
    previously enabled by \FUNC{shmem\_set\_cache\ \_inv} or
    \FUNC{shmem\_set\_cache\_line\_inv}.
    
    \FUNC{shmem\_udcflush} makes the entire user data cache coherent.
    
    \FUNC{shmem\_udcflush\_line} makes coherent the cache line that corresponds with
    the address specified by \VAR{dest}.
}

\apireturnvalues{
    None.
}

\apinotes{
    These routines have been retained for improved backward compatibility with
    legacy architectures.  They are not required to be supported by implementing
    them as \VAR{no-ops} and where used, they may have no effect on cache line
    states.
}

\begin{apiexamples}

None.

\end{apiexamples}

\end{apidefinition}
