\color{Green}
\apisummary{
    The put with signal routines provide a method for copying data from a
    contiguous local data object to a data object on a specified \ac{PE}
    and set a remote flag to signal completion.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_put\_signal}@(TYPE *dest, const TYPE *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
void @\FuncDecl{shmem\_put\_signal}@(shmem_ctx_t ctx, TYPE *dest, const TYPE *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{RMA} types specified by Table \ref{stdrmatypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_put\_signal}@(TYPE *dest, const TYPE *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_put\_signal}@(shmem_ctx_t ctx, TYPE *dest, const TYPE *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{RMA} types and has a corresponding \TYPENAME{} specified by Table \ref{stdrmatypes}.

\begin{CsynopsisCol}
void @\FuncDecl{shmem\_put\FuncParam{SIZE}\_signal}@(void *dest, const void *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
void @\FuncDecl{shmem\_ctx\_put\FuncParam{SIZE}\_signal}@(shmem_ctx_t ctx, void *dest, const void *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
\end{CsynopsisCol}
where \SIZE{} is one of \CONST{8, 16, 32, 64, 128}.

\begin{CsynopsisCol}
void @\FuncDecl{shmem\_putmem\_signal}@(void *dest, const void *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
void @\FuncDecl{shmem\_ctx\_putmem\_signal}@(shmem_ctx_t ctx, void *dest, const void *source, size_t nelems, uint64_t *sig_addr, uint64_t signal, int pe);
\end{CsynopsisCol}

\begin{apiarguments}
    \apiargument{IN}{ctx}{The context on which to perform the operation.
      When this argument is not provided, the operation is performed on
      \CONST{SHMEM\_CTX\_DEFAULT}.}
    \apiargument{OUT}{dest}{Data object to be updated on the remote \ac{PE}. This
    data object must be remotely accessible.}
    \apiargument{IN}{source}{Data object containing the data to be copied.}
    \apiargument{IN}{nelems}{Number of elements in the \VAR{dest} and \VAR{source}
    arrays. \VAR{nelems} must be of type \VAR{size\_t} for \Cstd. When using
    \Fortran, it must be a constant, variable, or array element of default
    integer type.}
    \apiargument{OUT}{sig\_addr}{Signal data object to be updated on the remote
    \ac{PE} to be updated as the signal. This signal data object must be
    remotely accessible and it can be in the same or differnt memory segment
    as the \VAR{dest} data object.}
    \apiargument{IN}{signal}{Unsigned 64-bit value used to set the remote
    \VAR{sig\_addr} signal data object.}
    \apiargument{IN}{pe}{\ac{PE} number of the remote \ac{PE}. \VAR{pe} must be
    of type integer. When using \Fortran, it must be a constant, variable,
    or array element of default integer type.}
\end{apiarguments}

\apidescription{
    The routines return after the data has been copied out of the \source{}
    array on the local \ac{PE}. The delivery of \signal flag on the remote
    \ac{PE} guarantees the delivery of data words into the data object on the
    remote \ac{PE}. Furthermore, two successive put with signal routines or
    a successive put followed by a put with signal routine may deliver data
    out of order unless a call to \FUNC{shmem\_fence} is introduced between
    the two calls and the delivery of the \signal flag on the remote \ac{PE}
    guarantees only the delivery of its corresponding data object on the
    remote \ac{PE}.
 }

\apidesctable{
    The \dest{} and \source{} data objects must conform to certain typing
    constraints, which are as follows:}
    {Routine}{Data type of \VAR{dest} and \VAR{source}}
    \apitablerow{shmem\_putmem}{Any data type. nelems is scaled in bytes.}
    \apitablerow{shmem\_put8}{Any noncharacter type that
        has a storage size equal to \CONST{8} bits.}
    \apitablerow{shmem\_put16}{Any noncharacter type that
        has a storage size equal to \CONST{16} bits.}
    \apitablerow{shmem\_put32}{Any noncharacter type
        that has a storage size equal to \CONST{32} bits.}
    \apitablerow{shmem\_put64}{Any noncharacter type that
        has a storage size equal to \CONST{64} bits.}
    \apitablerow{shmem\_put128}{Any noncharacter type that has a
        storage size equal to \CONST{128} bits.}

\apireturnvalues{
    None.
}
\apinotes{
}

\begin{apiexamples}

\apicexample
    { The following \FUNC{shmem\_put\_signal} example is for \Cstd[11] programs:}
    {./example_code/shmem_put_signal_example.c}
    {}
\end{apiexamples}

\end{apidefinition}
\color{Black}
