\apisummary{
    Releases, locks, and tests a mutual exclusion memory lock on a specific \ac{PE}.
}
\begin{apidefinition}

\begin{Csynopsis}
void shmem_clear_lock_pe(volatile long *lock, int pe);
void shmem_set_lock_pe(volatile long *lock, int pe);
int shmem_test_lock_pe(volatile long *lock, int pe);
\end{Csynopsis}

\begin{Fsynopsis}
INTEGER pe, lock, SHMEM_TEST_LOCK
CALL SHMEM_CLEAR_LOCK_PE(lock, pe)
CALL SHMEM_SET_LOCK_PE(lock, pe)
I = SHMEM_TEST_LOCK_PE(lock, pe)
\end{Fsynopsis}

\begin{apiarguments}
\apiargument{IN}{lock}{A symmetric data object that is a scalar variable or an array
    of  length \CONST{1}.  This data  object  must  be set to \CONST{0} on all
    \ac{PE}s prior to the first use.  \VAR{lock}  must  be  of type \CONST{long}.
    If you are using \Fortran, it must be of default kind.}
\apiargument{IN}{pe}{An integer that indicates the \ac{PE} number upon which lock is
    to be updated. If you are using Fortran, it must be a default integer value.}
\end{apiarguments}

\apidescription{
    The \FUNC{shmem\_set\_lock\_pe} routine sets a mutual exclusion lock on a
    specific \ac{PE} after waiting for the lock to be freed by any other \ac{PE}
    currently holding the lock.  Waiting \ac{PE}s are assured of getting the lock in
    a first-come, first-served manner. The \FUNC{shmem\_clear\_lock\_pe} routine
    releases a lock on a specific \ac{PE} previously set by
    \FUNC{shmem\_set\_lock\_pe} after ensuring that all local and remote stores
    initiated in the critical region are complete.  The \FUNC{shmem\_test\_lock\_pe}
    routine sets a mutual exclusion lock on a specific \ac{PE} only if it is
    currently cleared.  By using this routine, a \ac{PE} can avoid blocking on a set
    lock. If the lock is currently set, the routine returns without waiting. These
    routines are appropriate for protecting a critical region from simultaneous
    update by multiple \ac{PE}s at a fine-grain level.
}

\apireturnvalues{
    The \FUNC{shmem\_test\_lock} routine returns \CONST{0} if  the lock  was
    originally cleared and  this  call was  able  to set the lock.  A value of
    \CONST{1} is returned if the lock had been set and the call returned without
    waiting to set the lock.
}

\apinotes{
    The term symmetric data object is defined in Section \ref{subsec:memory_model}.
    The lock variable should always be initialized to zero and accessed only by the
    \openshmem locking \ac{API}.  Changing the value of the lock variable by other
    means without using the \openshmem \ac{API}, can lead to undefined behavior.
    Mixing the \FUNC{shmem\_lock} and \FUNC{shmem\_lock\_pe} routines with the same
    lock can lead to undefined behavior.
}

\begin{apiexamples}

\apicexample
    {The following example uses \FUNC{shmem\_set\_lock\_pe} and
    \FUNC{shmem\_clear\_lock\_pe} in a \Clang{} program.}
    {./example_code/shmem_lock_pe_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
