\color{Green}
\apisummary{
    This nonblocking routine performs an atomic fetch-and-increment operation
    on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_atomic\_fetch\_inc\_nbi}@(TYPE *fetch, TYPE *dest, int pe);
void @\FuncDecl{shmem\_atomic\_fetch\_inc\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by
Table~\ref{stdamotypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_fetch\_inc\_nbi}@(TYPE *fetch, TYPE *dest, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_fetch\_inc\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{stdamotypes}.

\begin{apiarguments}

\apiargument{IN}{ctx}{The context on which to perform the operation.
    When this argument is not provided, the operation is performed on
    \CONST{SHMEM\_CTX\_DEFAULT}.}
\apiargument{OUT}{fetch}{Local data object to be updated.}
\apiargument{OUT}{dest}{The remotely accessible integer data object to be updated
    on the remote \ac{PE}. The type of \dest{} should match that implied in the
    SYNOPSIS section.}
\apiargument{IN}{pe}{An integer that indicates the \ac{PE} number on which
    \dest{} is to be updated.  When using \Fortran, it must be a default
    integer value.}

\end{apiarguments}


\apidescription{
   These nonblocking routines perform a atomic fetch-and-increment operation.
   This routine returns after posting the operation. The operation is considered
   complete after a subsequent call to \FUNC{shmem\_quiet}. At the completion of
   \FUNC{shmem\_quiet}, the \dest{} on \ac{PE} \VAR{pe} is increased by one and
   the routine fetches the previous contents of \dest{} as an atomic operation
   into the \VAR{fetch} local data object.
}

\apireturnvalues{
    None.
}

\apinotes{
    None.
}

\end{apidefinition}
\color{Black}
