\apisummary{
    Performs all operations described in the \FUNC{shmem\_barrier\_all} interface
    but with respect to \newtext{a specified \ac{PE} team or}
    a subset of \acp{PE} defined by \oldtext{the} \newtext{an} active set \newtext{triple}.
}

\begin{apidefinition}

{\color{ForestGreen}
\begin{C11synopsis}
void @\FuncDecl{shmem\_barrier}@(shmem_ctx_t ctx);
\end{C11synopsis}
}

% These separate synopses should be merged when the color highlighting removed,
% preferably with shmem_ctx_barrier listed first.
\begin{Csynopsis}
void @\FuncDecl{shmem\_barrier}@(int PE_start, int logPE_stride, int PE_size, long *pSync);
\end{Csynopsis}
{\color{ForestGreen}
\begin{CsynopsisCol}
void @\FuncDecl{shmem\_ctx\_barrier}@(shmem_ctx_t ctx);
\end{CsynopsisCol}
}

\begin{Fsynopsis}
INTEGER PE_start, logPE_stride, PE_size
INTEGER pSync(SHMEM_BARRIER_SYNC_SIZE)
CALL @\FuncDecl{SHMEM\_BARRIER}@(PE_start, logPE_stride, PE_size, pSync)
\end{Fsynopsis}

\begin{apiarguments}

\newtext{
\apiargument{IN}{ctx}{The context on which to perform the operation.
  When this argument is not provided, the operation is performed on the
  default context.}
}
\apiargument{IN}{PE\_start}{The lowest \ac{PE} number of the active set of \acp{PE}.
    \VAR{PE\_start} must be of type integer.  When using \Fortran, it must be
    a default integer value.}
\apiargument{IN}{logPE\_stride}{The log (base 2) of the stride between consecutive
    \ac{PE} numbers in the active set.  \VAR{logPE\_stride} must be of type integer.
    When using \Fortran, it must be a default integer value.}
\apiargument{IN}{PE\_size}{The number of  \acp{PE} in the active set.  \VAR{PE\_size}
    must be of type integer.  When using  \Fortran, it must be a default
    integer value.}
\apiargument{IN}{pSync}{
    A symmetric work array of size \CONST{SHMEM\_BARRIER\_SYNC\_SIZE}.
    In \CorCpp, \VAR{pSync} must be an array of elements of type \CTYPE{long}.
    In \Fortran, \VAR{pSync} must be an array of elements of default integer type.
    Every element
    of this array must be initialized to \CONST{SHMEM\_SYNC\_VALUE} before any of
    the \acp{PE} in the active set enter \FUNC{shmem\_barrier} the first time.}

\end{apiarguments}

\apidescription{
    \FUNC{shmem\_barrier} is a collective synchronization routine over
    \newtext {the \ac{PE} team associated with a communication context or} an active set.
    Control returns from \FUNC{shmem\_barrier} after all \acp{PE} in
    the \newtext{specified \ac{PE} team or} active set \oldtext{(specified by \VAR{PE\_start}, \VAR{logPE\_stride}, and
    \VAR{PE\_size})} have called \FUNC{shmem\_barrier}.
    \newtext{
    An active set is specified by the triple of values: \VAR{PE\_start},
    \VAR{logPE\_stride}, and \VAR{PE\_size}.
    }

    {\color{ForestGreen}
    The \FUNC{shmem\_barrier} and \FUNC{shmem\_ctx\_barrier} routines that
    accept a context handle \VAR{ctx} have the effect of a call to
    \FUNC{shmem\_ctx\_quiet} on the specified context, followed by a call to
    \FUNC{shmem\_team\_sync} on the team associated with the specified context.

    The \FUNC{shmem\_barrier} routine that accepts an active set triple
    has the effect of a call to \FUNC{shmem\_quiet}, which implicitly
    operates on the default context, followed by a call to \FUNC{shmem\_sync}
    with the same active set and \VAR{pSync} arguments.
    }

    As with all \openshmem collective routines, each of these routines assumes that
    only \acp{PE} in the active set call the routine.  If a \ac{PE} not  in  the
    active set calls an \openshmem collective routine, the behavior is undefined.

    \begin{FeedbackRequest}
      Do we need to say something like the above for team-based collectives?
      We already say that teams are not portable across PEs, so only the PE
      that created the team could invoke it in a collective without undefined
      behavior.

      Should we have a harder partition between the description text between
      the team- and active set-based API (since the active set and pSync
      requirements don't affect the team call)?
    \end{FeedbackRequest}
    
    The values of arguments \VAR{PE\_start}, \VAR{logPE\_stride}, and \VAR{PE\_size}
    must be the same value on all \acp{PE} in the active set.  The same work array must be
    passed in \VAR{pSync} to all \acp{PE} in the active set.
    
    \newtext{The} \FUNC{shmem\_barrier} \newtext{routines} ensure\oldtext{s} that all previously issued stores and remote
    memory updates, including \acp{AMO} and \ac{RMA} operations, \newtext{issued} \oldtext{done} by any of the
    \acp{PE} in the \newtext{\ac{PE} team or} active set on the default context are complete before returning.
    
    The  same  \VAR{pSync} array may be reused on consecutive calls   to
    \FUNC{shmem\_barrier} if the same active set is used.
}

\apireturnvalues{
    None.
}

\apinotes{
    If the \VAR{pSync} array is initialized at the run time, all
    \acp{PE} must be synchronized before the first call to \FUNC{shmem\_barrier}
    (e.g., by \FUNC{shmem\_barrier\_all}) to ensure the array has been initialized
    by all \acp{PE} before it is used.
    
    If  the active set does not change, \FUNC{shmem\_barrier} can  be called
    repeatedly with the same \VAR{pSync} array.  No additional synchronization
    beyond that implied by \FUNC{shmem\_barrier} itself is necessary in this case.

    The \FUNC{shmem\_barrier} routine can be used to
    portably ensure that memory access operations observe remote updates in the order
    enforced by initiator \acp{PE}.

    Calls to \FUNC{shmem\_ctx\_quiet} can be performed prior
    to calling the barrier routine to ensure completion of operations issued on
    additional contexts.
}

\begin{apiexamples}

\apicexample
	{The following barrier example is for \Cstd[11] programs:}
	{./example_code/shmem_barrier_example.c}
	{}

\end{apiexamples}

\end{apidefinition}
