\apisummary{
    Performs an atomic conditional swap on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
TYPE @\FuncDecl{shmem\_atomic\_compare\_swap}@(TYPE *dest, TYPE cond, TYPE value, int pe);
TYPE @\FuncDecl{shmem\_atomic\_compare\_swap}@(shmem_ctx_t ctx, TYPE *dest, TYPE cond, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by
Table~\ref{stdamotypes}.

\begin{Csynopsis}
TYPE @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_compare\_swap}@(TYPE *dest, TYPE cond, TYPE value, int pe);
TYPE @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_compare\_swap}@(shmem_ctx_t ctx, TYPE *dest, TYPE cond, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{stdamotypes}.

\begin{DeprecateBlock}
\begin{C11synopsis}
TYPE @\FuncDecl{shmem\_cswap}@(TYPE *dest, TYPE cond, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of \{\CTYPE{int}, \CTYPE{long}, \CTYPE{long long}\}.

\begin{Csynopsis}
TYPE @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_cswap}@(TYPE *dest, TYPE cond, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of \{\CTYPE{int}, \CTYPE{long}, \CTYPE{long long}\}
and has a corresponding \TYPENAME{} specified by Table~\ref{stdamotypes}.
\end{DeprecateBlock}

\begin{Fsynopsis}
INTEGER pe
INTEGER*4 SHMEM_INT4_CSWAP,  cond_i4, value_i4, ires_i4
ires\_i4 = @\FuncDecl{SHMEM\_INT4\_CSWAP}@(dest, cond_i4, value_i4, pe)
INTEGER*8 SHMEM_INT8_CSWAP,  cond_i8, value_i8, ires_i8
ires\_i8 = @\FuncDecl{SHMEM\_INT8\_CSWAP}@(dest, cond_i8, value_i8, pe)
\end{Fsynopsis}

\begin{apiarguments}
    \apiargument{IN}{ctx}{A context handle specifying the context on which to perform the operation.
        When this argument is not provided, the operation is performed on
        the default context.}
    \apiargument{OUT}{dest}{Symmetric address of the destination data object.
        The type of \dest{} should match that implied in the SYNOPSIS section.}
    \apiargument{IN}{cond}{\VAR{cond} is compared to the remote \VAR{dest}
        value. If \VAR{cond} and the remote \VAR{dest} are equal, then \VAR{value}
        is swapped into the remote \VAR{dest}; otherwise, the remote \VAR{dest} is
        unchanged.  In either case, the old value of the remote \VAR{dest} is
        returned as the routine return value. \VAR{cond} must be of the same data
        type as \VAR{dest}.}
    \apiargument{IN}{value}{The value to be atomically written to the remote \ac{PE}.
        The type of \VAR{value} should match that implied in the SYNOPSIS section.}
    \apiargument{IN}{pe}{An integer that indicates the \ac{PE} number upon which
        \VAR{dest} is to be updated. When using \Fortran, it must be a default
        integer value.}
\end{apiarguments}

\apidescription{
    The conditional swap routines conditionally update a \VAR{dest} data object on
    the specified \ac{PE} and return the prior contents of the data object in one
    atomic operation.
    If the context handle \VAR{ctx} does not correspond to a valid context,
    the behavior is undefined.
}
\apidesctable{
    When using \Fortran, \VAR{dest}, \VAR{cond}, and \VAR{value} must be of the following type:
}{Routine}{Data type of \VAR{dest}, \VAR{cond}, and \VAR{value}}

\apitablerow{SHMEM\_INT4\_CSWAP}{\CONST{4}-byte integer.}
\apitablerow{SHMEM\_INT8\_CSWAP}{\CONST{8}-byte integer.}


\apireturnvalues{
    The contents that had been in the \VAR{dest} data object on the remote
    \ac{PE} prior to the conditional swap. Data type is the same as the
    \VAR{dest} data type.
}

\apinotes{
    None.
}

\begin{apiexamples}

\apicexample
    {The following call ensures that the first \ac{PE} to execute the
    conditional swap will successfully write its \ac{PE} number to
    \VAR{race\_winner} on \ac{PE} \CONST{0}.}
    {./example_code/shmem_atomic_compare_swap_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
