\apisummary{
  Atomically perform a fetching bitwise exclusive OR (XOR) operation on a
  remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
TYPE @\FuncDecl{shmem\_atomic\_fetch\_xor}@(TYPE *dest, TYPE value, int pe);
TYPE @\FuncDecl{shmem\_atomic\_fetch\_xor}@(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the bitwise \ac{AMO} types specified by
Table~\ref{bitamotypes}.

\begin{Csynopsis}
TYPE @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_fetch\_xor}@(TYPE *dest, TYPE value, int pe);
TYPE @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_fetch\_xor}@(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the bitwise \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{bitamotypes}.

\begin{apiarguments}

  \apiargument{IN}{ctx}{A context handle specifying the context on which to perform the operation.
    When this argument is not provided, the operation is performed on
    the default context.}
  \apiargument{OUT}{dest}{Symmetric address of the destination data object.
    The type of \dest{} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{value}{The operand to the bitwise XOR operation.
    The type of \VAR{value} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{pe}{\ac{PE} number of the remote \ac{PE} relative to the team associated
    with the given \VAR{ctx} when provided, or the default context otherwise.}
\end{apiarguments}

\apidescription{
  \FUNC{shmem\_atomic\_fetch\_xor} atomically performs a fetching bitwise XOR
  on the remotely accessible data object pointed to by \VAR{dest} at PE
  \VAR{pe} with the operand \VAR{value}.
}

\apireturnvalues{
  The value pointed to by \VAR{dest} on PE \VAR{pe} immediately before the
  operation is performed.
}

\end{apidefinition}
