\apisummary{
    The nonblocking atomic routine performs an atomic fetch-and-add operation on
    a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_atomic\_fetch\_add\_nbi}@(TYPE *fetch, TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_atomic\_fetch\_add\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by
Table~\ref{stdamotypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_fetch\_add\_nbi}@(TYPE *fetch, TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_fetch\_add\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{stdamotypes}.

\begin{apiarguments}

  \apiargument{IN}{ctx}{A context handle specifying the context on which to
      perform the operation. When this argument is not provided, the operation
      is performed on the default context.}
  \apiargument{OUT}{fetch}{Local address of data object to be updated.
      The type of \VAR{fetch} should match that implied in the SYNOPSIS section.}
  \apiargument{OUT}{dest}{Symmetric address of the destination data object.
    The type of \dest{} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{value}{The operand to the atomic fetch-and-add operation.
      The type of \VAR{value} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{pe}{An integer that indicates the \ac{PE} number on which
      \VAR{dest} is to be updated.}

\end{apiarguments}

\apidescription{
    The nonblocking \FUNC{shmem\_atomic\_fetch\_add\_nbi} routines perform an
    atomic fetch-and-add operation. An atomic fetch-and-add operation fetches
    the old \VAR{dest} and adds \VAR{value} to \VAR{dest} without the
    possibility of another atomic operation on the \VAR{dest} between the time
    of the fetch and the update. This routine returns after initiating the
    operation. The operation is considered complete after a subsequent call to
    \FUNC{shmem\_quiet}. At the completion of \FUNC{shmem\_quiet}, \VAR{value}
    has been added to \VAR{dest} on \VAR{pe} and the prior contents of \VAR{dest}
    fetched into the \VAR{fetch} local data object.
}

\apireturnvalues{
    None.
}

\apinotes{
    None.
}

\end{apidefinition}
