\apisummary{
    Registers the arrival of a \ac{PE} at a barrier and returns immediately. It completes when all \acp{PE}
    arrive at the barrier and all local updates and remote memory updates on the default context are completed. 
    }

\begin{apidefinition}

\begin{Csynopsis}
void @\FuncDecl{shmem\_barrier\_all\_nb}@(shmem_req_h *request);
\end{Csynopsis}

\begin{apiarguments}

    \apiargument{OUT}{request}{An opaque request handle identifying the
    collective operation.}

\end{apiarguments}

\apidescription{   
    Similar to the \FUNC{shmem\_barrier\_all} routine, the nonblocking \FUNC{shmem\_barrier\_all\_nb}
    is a mechanism for synchronizing all \acp{PE} in the world team at
    once. This routine completes when all \acp{PE} have called
    \FUNC{shmem\_barrier\_all\_nb}. 

    A call to the nonblocking barrier routine initiates the operation and returns
    immediately without necessarily completing the operation. On success, 
    an opaque request handle is created and returned. The
    operation is completed after at least one call to \FUNC{shmem\_req\_test} or
    a call to \FUNC{shmem\_req\_wait}. When the operation is complete, the
    request handle is deallocated and cannot be reused.

    Prior to completion, \FUNC{shmem\_barrier\_all\_nb}
    ensures completion of all previously issued memory stores and remote memory
    updates issued on the default context via \openshmem \acp{AMO} and
    \ac{RMA} routine calls such
    as \FUNC{shmem\_int\_add}, \FUNC{shmem\_put32},
    \FUNC{shmem\_put\_nbi}, and \FUNC{shmem\_get\_nbi}.
}

\apireturnvalues{
    None.
}

\apinotes{
}

\end{apidefinition}
