\apisummary{
    The nonblocking atomic routine provides a method for performing an atomic
    conditional swap on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_atomic\_compare\_swap\_nbi}@(TYPE *fetch, TYPE *dest, TYPE cond, TYPE value, int pe);
void @\FuncDecl{shmem\_atomic\_compare\_swap\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE cond, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by
Table~\ref{stdamotypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_compare\_swap\_nbi}@(TYPE *fetch, TYPE *dest, TYPE cond, TYPE value, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_compare\_swap\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE cond, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{stdamotypes}.

\begin{apiarguments}
  \apiargument{IN}{ctx}{A context handle specifying the context on which to
      perform the operation. When this argument is not provided, the operation
      is performed on the default context.}
  \apiargument{OUT}{fetch}{Local data object to be updated.}
  \apiargument{OUT}{dest}{The remotely accessible data object to be updated on
      the remote \ac{PE}. }
  \apiargument{IN}{cond}{\VAR{cond} is compared to the remote \VAR{dest}
      value. If \VAR{cond} and the remote \VAR{dest} are equal, then \VAR{value}
      is swapped into the remote \VAR{dest}; otherwise, the remote \VAR{dest} is
      unchanged.}
  \apiargument{IN}{value}{The value to be atomically written to the remote
      \ac{PE}. }
  \apiargument{IN}{pe}{An integer that indicates the \ac{PE} number upon which
      \VAR{dest} is to be updated.}
\end{apiarguments}

\apidescription{
    The nonblocking conditional swap routines conditionally update a \VAR{dest}
    data object on the specified \ac{PE} as an atomic operation and fetches the prior contents of the
    \VAR{dest} data object into the \VAR{fetch} local data object.
    This routine returns after initiating the operation. The operation
    is considered complete after a subsequent call to \FUNC{shmem\_quiet}. At the
    completion of \FUNC{shmem\_quiet}, prior contents of the \VAR{dest} data
    object have been fetched into \VAR{fetch} local data object and the
    contents of \VAR{value} have been conditionally updated into \VAR{dest} on the
    remote \ac{PE}.
}

\apireturnvalues{
    None.
}

\apinotes{
    None.
}

\end{apidefinition}
