\apisummary{
    Broadcasts a block of data from one \ac{PE} to one or more destination
    \acp{PE}.
}

\begin{apidefinition}

\begin{Csynopsis}
void @\FuncDecl{shmem\_team\_broadcast32}@(shmem_team_t team, void *dest, const void *source, size_t nelems, int PE_root);
void @\FuncDecl{shmem\_team\_broadcast64}@(shmem_team_t team, void *dest, const void *source, size_t nelems, int PE_root);
\end{Csynopsis}

\begin{apiarguments}

\apiargument{IN}{team}{A valid \openshmem team handle to a team which has been created without
    disabling support for collective operations.}
\apiargument{OUT}{dest}{A symmetric data object. See the table below in this description
    for allowable types} 
\apiargument{IN}{source}{A symmetric data object that can be of any data type
    that is permissible for the \dest{} argument.}
\apiargument{IN}{nelems}{The number of elements in \source{}.  For
    \FUNC{shmem\_team\_broadcast32}, this is the number of
    32-bit halfwords. nelems must be of type \CTYPE{size\_t} in \Cstd.}
\apiargument{IN}{PE\_root}{Zero-based ordinal of the \ac{PE}, with respect to
    the team, from which the data is copied. Must be greater than or equal to
    0 and less than N-1, where N is the result of calling \FUNC{shmem\_team\_n\_pes(team)}.
    \VAR{PE\_root} must be of type \CTYPE{int}.} 

\end{apiarguments}

\apidescription{   
    \openshmem broadcast routines are collective routines over an existing team.
    They copy data object \source{} on the processor specified by \VAR{PE\_root}
    and store the values at \dest{} on the other \acp{PE} that are members of the
    team. The data is not copied to the \dest{} area on the root \ac{PE}.
    
    If the team has been created with the \LibConstRef{SHMEM\_TEAM\_NOCOLLECTIVE} option,
    it will not have the required support structures to complete this routine. If
    such a team is passed to this or any other team collective routine, the behavior
    is undefined.

    As with all \openshmem routines where the operation occurs for a given team -
    either when the team is an argument to the routine, or when the team is an attribute
    of the context argument to a routine - the \ac{PE} numbers are relative to the team,
    and must be in the range of 0 to N-1, where N is the result of \FUNC{shmem\_team\_n\_pes(team)}.
    
    The values of the argument \VAR{PE\_root} must be the same value on all \acp{PE} in
    the team. The same \dest{} and \source{} data objects must be passed by all \acp{PE}
    in the team.

    Upon return from a broadcast routine, the following are true for the local
    \ac{PE}:
    \begin{itemize}
    \item If the current \ac{PE} is not the root \ac{PE},
      the \dest{} data object is updated.
    \item The \source{} data object may be safely reused.
    \end{itemize}

    Error checking will be done to ensure a valid team handle is provided.
    All errors are considered fatal and will result in the job aborting with
    an informative error message.
}

\apidesctable{
The  \dest{}  and \source{} data  objects must conform to certain typing
constraints, which are as follows:
}{Routine}{Data type of \VAR{dest} and \VAR{source}}

\apitablerow{shmem\_team\_broadcast64}{Any noncharacter
    type that has an element size of \CONST{64} bits.
    \CorCpp{} structures are NOT allowed.}
\apitablerow{shmem\_team\_broadcast32}{Any noncharacter
    type that has an element size of \CONST{32} bits.
    \CorCpp{} structures are NOT allowed.}

\apireturnvalues{
    None.
}

\apinotes{
    All \openshmem team collective routines use symmetric data structures associated
    with the team to synchronize and share data. By default, new teams that result from
    split operations will have these structures.

    Multiple calls to the same collective routine for the same team by different threads
    must avoid any simultaneous updates to these structures. In general, this will mean
    that threads will need to serialize access to teams.
}

\end{apidefinition}
