\apisummary{
    Performs an atomic swap to a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
TYPE shmem_swap(TYPE *dest, TYPE value, int pe);
TYPE shmem_swap(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the extended \ac{AMO} types specified by Table \ref{extamotypes}.

\begin{Csynopsis}
TYPE shmem_<TYPENAME>_swap(TYPE *dest, TYPE value, int pe);
TYPE shmem_ctx_<TYPENAME>_swap(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the extended \ac{AMO} types and has a corresponding \TYPENAME{} specified by Table \ref{extamotypes}.

\begin{Fsynopsis}
INTEGER SHMEM_SWAP, value, pe
ires = SHMEM_SWAP(dest, value, pe) 
INTEGER*4 SHMEM_INT4_SWAP, value_i4, ires_i4
ires_i4 = SHMEM_INT4_SWAP(dest, value_i4, pe) 
INTEGER*8 SHMEM_INT8_SWAP, value_i8, ires_i8
ires_i8 = SHMEM_INT8_SWAP(dest, value_i8, pe)
REAL*4 SHMEM_REAL4_SWAP, value_r4, res_r4
res_r4 = SHMEM_REAL4_SWAP(dest, value_r4, pe) 
REAL*8 SHMEM_REAL8_SWAP, value_r8, res_r8
res_r8 = SHMEM_REAL8_SWAP(dest, value_r8, pe)
\end{Fsynopsis}

\begin{apiarguments}
    \newtext{
    \apiargument{IN}{ctx}{Context on which to perform the operation.  When this
        argument is not provided, \CONST{SHMEM\_CTX\_DEFAULT} is used.}
    }
    \apiargument{OUT}{dest}{The  remotely accessible integer data object to be
        updated on the remote \ac{PE}.	 If you are using \CorCpp, the type of
        \dest{} should match that  implied in the SYNOPSIS section.}
    \apiargument{IN}{value}{The value to be atomically written to the remote
        \ac{PE}. \VAR{value}  is the same type as \dest.}
    \apiargument{IN}{pe}{ An integer that indicates the \ac{PE} number on which
        \dest{} is to be updated. If you are using \Fortran, it must be a default
        integer value.}
\end{apiarguments}

\apidescription{
    \FUNC{shmem\_swap}  performs  an atomic swap operation. It writes \VAR{value}
    into \dest{} on \ac{PE} and returns the previous contents of \dest{} as an
    atomic operation. 
}

\apidesctable{
    If you are using \Fortran, \VAR{dest} must be of the following type:
}{Routine}{Data type of \VAR{dest} and \VAR{source}}

\apitablerow{SHMEM\_SWAP}{Integer of default kind}
\apitablerow{SHMEM\_INT4\_SWAP}{\CONST{4}-byte integer}
\apitablerow{SHMEM\_INT8\_SWAP}{\CONST{8}-byte integer}
\apitablerow{SHMEM\_REAL4\_SWAP}{\CONST{4}-byte real}
\apitablerow{SHMEM\_REAL8\_SWAP}{\CONST{8}-byte real}

\apireturnvalues{
       The content that had been at the \dest{} address on the remote \ac{PE}
       prior to the swap is returned.
}

\apinotes{
    None.
}

\begin{apiexamples}

\apicexample
    {The example below swap values between odd numbered \acp{PE} and their right
    (modulo) neighbor and outputs the result of swap.}
    {./example_code/shmem_swap_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
