\apisummary{
    This nonblocking atomic operation performs an atomic fetching bitwise AND
    operation on a remote data object.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_atomic\_fetch\_and\_nbi}@(TYPE *fetch, TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_atomic\_fetch\_and\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the bitwise \ac{AMO} types specified by
Table~\ref{bitamotypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_fetch\_and\_nbi}@(TYPE *fetch, TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_fetch\_and\_nbi}@(shmem_ctx_t ctx, TYPE *fetch, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the bitwise \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{bitamotypes}.

\begin{apiarguments}

  \apiargument{IN}{ctx}{A context handle specifying the context on which to
      perform the operation. When this argument is not provided, the
      operation is performed on the default context.}
  \apiargument{OUT}{fetch}{Local address of data object to be updated.
      The type of \VAR{fetch} should match that implied in the SYNOPSIS section.}
  \apiargument{OUT}{dest}{Symmetric address of the destination data object.
      The type of \dest{} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{value}{The operand to the bitwise AND operation.
      The type of \VAR{value} should match that implied in the SYNOPSIS section.}
  \apiargument{IN}{pe}{\ac{PE} number of the remote \ac{PE} relative to the team associated
      with the given \VAR{ctx} when provided, or the default context otherwise.}
\end{apiarguments}

\apidescription{
    The nonblocking \FUNC{shmem\_atomic\_fetch\_and\_nbi} routines perform an
    atomic fetching bitwise AND on the remotely accessible data object pointed
    by \VAR{dest} at \ac{PE} \VAR{pe} with the operand \VAR{value}. This routine
    returns after initiating the operation. The operation is considered complete
    after a subsequent call to \FUNC{shmem\_quiet}. At the completion of
    \FUNC{shmem\_quiet}, these routines have performed a fetching bitwise AND on
    \VAR{dest} at \ac{PE} \VAR{pe} with the operand \VAR{value} and fetched the prior
    contents of \VAR{dest} into the \VAR{fetch} local data object.
}

\apireturnvalues{
  None.
}

\end{apidefinition}
