\apisummary{
  Return the configuration parameters of a given team
}

\begin{apidefinition}

\begin{Csynopsis}
int @\FuncDecl{shmem\_team\_get\_config}@(shmem_team_t team, long config_mask, shmem_team_config_t *config);
\end{Csynopsis}

\begin{apiarguments}
  \apiargument{IN}{team}{An \openshmem team handle.}
  \apiargument{IN}{config\_mask}{
    The bitwise mask representing the set of configuration parameters to fetch from the given team.
    }
  \apiargument{OUT}{config}{
    A pointer to the configuration parameters for the given team.}
\end{apiarguments}

\apidescription{
\FUNC{shmem\_team\_get\_config} returns through the \VAR{config} argument
the configuration parameters as described by the mask, which were assigned according
to input configuration parameters when the team was created.
The output \VAR{config} argument indicates the \openshmem library's
parameter values at the time \FUNC{shmem\_team\_get\_config} is called.
These values may differ from the parameter values that were assigned at the
time of the team's creation.

If \VAR{team} compares equal to \LibConstRef{SHMEM\_TEAM\_INVALID},
then no operation is performed.
If \VAR{team} is otherwise invalid, the behavior is undefined.
If \VAR{config\_mask} is 0, then \VAR{shmem\_team\_get\_config} performs no action
and \VAR{config} may or may not be a null pointer.
If \VAR{config} is a null pointer, then \VAR{config\_mask} must be 0, otherwise
the behavior is undefined.
}

\apireturnvalues{
  If \VAR{team} does not compare equal to
  \LibConstRef{SHMEM\_TEAM\_INVALID}, then
  \FUNC{shmem\_team\_get\_config} returns \CONST{0};
  otherwise, it returns nonzero.
}

\end{apidefinition}
