\apisummary{
    Start a communication bundle.
}

\begin{apidefinition}

\begin{Csynopsis}
void @\FuncDecl{shmem\_bundle\_start}@(long options);
void @\FuncDecl{shmem\_ctx\_bundle\_start}@(shmem_ctx_t ctx, long options);
\end{Csynopsis}

\begin{apiarguments}
    \apiargument{IN}{ctx}{A context handle specifying the context on which to
    perform the optimization. When this argument is not provided, the
    optimization is performed on the default context.}
    \newtext{
    \apiargument{IN}{options}{The set of options requested for the
    given bundle.  Multiple options may be requested by combining
    them with a bitwise OR operation; otherwise, \CONST{0} can be
    given if no options are requested.}
    }
\end{apiarguments}

\apidescription{
    The \FUNC{shmem\_bundle\_start} routine provides a hint to the \openshmem
    library to \newtext{begin a bundling phase} \oldtext{being applying
    bundling-related optimizations}.
    \newtext{
        If a bundling phase is already started on a given
        communication context, another call to
        \FUNC{shmem\_bundle\_start} on that context has no effect.
        A bundling phase on a communication context must be
        stopped with a call to \FUNC{shmem\_bundle\_stop} on the
        same context.
    }
}

\apireturnvalues{
    None.
}

\apinotes{
    The \FUNC{shmem\_bundle\_start} routine is a hint for improving
    performance, and \openshmem implementations are not required to apply any
    optimization.
}

\end{apidefinition}


