\apisummary{
  Collectively resize an allocation of symmetric memory.
}

\begin{apidefinition}

\begin{Csynopsis}
void *@\FuncDecl{shmem\_realloc}@(void *ptr, size_t size);
\end{Csynopsis}

\begin{apiarguments}
  \apiargument{IN}{ptr}{Symmetric address of an object in the symmetric heap.}
  \apiargument{IN}{size}{The size, in bytes, of a block to be
    allocated from the symmetric heap.}
\end{apiarguments}


\apidescription{
  The \FUNC{shmem\_realloc} routine changes the size of the block to
  which \VAR{ptr} points to the size (in bytes) specified by
  \VAR{size}.  The contents of the block are unchanged up to the
  lesser of the new and old sizes.

  The \FUNC{shmem\_realloc} routine preserves allocation hints (e.g.,
  if \VAR{ptr} was allocated by \FUNC{shmem\_malloc\_with\_hints}).
  If the new size is larger, the newly allocated portion of the block
  is uninitialized.  If \VAR{ptr} is a null pointer, the
  \FUNC{shmem\_realloc} routine behaves like the \FUNC{shmem\_malloc}
  routine for the specified size.  If \VAR{size} is \CONST{0} and
  \VAR{ptr} is not a null pointer, the block to which it points is
  freed as if with \FUNC{shmem\_free}. If the space cannot be
  allocated or if hints cannot be preserved, the block to which
  \VAR{ptr} points is unchanged and a null pointer is returned.

  \FUNC{shmem\_realloc} may call barriers on both entry and exit,
  depending on whether an existing allocation is modified and whether
  new memory is allocated, respectively.
  It is the user's responsibility to ensure that no communication
  operations involving the given memory block are pending on other
  communication contexts prior to calling \FUNC{shmem\_realloc}.

  The value of the \VAR{ptr} and \VAR{size} arguments must be
  identical on all \acp{PE}; otherwise, the behavior is undefined.
}

\apireturnvalues{
  The \FUNC{shmem\_realloc} routine returns the symmetric address of
  the allocated space (which may have moved); otherwise, all \acp{PE}
  return a null pointer.
}

\apinotes{
  When the \VAR{ptr} argument in a call to \FUNC{shmem\_realloc} corresponds
  to a buffer allocated using \FUNC{shmem\_align}, the buffer returned by
  \FUNC{shmem\_realloc} is not guaranteed to maintain the alignment requested
  in the original call to \FUNC{shmem\_align}.
}

\end{apidefinition}
