\apisummary{
    A collective operation that allocates and initializes the resources used by
    the \openshmem library.
}

\begin{apidefinition}

\begin{Csynopsis}
void @\FuncDecl{shmem\_init}@(void);
\end{Csynopsis}

\begin{apiarguments}
    \apiargument{None.}{}{}
\end{apiarguments}

\apidescription{
    \FUNC{shmem\_init} allocates and initializes resources used by the \openshmem
    library. It is a collective operation that all \acp{PE} must call before any
    other \openshmem routine may be called, except \FUNC{shmem\_query\_initialized} 
    which checks the current initialized state of the library. At the end of the 
    \openshmem program which it initialized, the call to \FUNC{shmem\_init} must 
    be matched with a call to \FUNC{shmem\_finalize}.

    The \FUNC{shmem\_init} and \FUNC{shmem\_init\_thread} initialization
    routines may be called multiple times within an \openshmem program. A
    corresponding call to \FUNC{shmem\_finalize} must be made for each call to
    an \openshmem initialization routine. The \openshmem library must not be
    finalized until after the last call to \FUNC{shmem\_finalize} and may be
    re-initialized with a subsequent call to an initialization routine.

}

\apireturnvalues{
    None.
}

\begin{DeprecateBlock}
\apinotes{
    As of \openshmem[1.2], the use of \FUNC{start\_pes} has been
    deprecated and calls to it should be replaced with calls to \FUNC{shmem\_init}.
    While support for \FUNC{start\_pes} is still required in \openshmem libraries,
    users are encouraged to use \FUNC{shmem\_init}. An important difference between
    \FUNC{shmem\_init} and \FUNC{start\_pes} is that every call to
    \FUNC{shmem\_init} within a program must be matched with a call to \FUNC{shmem\_finalize}.
    In the case of \FUNC{start\_pes}, any subsequent calls to \FUNC{start\_pes} after the
    first one results in a no-op.
}
\end{DeprecateBlock}

\begin{apiexamples}

\apicexample
    {The following \FUNC{shmem\_init} example is for \Cstd[11] programs:}
    {example_code/shmem_init_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
