
\apisummary{
    Collective memory allocation routine with support for providing hints.
}

\begin{apidefinition}

\begin{Csynopsis}
void *@\FuncDecl{shmem\_malloc\_with\_hints}@(size_t size, long hints);
\end{Csynopsis}

\begin{apiarguments}
    \apiargument{IN}{size}{The size, in bytes, of a block to be
        allocated from the symmetric heap. This argument is of type \CTYPE{size\_t}}
    \apiargument{IN}{hints}{A bit array of hints provided by the user to the implementation}
\end{apiarguments}


\apidescription{

    The \FUNC{shmem\_malloc\_with\_hints} routine, like \FUNC{shmem\_malloc}, returns a pointer to a block of at least
    \VAR{size} bytes, which shall be suitably aligned so that it may be
    assigned to a pointer to any type of object.  This space is allocated from
    the symmetric heap (similar to \FUNC{shmem\_malloc}).  When the \VAR{size} is zero, 
    the \FUNC{shmem\_malloc\_with\_hint} routine performs no action and returns a null pointer. 
    
    In addition to the \VAR{size} argument, the \VAR{hints} argument is provided by the user. 
    The \VAR{hints} describes the expected manner in which the \openshmem program may use the allocated memory.
    The valid usage hints are described in Table~\ref{usagehints}. Multiple hints may be requested by combining them with a bitwise \CONST{OR} operation.
    
    The information provided by the \VAR{hints} is used to optimize for performance by the implementation. 
    If the implementation cannot optimize, the behavior is same as \FUNC{shmem\_malloc}.
    If more than one hint is provided, the implementation will make the best effort to use one or more hints 
    to optimize performance. 
            
    The \FUNC{shmem\_malloc\_with\_hint} routine is provided  so that multiple \acp{PE} in a program can allocate symmetric,
    remotely accessible memory blocks.  When no action is performed, these
    routines return without performing a barrier. Otherwise, the routine will call a barrier on exit.
    This ensures that all \acp{PE} participate in the memory allocation, and that the memory on other
    \acp{PE} can be used as soon as the local \ac{PE} returns. The implicit barrier performed by this routine will quiet the
    default context.  It is the user's responsibility to ensure that no communication operations involving the given memory block are pending on
    other contexts prior to calling the \FUNC{shmem\_free} and \FUNC{shmem\_realloc} routines.
    The user is also responsible for calling these routines with identical argument(s) on all
    \acp{PE}; if differing \VAR{size}, or \VAR{hints} arguments are used, the behavior of the call
    and any subsequent \openshmem calls is undefined.
}

\apireturnvalues{
    The \FUNC{shmem\_malloc\_with\_hints} routine returns a pointer to the allocated space;
    otherwise, it returns a null pointer.
}

\apinotes{ 
}

\apiimpnotes{
}
	\begin{longtable}{|p{0.45\textwidth}|p{0.5\textwidth}|}
	\hline
	\textbf{Hints} & \textbf{Usage hint}
	\tabularnewline \hline
	\endhead
	%%
	\LibConstDecl{SHMEM\_HINT\_NONE} &
	Behavior same as \FUNC{shmem\_malloc}
	\tabularnewline \hline
		
	\LibConstDecl{SHMEM\_HINT\_LOW\_LAT\_MEM} &
	Allocate memory on low-latency storage	
	\tabularnewline \hline
	
	\LibConstDecl{SHMEM\_HINT\_HIGH\_BW\_MEM} &
	Allocate memory on high-bandwidth storage	
	\tabularnewline \hline

	\LibConstDecl{SHMEM\_HINT\_PSYNC} &
	Memory used as \CONST{PSYNC} array
	\tabularnewline \hline
		
	\LibConstDecl{SHMEM\_HINT\_PWORK} &
	Memory used as \CONST{PWORK} array
	\tabularnewline \hline
	
	\LibConstDecl{SHMEM\_HINT\_ATOMICS} &
	Memory used for \VAR{Atomic} operations
	\tabularnewline \hline
	
	\LibConstDecl{SHMEM\_HINT\_SIGNAL} &
	Memory used for \VAR{signal} operations
	\tabularnewline \hline

	\TableCaptionRef{Memory usage hints}
        \label{usagehints}
    \end{longtable}

\end{apidefinition}
\newpage
