\apisummary{
    Performs an atomic add operation on a remote symmetric data object.
}

\begin{apidefinition}

\begin{C11synopsis}
void @\FuncDecl{shmem\_atomic\_add}@(TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_atomic\_add}@(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of the standard \ac{AMO} types specified by
Table~\ref{stdamotypes}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_atomic\_add}@(TYPE *dest, TYPE value, int pe);
void @\FuncDecl{shmem\_ctx\_\FuncParam{TYPENAME}\_atomic\_add}@(shmem_ctx_t ctx, TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of the standard \ac{AMO} types and has a corresponding
\TYPENAME{} specified by Table~\ref{stdamotypes}.

\begin{DeprecateBlock}
\begin{C11synopsis}
void @\FuncDecl{shmem\_add}@(TYPE *dest, TYPE value, int pe);
\end{C11synopsis}
where \TYPE{} is one of \{\CTYPE{int}, \CTYPE{long}, \CTYPE{long long}\}.

\begin{Csynopsis}
void @\FuncDecl{shmem\_\FuncParam{TYPENAME}\_add}@(TYPE *dest, TYPE value, int pe);
\end{Csynopsis}
where \TYPE{} is one of \{\CTYPE{int}, \CTYPE{long}, \CTYPE{long long}\}
and has a corresponding \TYPENAME{} specified by Table~\ref{stdamotypes}.
\end{DeprecateBlock}

\begin{Fsynopsis}
INTEGER pe
INTEGER*4  value_i4
CALL @\FuncDecl{SHMEM\_INT4\_ADD}@(dest, value_i4, pe)
INTEGER*8 value_i8
CALL @\FuncDecl{SHMEM\_INT8\_ADD}@(dest, value_i8, pe)
\end{Fsynopsis}

\begin{apiarguments}
    \apiargument{IN}{ctx}{A context handle specifying the context on which to perform the operation.
        When this argument is not provided, the operation is performed on
        the default context.}
    \apiargument{OUT}{dest}{The remotely accessible integer data object to be
        updated  on the remote \ac{PE}.  When using \CorCpp, the type of
        \dest{} should match that implied in the SYNOPSIS section.}
    \apiargument{IN}{value}{The value to be atomically added to \dest. When using \CorCpp, the type of \VAR{value} should match that  implied  in
        the SYNOPSIS  section.  When using \Fortran, it must be of type
        integer with an element size of \dest.}
    \apiargument{IN}{pe}{An integer that indicates the \ac{PE} number upon which
        \dest{} is to be updated.  When using \Fortran, it must be a default
        integer value.}
\end{apiarguments}

\apidescription{
    The \FUNC{shmem\_atomic\_add} routine performs an atomic add operation. It adds
    \VAR{value} to \dest{} on \ac{PE} \VAR{pe} and atomically updates the \dest{}
    without returning the value.
    If the context handle \VAR{ctx} does not correspond to a valid context,
    the behavior is undefined.
 }

\apidesctable{
    When using \Fortran, \VAR{dest} and \VAR{value} must be of the following type:
}{Routine}{Data type of \VAR{dest} and \VAR{value}}

\apitablerow{SHMEM\_INT4\_ADD}{\CONST{4}-byte integer}
\apitablerow{SHMEM\_INT8\_ADD}{\CONST{8}-byte integer}

\apireturnvalues{
    None.
}

\apinotes{
    None.
}

\begin{apiexamples}

\apicexample
    {}
    {./example_code/shmem_atomic_add_example.c}
    {}

\end{apiexamples}

\end{apidefinition}
