\openshmem is a \ac{PGAS} library interface specification. \openshmem aims to
provide a standard \ac{API} for SHMEM libraries to aid portability and
facilitate uniform predictable results of \openshmem programs by explicitly
stating the behavior and semantics of the \openshmem library calls. Through the
different versions, \openshmem will continue to address the requirements of the
\ac{PGAS} community.  As of this specification, many existing vendors support
\openshmem-compliant implementations and new vendors are developing
\openshmem library implementations to help the users write portable \openshmem
code. This ensures that programs can run on multiple platforms without having to
deal with subtle vendor-specific implementation differences. For more details on
the history of \openshmem please refer to the
\hyperref[sec:openshmem_history]{History of \openshmem} section.

The \openshmem\footnote{The \openshmem specification is owned by Open Source
Software Solutions Inc., a nonprofit organization, under an agreement with
\ac{HPE}.} effort is driven by the \ac{DoD} with continuous input from the \openshmem community.
To see all of the contributors and participants for the \openshmem \ac{API},
please see: \url{http://www.openshmem.org/site/Contributors}. In addition to the
specification, the effort includes a reference \openshmem
implementation, validation and verification suites, tools, a mailing list and
website infrastructure to support specification activities. For more information
please refer to: \url{http://www.openshmem.org/}.
