\section{Version 1.2}
This section summarizes the changes from the \openshmem specification Version 1.1 to the Version 1.2.  
A major change in this version is that it improves upon the execution model described in 1.1 by introducing an explicit \FUNC{shmem\_finalize} library call. This provides a collective mechanism of exiting an \openshmem application and releasing resources used by the library.  



The following list describes the specific changes in 1.2:
\begin{itemize}
\item New Execution Model for exiting/finishing OpenSHMEM applications.
\\See Section  \ref{subsec:execution_model}.
\item New library constants to support API that query version and name information. 
\\See Section \ref{subsec:library_constants}.
\item Deprecation of \FUNC{\_my\_pe} and \FUNC{\_num\_pes} routines.
\\See Sections \ref{subsec:shmem_my_pe} and \ref{subsec:shmem_num_pe}
\item New API \FUNC{shmem\_finalize} to provide collective mechanism to cleanly exit an \openshmem application and release resources.
\\See Section \ref{subsec:shmem_finalize}
\item New API \FUNC{shmem\_global\_exit} to provide mechanism to exit an \openshmem application.
\\See Section \ref{subsec:shmem_global_exit}.
\item New API to query the version and name information. 
\\See Section \ref{subsec:shmem_version} and \ref{subsec:shmem_name}.
\item \openshmem library API normalization. All C symmetric memory management API begins with  \FUNC{shmem\_}.
\\See Section \ref{subsec:shfree}.
\item Clarification related to \FUNC{shmem\_wait}.
\\See Section \ref{subsec:shmem_wait}.
\item Addition of new Annex for clearly specifying deprecated API and its support in the existing specification version.
\\See Section \ref{sec:dep_api}

\end{itemize}
