
\section{Library Constants}


\subsection{Constants Related To Reduction Operations}
Below are the library constants for the reduction operations.
The constants that start with SHMEM\_* are for \Fortran{} and 
\_SHMEM\_* for \Clang.

\subsubsection{SHMEM\_BCAST\_SYNC\_SIZE, \_SHMEM\_BCAST\_SYNC\_SIZE}

Length of the pSync arrays needed for broadcast operations. The value
of this constant is implementation specific. Refer to the \textbf{Broadcast
Routines} section under \textbf{Library Routines} for more information
about the usage of this constant.


\subsubsection{SHMEM\_SYNC\_VALUE, \_SHMEM\_SYNC\_VALUE}

Holds the value used to initialize the elements of pSync arrays. The
value of this constant is implementation specific.


\subsubsection{SHMEM\_REDUCE\_SYNC\_SIZE, \_SHMEM\_REDUCE\_SYNC\_SIZE}

Length of the work arrays needed for reduction operations. The value
of this constant is implementation specific. Refer to the \textbf{Reduction
Routines} section under \textbf{Library Routines} for more information
about the usage of this constant.


\subsubsection{SHMEM\_BARRIER\_SYNC\_SIZE, \_SHMEM\_BARRIER\_SYNC\_SIZE }

Length of the work array needed for barrier operations. The value
of this constant is implementation specific. Refer to the \textbf{Barrier
Synchronization Routines} section under \textbf{Library Routines}
for more information about the usage of this constant.


\subsubsection{SHMEM\_COLLECT\_SYNC\_SIZE, \_SHMEM\_COLLECT\_SYNC\_SIZE }

Length of the work array needed for collect operations. The value
of this constant is implementation specific. Refer to the \textbf{Collect
Routines} section under \textbf{Library Routines} for more information
about the usage of this constant.


\subsubsection{SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE, \_SHMEM\_REDUCE\_MIN\_WRKDATA\_SIZE }

Minimum length of work arrays used in various collective operations.
