\section{Overview}
\openshmem is a one-sided \ac{PGAS} library interface specification. In the \ac{PGAS} model, each process has local (or private) and 
globally shared memory that can be accessible by all processes where portions of the shared memory may have affinity to a particular process. 
\openshmem implements \ac{PGAS} using symmetric memory data objects to share information among processes or \ac{PE}s.   
\openshmem provides interfaces to perform communication and synchronization operations on both local and symmetric memory. 
\openshmem is a library and unlike UPC, CAF, Titanium, X10 and Chapel, which are all
PGAS languages, it relies on the programmer to create, destroy, access symmetric data objects, and synchronize \ac{PE}s using library calls.

The \openshmem specification is a result of effort to standardize widely available SHMEM implementations. 
The initial goal of the specification is to consolidate the existing vendor SHMEM implementations into a single specification, and  pave the way for 
a de-facto standard for SHMEM driven by the \openshmem community. A de-facto standard enables portability of SHMEM programs, and 
allows vendors to build and optimize their hardware architecture for OpenSHMEM.

The \openshmem specification defines library calls, constants, variables, and language bindings for C and Fortran.
Some of important \openshmem{} operations that you can do with \openshmem are as follows:

\begin{enumerate}
\item \textbf{Data Transfers }

\begin{enumerate}
\item One-sided puts : the initiator \ac{PE} (active side) specifies the local
data to be written to the target \ac{PE}'s (passive side) memory. 
\item One-sided gets : an explicit fetch operation is used to copy a variable
amount of data from a remote process and store it locally.\end{enumerate}
\begin{description}
\item [{{Note:}}] By avoiding the need for matching send and receive
calls, \openshmem simplifies the communication process by reducing the
number of calls required to have one \ac{PE} interact with other \ac{PE}s. 
\end{description}
\item \textbf{Synchronization Mechanisms }

\begin{enumerate}
\item Fence: Ensures ordering of PUT operations to a specific \ac{PE}. 
\item Quiet: Ensures ordering of PUT operations to all \ac{PE}s. 
\item Barrier: A collective synchronization routine in which no \ac{PE} may leave
the barrier prior to all \ac{PE}s entering the barrier. 
\end{enumerate}
\item \textbf{Collective Communication}

\begin{enumerate}
\item Broadcast: Copy a block of data from one \ac{PE} to one or more remote
PEs. 
\item Collection: Concatenate elements from the source array to a target
array over the specified \ac{PE}s. 
\item Reduction: Perform an associative binary operation over the specified
\ac{PE}s. 
\end{enumerate}
\item \textbf{Address Manipulation}

\begin{enumerate}
\item Allocating and deallocating memory blocks in the symmetric space.
\end{enumerate}
\item \textbf{Locks}

\begin{enumerate}
\item Implementation of mutual exclusion.
\end{enumerate}
\item \textbf{Atomic Memory Operations}

\begin{enumerate}
\item Swap, Conditional Swap, Add and Increment 
\end{enumerate}
\item \textbf{Data Cache control}

\begin{enumerate}
\item Implementation of mechanisms to exploit the capabilities of hardware
cache if available.
\end{enumerate}
\end{enumerate}
\begin{description}
\item [{{Note:}}] More information about \openshmem routines can be found
in the Library Routines section.
\end{description}

