       Copies data from a specified processing element (PE).

SYNOPSIS
       C or C++:

	  void shmem_double_get(double *target, const double  *source,	size_t
	  nelems, int pe);

	  void shmem_float_get(float *target, const float *source, size_t nelems,
	  int pe);

	  void shmem_get32(void *target, const void *source, size_t  nelems,  int
	  pe);

	  void	shmem_get64(void  *target, const void *source, size_t nelems, int
	  pe);

	  void shmem_get128(void *target, const void *source, size_t nelems,  int
	  pe);

	  void	shmem_getmem(void *target, const void *source, size_t nelems, int
	  pe);

	  void shmem_int_get(int *target, const int *source, size_t  nelems,  int
	  pe);

	  void	shmem_long_get(long  *target,  const long *source, size_t nelems,
	  int pe);

	  void shmem_longdouble_get(long double	 *target,  const  long	double
	  *source, size_t nelems, int pe);

	  void	shmem_longlong_get(long long *target, const long long *source,
	  size_t nelems, int pe);

	  void shmem_short_get(short *target, const short *source, size_t nelems,
	  int pe);

       Fortran:

	  INTEGER nelems, pe

	  CALL SHMEM_CHARACTER_GET(target, source, nelems, pe)

	  CALL SHMEM_COMPLEX_GET(target, source, nelems, pe)

	  CALL SHMEM_DOUBLE_GET(target, source, nelems, pe)

	  CALL SHMEM_GET4(target, source, nelems, pe)

	  CALL SHMEM_GET8(target, source, nelems, pe)

	  CALL SHMEM_GET32(target, source, nelems, pe)

	  CALL SHMEM_GET64(target, source, nelems, pe)

	  CALL SHMEM_GET128(target, source, nelems, pe)

	  CALL SHMEM_GETMEM(target, source, nelems, pe)

	  CALL SHMEM_INTEGER_GET(target, source, nelems, pe)

	  CALL SHMEM_LOGICAL_GET(target, source, nelems, pe)

	  CALL SHMEM_REAL_GET(target, source, nelems, pe)

DESCRIPTION

Arguments

	OUT       target	 Local data object to be updated.

       IN	source	 Data object on the PE identified by pe that contains the data
		 to  be copied.	 This data object must be remotely accessible.

       IN	nelems	 Number of elements in the target and source arrays.  nelems must
		 be  of	 type integer.	If you are using Fortran, it must be a
		 constant, variable, or array element of default integer type.

       IN	pe	 PE  number of the remote PE.  pe must be of type integer.  If
		 you are using Fortran, it must be a  constant,	 variable,  or
		 array element of default integer type.

API Description

       The  get	 routines  provide  a  method	 for copying a
       contiguous symmetric data object from a different PE to a contiguous data	object
       on  a  the  local  PE.	The  routines  return  after the data has been
       delivered to the target array on the local PE.

       The  target and source data objects must conform to typing constraints,
       which are as follows:

       Routine			     Data Type of target and source

       shmem_getmem		     Fortran:  Any noncharacter type.

				     C:	 Any  data  type.  nelems	is  scaled  in
				     bytes.

       shmem_get4, shmem_get32	     Any  noncharacter type that has a storage
				     size equal to 32 bits.

       shmem_get8, shmem_get64	     Any noncharacter type that has a  storage
				     size equal to 64 bits.

       shmem_get128		     Any  noncharacter type that has a storage
				     size equal to 128 bits.

       shmem_short_get		     Elements of type short.

       shmem_int_get		     Elements of type int.

       shmem_long_get		     Elements of type long.

       shmem_longlong_get	     Elements of type long long.

       shmem_float_get		     Elements of type float.

       shmem_double_get		     Elements of type double.

       shmem_longdouble_get	     Elements of type long double.

       SHMEM_CHARACTER_GET	     Elements of type character.  nelems  is  the
				     number  of	 characters  to transfer.  The
				     actual character nelemsgths  of  the	source
				     and target variables are ignored.

       SHMEM_COMPLEX_GET	     Elements of type complex of default size.

       SHMEM_DOUBLE_GET (Fortran)    Elements of type double precision.

       SHMEM_INTEGER_GET	     Elements of type integer.

       SHMEM_LOGICAL_GET	     Elements of type logical.

       SHMEM_REAL_GET		     Elements of type real.

       If you are using Fortran, data types must  be  of  default  size.   For
       example,	 a  real  variable  must  be  declared	as  REAL,  REAL*4,  or
       REAL(KIND=4).

NOTES
       See Introduction for a definition of the term remotely accessible.

EXAMPLES
       Consider this simple example for Fortran.

	 \lstinputlisting[language=C]{shmem_get_example.f90}
