 \bAPI{SHMEM\_LOCK}{Releases, locks, and tests a mutual exclusion memory lock.}
\synC
void shmem_clear_lock(long *lock);
void shmem_set_lock(long *lock);
int shmem_test_lock(long *lock);
%*\synCE    %DO NOT DELETE. THIS LINE IS NOT A COMMENT
\synF   %Synopsis for FORTRAN API
INTEGER lock, SHMEM_TEST_LOCK
CALL SHMEM_CLEAR_LOCK(lock)
CALL SHMEM_SET_LOCK(lock)
I = SHMEM_TEST_LOCK(lock)
 %*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT  
\desB{
   \argRow{IN}{lock}{	 A symmetric data object that is a scalar variable or an array
		 of  length \CONST{1}. This data  object  must  be set to \CONST{0} on all
		 \ac{PE}s prior to the first use. \VAR{lock}  must  be  of type \CONST{long}. If you are using Fortran, it must be of
		 default kind.}
}
{
       The \FUNC{shmem\_set\_lock} routine sets a mutual exclusion lock after  waiting
       for  the lock  to be freed by any other \ac{PE} currently holding the lock.
       Waiting \ac{PE}s  are  assured  of  getting	the  lock  in  a  first-come,
       first-served manner.The \FUNC{shmem\_clear\_lock}  routine releases  a  lock  previously  set  by
       \FUNC{shmem\_set\_lock}  after  ensuring that  all  local  and  remote	 stores
       initiated in the critical region are complete. The \FUNC{shmem\_test\_lock} function sets a mutual exclusion lock only if it is
       currently cleared.  By using this function, a \ac{PE} can avoid blocking  on
       a set lock.  If the lock is currently set, the function returns without
       waiting. These routines are appropriate for protecting a critical region from
       simultaneous  update  by multiple  \ac{PE}s.	  
}
{
\desR{
       The \FUNC{shmem\_test\_lock} function returns \CONST{0} if  the lock  was  originally
       cleared and  this  call was  able  to set the lock.  A value of \CONST{1} is
       returned if the lock had been set and the call returned without waiting
       to set the lock.}

\notesB{
       The term symmetric data object is defined in Introduction.
}
}

\exampleB {
\exampleITEM	
 {The following  simple example uses  \FUNC{shmem\_lock}  in a C program.}
 {./EXAMPLES/shmem_lock_example.c}{}
}
\eAPI