\bAPI{SHMEM\_SWAP}{Performs an atomic swap to a remote data object.}
\synC
 	  
double shmem_double_swap(double *dest, double value, int pe);
float shmem_float_swap(float *dest, float value, int pe);
int shmem_int_swap(int *dest, int value, int pe);
long shmem_long_swap(long *dest, long value, int pe);
long long shmem_longlong_swap(long long *dest, long long value, int pe);
long shmem_swap(long *dest, long value, int pe); %*\synCE    %DO NOT DELETE. THIS LINE IS NOT A COMMENT

\synF   %Synopsis for FORTRAN API

INTEGER SHMEM_SWAP, value, pe
ires = SHMEM_SWAP(dest, value, pe) 
INTEGER*4 SHMEM_INT4_SWAP, value_i4, ires_i4
ires_i4 = SHMEM_INT4_SWAP(dest, value_i4, pe) 
INTEGER*8 SHMEM_INT8_SWAP, value_i8, ires_i8
ires_i8 = SHMEM_INT8_SWAP(dest, value_i8, pe)
REAL*4 SHMEM_REAL4_SWAP, value_r4, res_r4
res_r4 = SHMEM_REAL4_SWAP(dest, value_r4, pe) 
REAL*8 SHMEM_REAL8_SWAP, value_r8, res_r8
res_r8 = SHMEM_REAL8_SWAP(dest, value_r8, pe)%*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT  
%ORIGINAL

% Arguments table. If no arguments you can use \argRow{None}{}{} 
\desB{  
\argRow{OUT}{dest}{The  remotely accessible integer data object to be updated on
		 the remote \ac{PE}.	 If you are using \CorCpp, the type of \dest{}
		 should match that  implied in the SYNOPSIS section.}
\argRow{IN}{value}{The value to be atomically written to the remote  \ac{PE}. \VAR{value}  is
		 the same type as \dest.}
\argRow{IN}{pe}{ An integer that indicates the \ac{PE} number on which \dest{} is to
		 be updated. If you are using \Fortran, it must be a default
		 integer value.}
}
%API description
{      \FUNC{shmem\_swap}  performs  an atomic swap operation. It writes \VAR{value} into \dest{} on \ac{PE} and returns the previous
       contents of \dest{} as an atomic operation. 
}
%API Description Table
{
\hfill \\
\desTB {If you are using \Fortran, \VAR{dest} must be of the following type:}
{
\cRow{SHMEM\_SWAP}{Integer of default kind}
\cRow{SHMEM\_INT4\_SWAP}{\CONST{4}-byte integer}
\cRow{SHMEM\_INT8\_SWAP}{\CONST{8}-byte integer}
\cRow{SHMEM\_REAL4\_SWAP}{\CONST{4}-byte real}
\cRow{SHMEM\_REAL8\_SWAP}{\CONST{8}-byte real}
}
 %Return Values     
\desR{
       The content that had been at the \dest{} address on the remote \ac{PE} prior
       to the swap is returned.
}
%end of DesB% Notes. If there are no notes, this field can be left empty.
\notesB{None.}
}
%Example
\exampleB{
    %For each example, you can enter it as an item.
    \exampleITEM
    {The example below swap values between odd numbered \acp{PE} and their right (modulo) neighbor and outputs the result of swap.}
    {./EXAMPLES/shmem_swap_example.c}
{}
}  	
\eAPI
