\bAPI{SHMEM\_PE\_ACCESSIBLE}{Determines whether a \ac{PE} is accessible via \openshmem's data transfer operations.}
\synC     
int shmem_pe_accessible(int pe); %*\synCE    %DO NOT DELETE. THIS LINE IS NOT A COMMENT
\synF
LOGICAL LOG, SHMEM_PE_ACCESSIBLE
INTEGER pe
LOG = SHMEM_PE_ACCESSIBLE(pe) %*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT

\desB{
\argRow{IN}{pe}{Specific pe that needs to be checked if accessible from the local \ac{PE}.}
}
{
       \FUNC{shmem\_pe\_accessible} is  a  query function  that indicates  whether  a
       specified \ac{PE} is accessible via \openshmem from the local \ac{PE}. The \FUNC{shmem\_pe\_accessible} function returns \CONST{TRUE} only if  the  remote  \ac{PE} is a process  running from the same executable  file as the local \ac{PE}, indicating that full \openshmem support for symmetric data objects (that resides in the static memory and symmetric heap) is available, otherwise it returns \CONST{FALSE}.  This function may be particular useful for hybrid programming with other communication libraries (such as a \ac{MPI}) or parallel languages.  For example, on  SGI Altix  series  systems, \openshmem is  supported  across multiple partitioned hosts and InfiniBand connected hosts. When running multiple executable MPI applications using \openshmem on an Altix, full \openshmem support is available between processes running from the same executable file. However, \openshmem support between processes of different executable  files  is  supported only for data objects on the symmetric heap, since static data objects are  not symmetric  between  different executable  files.        
%       The \FUNC{shmem\_pe\_accessible} function on Altix returns
%       TRUE only if  the  remote  \ac{PE}  is  a  process  running  from  the  same
%       executable  file	 as  the  local \ac{PE}, indicating that full \openshmem support
%       (static memory and symmetric heap) is available.
}
{
\desR{\Clang: The return value is 1 if the specified \ac{PE} is a valid remote
	          \ac{PE} for \openshmem functions; otherwise,it is 0. \\ \\
	  \Fortran:	The return value is \CONST{.TRUE.} if the specified \ac{PE} is a valid
		 remote \ac{PE} for \openshmem functions; otherwise, it is \CONST{.FALSE.}.	 
		 }
\notesB{ None. }
}

\eAPI
