\bAPI{SHMEM\_WAIT}{Wait for a variable on the local \ac{PE} to change.}
\label{subsec:shmem_wait}
\synC   %Synopisis for C API

void shmem_int_wait(int *ivar, int cmp_value);
void shmem_int_wait_until(int *ivar, int cmp, int cmp_value);
void shmem_long_wait(long *ivar, long cmp_value);
void shmem_long_wait_until(long *ivar, int cmp, long cmp_value);
void shmem_longlong_wait(long long *ivar, long long cmp_value);
void shmem_longlong_wait_until(long long *ivar, int cmp, long long cmp_value);
void shmem_short_wait(short *ivar, short cmp_value);
void shmem_short_wait_until(short *ivar, int cmp, short cmp_value);
void shmem_wait(long *ivar, long cmp_value);
void shmem_wait_until(long *ivar, int cmp, long cmp_value);%*\synCE    %DO NOT DELETE. THIS LINE IS NOT A COMMENT
%
%void shmem_int_wait(int *var, int value);
%void shmem_int_wait_until(int *var, int cond, int value);
%void shmem_long_wait(long *var, long value);
%void shmem_long_wait_until(long *var, int cond, long value);
%void shmem_longlong_wait(long long *var, long long value);
%void shmem_longlong_wait_until(long long *var, int cond, long long value);
%void shmem_short_wait(short *var, short value);
%void shmem_short_wait_until(short *var, int cond, short value);
%void shmem_wait(long *ivar, long cmp_value);
%void shmem_wait_until(long *ivar, int cmp, long value); %*\synCE    %DO NOT DELETE. THIS LINE IS NOT A COMMENT

\synF   %Synopsis for FORTRAN API

CALL SHMEM_INT4_WAIT(ivar, cmp_value)
CALL SHMEM_INT4_WAIT_UNTIL(ivar, cmp, cmp_value)
CALL SHMEM_INT8_WAIT(ivar, cmp_value)
CALL SHMEM_INT8_WAIT_UNTIL(ivar, cmp, cmp_value)
CALL SHMEM_WAIT(ivar, cmp_value)
CALL SHMEM_WAIT_UNTIL(ivar, cmp, cmp_value) %*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT  

% Arguments table. If no arguments you can use \argRow{None}{}{} 
\desB{  
\argRow{OUT}{ivar}{A remotely accessible integer variable that is being updated by
	       another \ac{PE}.  If you are using \CorCpp, the type of \VAR{ivar} should
	       match that implied in the SYNOPSIS section.} 
\argRow{IN}{cmp}{The compare operator that compares \VAR{ivar} with \VAR{cmp\_value}.  \VAR{cmp}
	       must be of type integer.  If you are using \Fortran, it must  be
	       of  default kind.  If you are using \CorCpp, the type of \VAR{cmp}
	       should match that implied in the SYNOPSIS section.}        
\argRow{IN}{cmp\_value}{\VAR{cmp\_value} must be of type integer.  If you are using \CorCpp, the type of \VAR{cmp\_value} should match that implied in the SYNOPSIS
	       section.  If  you are using \Fortran, cmp\_value must be an
	       integer of the same size and kind as \VAR{ivar}.}
}
%API description
{ 
        \FUNC{shmem\_wait} and \FUNC{shmem\_wait\_until} wait for \VAR{ivar} to be changed by a remote
       write or an atomic operation issued by a different \ac{PE}. 
       These  routines can be used for point-to-point direct synchronization.  A call to
       \VAR{shmem\_wait} does not return until some other \ac{PE} writes  a value,
       not equal to \VAR{cmp\_value}, into \VAR{ivar} on the waiting \ac{PE}.  A call to
       \FUNC{shmem\_wait\_until} does not return until some  other \ac{PE} changes
       \VAR{ivar} to satisfy the condition implied by \VAR{cmp} and \VAR{cmp\_value}.  
       This mechanism is useful when a \ac{PE} needs to tell another \ac{PE}
       that it has completed some action.
       The \FUNC{shmem\_wait}  routines return when \VAR{ivar} is no  longer  equal  to
       \VAR{cmp\_value}. The \FUNC{shmem\_wait\_until} routines return when the compare condition is true.  The compare condition is defined by the \VAR{ivar}  argument  compared
       with the \VAR{cmp\_value} using the comparison operator, \VAR{cmp}. 
  }
 %API Description Table. 
{
\hfill \\
 % If there is no Description Table and return, this field can be 
  \desTBC{ If you are using \Fortran, \VAR{ivar} must be a specific sized integer type according to the routine being called, as follows:}
  {Routine}{Type of \VAR{ivar}}
 {
 %\cRow{Function}{Type of ivar}
     \cRow{shmem\_wait, shmem\_wait\_until}{default INTEGER}
     \cRow{shmem\_int4\_wait, shmem\_int4\_wait\_until}{INTEGER*4}
\cRow{shmem\_int8\_wait, shmem\_int8\_wait\_until}{INTEGER*8}
}

\desTBC{ The following \VAR{cmp} values are supported:}{CMP Value}{Comparison}
 {
%\cRow{cmp Value}{Comparison}
\CorCpp:\\
\cRow{\_SHMEM\_CMP\_EQ }{  Equal}
\cRow{\_SHMEM\_CMP\_NE}{Not equal}
\cRow{\_SHMEM\_CMP\_GT}{Greater than}
\cRow{\_SHMEM\_CMP\_LE}{Less than or equal to}
\cRow{\_SHMEM\_CMP\_LT}{Less than}
\cRow{\_SHMEM\_CMP\_GE}{Greater than or equal to}
\\
\Fortran:\\
\cRow{SHMEM\_CMP\_EQ }{  Equal}
\cRow{SHMEM\_CMP\_NE}{Not equal}
\cRow{SHMEM\_CMP\_GT}{Greater than}
\cRow{SHMEM\_CMP\_LE}{Less than or equal to}
\cRow{SHMEM\_CMP\_LT}{Less than}
\cRow{SHMEM\_CMP\_GE}{Greater than or equal to}
}
%Return Values     
\desR{None.}
%end Description Table.
\notesImp{
    Implementations must ensure that \FUNC{shmem\_wait} and
    \FUNC{shmem\_wait\_until} do not return before the update of the memory
    indicated by \VAR{ivar} is fully complete.  Partial updates to the memory
    must not cause \FUNC{shmem\_wait} or \FUNC{shmem\_wait\_until} to return.
}
}
\exampleB{
%For each example, you can enter it as an item.
 \exampleITEMF
 { The following call returns when variable ivar is not equal to 100:}
{./EXAMPLES/shmem_wait1_example.f90}
 {}
 \exampleITEMF
 { The following call to \FUNC{SHMEM\_INT8\_WAIT\_UNTIL} is  equivalent to the call to \FUNC{SHMEM\_INT8\_WAIT} in example 1:}
{./EXAMPLES/shmem_wait2_example.f90}
 {}
 \exampleITEMF
 {The following \CorCpp{} call waits until the sign bit in ivar
       is set by a transfer from a remote PE:}
{./EXAMPLES/shmem_wait3_example.f90}
 {}
 \exampleITEMF
 {The following \Fortran{} example is in the context of a
       subroutine:}
{./EXAMPLES/shmem_wait4_example.f90}
 {}
}
\eAPI 
