\bAPI{SHMEM\_FINC}{Performs an atomic fetch-and-increment  operation on a remote data object.}
\synC   %Synopisis for C API

int shmem_int_finc(int *target, int pe);
long shmem_long_finc(long *target, int pe);
long long shmem_longlong_finc(long long *target, int pe); %*\synCE    %DO NOT DELETE. THIS LINE IS NOT A COMMENT
%\rcomment{Manju: Do we need the pe, ires4, ires8 ? }

\synF   %Synopsis for FORTRAN API

INTEGER pe 
INTEGER*4 SHMEM_INT4_FINC, ires_i4
ires_i4 = SHMEM_INT4_FINC(target, pe)
INTEGER*8 SHMEM_INT8_FINC, ires_i8
ires_i8 = SHMEM_INT8_FINC(target, pe) %*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT  

% Arguments table. If no arguments you can use \argRow{None}{}{} 
\desB{  
	\argRow{IN}{target}{The remotely accessible integer data object to be updated on
		 the remote \ac{PE}.	 The type of \target{} should match that implied
		 in the SYNOPSIS section.}
    \argRow{IN}{pe}{An integer that indicates the \ac{PE} number on which \target{} is to
		 be updated.  If you are using \Fortran, it must be a default
		 integer value.}
 }
%API description
{
   These routines perform a fetch-and-increment operation.  The \target{} on
   \ac{PE} \VAR{pe} is increased by one and the routine returns
   the previous contents of \target{} as an atomic operation.
}
%API Description Table.
{ \hfill \\
\desTB {If you are using \Fortran, \VAR{target} must be of the following type:}
{
\cRow{SHMEM\_INT4\_FINC}{\CONST{4}-byte integer}
\cRow{SHMEM\_INT8\_FINC}{\CONST{8}-byte integer}
}
    %Return Values     
\desR{The contents that had been at the \target{} address on the remote \ac{PE} prior to the increment.  The data type of the return value is the same as the \target.} 
% Notes. If there are no notes, this field can be left empty.
\notesB{None.}
}
%\rcomment{Manju: Seems like the indent for notes and return depends on whether
%there is a newline before (\ac{API} Description Table) or not. We might have to fix
%it}
\exampleB{
       \exampleITEM
	    {The following \FUNC{shmem\_finc} example is for \CorCpp{} programs:}
        {./EXAMPLES/shmem_finc_example.c}
        {}
}
\eAPI



	
