       Performs an atomic fetch-and-add operation	 on  a
       remote data object.

SYNOPSIS

       C or C++:

	  int shmem_int_fadd(int *target, int value, int pe);

	  long shmem_long_fadd(long *target, long value, int pe);

	  long	long  shmem_longlong_fadd(long	long *target, long long value,
	  int pe);

       Fortran:

	  INTEGER pe

	  INTEGER(KIND=4) SHMEM_INT4_FADD, ires, target, value
	  ires = SHMEM_INT4_FADD(target, value, pe)

	  INTEGER(KIND=8) SHMEM_INT8_FADD, ires, target, value
	  ires = SHMEM_INT8_FADD(target, value, pe)


DESCRIPTION

Arguments

	OUT       target	 The  remotely accessible integer data object to be updated on
		 the remote PE.	 The type of target should match that  implied
		 in the SYNOPSIS section.

       IN	value	 The  value  to	 be  atomically	 added to target.  The type of
		 value should match that implied in the SYNOPSIS section.

       IN	pe	 An integer that indicates the PE number on which target is to
		 be  updated.	If you are using Fortran, it must be a default
		 integer value.
API Description

       shmem_fadd functions perform an	atomic	fetch-and-add  operation.   An
       atomic fetch-and-add operation fetches the old target and adds value to
       target without the  possibility	of  another atomic operation on the target
       between the time of the fetch and the update.  These routines add value
       to target on  Processing	 Element  (PE)	pe  and	 return	 the  previous
       contents of target as an atomic operation.

Return Value

       The contents that had been at the target address on the remote PE prior
       to the atomic addition operation. The data type of return value is the same as the target.


NOTES

EXAMPLE

	\lstinputlisting[language=C]{shmem_fadd_example.c}
