\bAPI{SHMEM\_GLOBAL\_EXIT}{A non-collective routine that allows any \ac{PE} to force
termination of an entire \openshmem program. This routine terminates the entire
program, not just the \openshmem portion.}
%SYNOPSIS
\synC
void shmem_global_exit(int status); %*\synCE
\synF
INTEGER STATUS
CALL SHMEM_GLOBAL_EXIT(status) %*\synFE

%DESCRIPTION

%Arguments
\desB{
    \argRow{IN}{status}{The exit status from the main program.}
}
%API Description
{
    \FUNC{shmem\_global\_exit} is a non-collective routine that allows any one
    \ac{PE} to force termination of an \openshmem program for all \acp{PE},
    passing an exit status to the execution environment. This routine
    terminates the entire program, not just the \openshmem portion. When any
    \ac{PE} calls \FUNC{shmem\_global\_exit}, it results in the termination of
    all \acp{PE} with no further code from the program being executed.
    \FUNC{shmem\_global\_exit} flushes I/O and releases resources in accordance
    with C/C++/Fortran language requirements for normal program termination. If
    more than one \ac{PE} calls \FUNC{shmem\_global\_exit}, then the exit
    status returned to the environment shall be one of the values passed to
    \FUNC{shmem\_global\_exit} as the status argument.  There is no return to
    the caller of \FUNC{shmem\_global\_exit}; control is returned from the
    \openshmem library to the execution environment for all \acp{PE}.
}
%API Description Table
{
%Return Value
\desR{		
None.}
%NOTES	
\notesB{ 
    \FUNC{shmem\_global\_exit} may be used in situations where one or more
    \acp{PE} have determined that the program has completed and/or should
    terminate early.  Accordingly, the integer status argument can be used to
    pass any information about the nature of the exit, e.g an encountered error
    or a found solution.  Since \FUNC{shmem\_global\_exit} is a non-collective
    routine, there is no implied synchronization, and all \acp{PE} must
    terminate regardless of their current execution state. If
    \FUNC{shmem\_global\_exit} is called by more than one \ac{PE}, then the
    exit status that is returned to the execution environment is one of the
    values passed to \FUNC{shmem\_global\_exit}. While I/O must be flushed for
    standard language I/O calls from C/C++/Fortran, it is implementation
    dependent as to how I/O done by other means (e.g. third party I/O
    libraries) is handled. Similarly, resources are released according to
    C/C++/Fortran standard language requirements, but this may not include all
    resources allocated for the \openshmem program. However, a quality
    implementation will make a best effort to flush all I/O and clean up all
    resources.
}
}
%EXAMPLES
\exampleB{
\exampleITEM
    {}
    {./EXAMPLES/shmem_global_exit_example.c}
    {}
}
\eAPI
