\bAPI{SHPALLOC}{Allocates a block of memory from the symmetric heap.}
\synF   %Synopsis for FORTRAN API

POINTER (addr, A(1))
INTEGER (length, errcode, abort)
CALL SHPALLOC(addr, length, errcode, abort) %*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT  

% Arguments table. If no arguments you can use \argRow{None}{}{}
\desB{  
 \argRow{OUT}{addr}{First word address of the allocated block.}
 \argRow{IN}{length}{Number of words of memory requested. One word is 32 bits.}
 \argRow{OUT}{errcode}{Error code is \CONST{0} if no error was detected; otherwise, it is a negative integer code for the type of error.}
 \argRow{IN}{abort}{Abort code; nonzero requests abort on error; \CONST{0}  requests
		      an error code.}
}
 %API description
 {   
       \FUNC{SHPALLOC} allocates a block of memory from the program's symmetric heap
       that is greater than or equal  to  the  size  requested. To  maintain symmetric heap 
       consistency, all \ac{PE}s in an program must call \FUNC{SHPALLOC} with the same value of length; if any  \ac{PE}s are missing, the program will hang.
       
       By using the \Fortran{} \CONST{POINTER} mechanism in the following manner, you can use array \VAR{A} to refer to the block allocated by \FUNC{SHPALLOC}: \CONST{POINTER} (\VAR{addr},
       \VAR{A}())
  }
 %API Description Table. 
{
{
 %Return Values     
\desR{ }
\cRow{Error Code} {Condition}
\cRow{ \CONST{-1} } {Length is not an integer greater than \CONST{0}}
\cRow{\CONST{-2}} { No more memory is available from the system (checked if the  request cannot be satisfied from the available blocks on the symmetric heap).}
}%end of DesR
\notesB{  
       The total size of the symmetric heap is determined at job startup.  One
       may adjust the size of the heap using the \CONST{SMA\_SYMMETRIC\_SIZE}
       environment variable (if available).	
}
}
%Example
%\exampleB{}
\eAPI 
