\bAPI{SHPCLMOVE}{Extends  a symmetric heap block or copies the contents of the block into a larger block.}
\synF   %Synopsis for FORTRAN API

POINTER (addr, A(1))
INTEGER length, status, abort
CALL SHPCLMOVE (addr, length, status, abort) %*\synFE   %DO NOT DELETE. THIS LINE IS NOT A COMMENT  

% Arguments table. If no arguments you can use \argRow{None}{}{} 
\desB{  
       \argRow{INOUT}{addr}{On  entry, first word address of the block to change; on
		      exit, the new address of the block if it was moved.}
        \argRow{IN}{length}{Requested new total length in words. One word
		      is \CONST{32} bits.}
        \argRow{OUT}{status}{Status is \CONST{0} if the block was extended in place, \CONST{1} if it
		      was moved, and a negative integer for the type of error 		      detected.}
       \argRow{IN}{abort}{Abort code.  Nonzero requests abort on error; \CONST{0} requests
		      an error code.}
}
%API description
 {     The \FUNC{SHPCLMOVE} function either extends a symmetric  heap block  if  the
       block is followed by a large enough free block or copies the contents
       of the existing block to a larger  block	 and  returns  a  status  code
       indicating that the block was moved.  This function also can reduce the
       size of a block if the new length is less than  the old length. All
       \ac{PE}s  in a program must call \FUNC{SHPCLMOVE} with the
       same value of \VAR{addr} to maintain symmetric heap consistency; if any  \ac{PE}s
       are missing, the program hangs.
 }
 %API Description Table. 
{
 %Return Values     
\desR{ 
\cRow{Error Code} {Condition}
\cRow{\CONST{-1} } {Length is not an integer greater than \CONST{0}}
\cRow{\CONST{-2}} { No more memory is available from the system (checked  if the  request  cannot  be	satisfied from the available blocks on the symmetric heap).}
\cRow{\CONST{-3}}{	 Address is outside the bounds of the symmetric heap.}
\cRow{\CONST{-4}}{Block is already free.}
\cRow{\CONST{-5}}{Address is not at the beginning of a block.}
}%end of DesB
\notesB{None.}
}   
\eAPI 
