\openshmem \Fortran[bind(C)] language bindings is based on \Fortran-\Cstd
interoperability feature introduced in
\Fortran[2003]\footnote{ISO/IEC 1539-1:2004(E)} language standard. Since
\Fortran[2003] there is a standarized way to generate procedure and derived-type
declarations and global variables which are interoperable with
\Cstd\footnote{ISO/IEC 9899:1999}. A bind(C) attribute is added in the \Fortran
language to enable this interoperability with \Cstd. The \openshmem
\Fortran[bind(C)] language bindings use this standard way to generate \Fortran
wrappers over the primary \Cstd language bindings provided by \openshmem.

\begin{itemize}
    \item All available language constants, library handles, and environment
    variables from the \openshmem specification are supported by this language
    bindings.
    \item All the \openshmem APIs specified by this language bindings are
    implemented as a wrapper interface using \Fortran bind(C) attribute over the
    \Cstd language bindings specified by \openshmem specification.
    \item The \Fortran[bind(C)] language bindings is defined in a module named
    \textit{shmem}. The \textit{shmem} module must contain only the interfaces
    and constant names defined in this specification.
    \item All \openshmem extension APIs that are not part of this specification
    must be defined in a separate \textit{shmemx} module. The \textit{shmemx}
    module must exist, even if no extensions are provided. Any extensions shall
    use the \textit{shmemx\_} prefix for all routine, variable, and constant
    names.
    \item \openshmem APIs in this language bindings are available either as a
    subroutine or a function. \openshmem \Cstd APIs which returns a value are
    wrapped as functions, while those APIs that in some arguments and perform a
    specific operation without returning any values are wrapped as subroutines.
    \item As the \Fortran[bind(C)] language bindings are implemented over the
    \openshmem \Cstd language bindings, there are no semantic or functional
    differences in the \Fortran[bind(C)] language binding interfaces.
\end{itemize}
